%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Death Master}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Death Masters are the minions of the Gods of Undead, Deamon Lords, and Archdevils. Armed with a powerful combination of divine and arcane magic, the Death Master is the unquestioned master of necromancy. He gains a series of boons from his Master of Undeath that allow him to spread terror and fear across the land. Even some of the mightiest undead creatures see him as a worthy leader. While rare, the magical powers and deadly abilities of Death Masters allow them to cause far more damage than their numbers would otherwise allow.

\textbf{Alignment:} Always Evil. A majority of them are Chaotic Evil, but a few lean toward Neutral Evil or Lawful Evil.

\textbf{Starting Gold:} 4d6x10 gp (140 gold)

\textbf{Starting Age:} Complex

\textbf{Hit Die:} d8

\textbf{Class Skills:} The \currentclassname{}'s class skills are \linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Decipher Script} (Int), \linkskill{Heal} (Wis), \linkskill{Intimidate} (Cha), \linkskill{Listen} (Wis), \linkskill{Knowledge} (Int), \linkskill{Profession} (Wis), \linkskill{Spot} (Wis), and \linkskill{Spellcraft} (Int).

\textbf{Skills/Level:} 2 + Intelligence Bonus

\poorbab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{fullcastingclasstable}
\levelone{Rebuke Undead, Undead Minion					& 3 & 1 & - & - & - & - & - & - & - & -}
\leveltwo{ -											& 4 & 2 & - & - & - & - & - & - & - & -}
\levelthree{ -											& 4 & 2 & 1 & - & - & - & - & - & - & -}
\levelfour{ -											& 5 & 3 & 2 & - & - & - & - & - & - & -}
\levelfive{Master of the Dead							& 5 & 3 & 2 & 1 & - & - & - & - & - & -}
\levelsix{ -											& 5 & 3 & 3 & 2 & - & - & - & - & - & -}
\levelseven{ -											& 6 & 4 & 3 & 2 & 1 & - & - & - & - & -}
\leveleight{ -											& 6 & 4 & 3 & 3 & 2 & - & - & - & - & -}
\levelnine{ -											& 6 & 4 & 4 & 3 & 2 & 1 & - & - & - & -}
\levelten{Sustenance of the Dead 						& 6 & 4 & 4 & 3 & 3 & 2 & - & - & - & -}
\leveleleven{ -											& 6 & 5 & 4 & 4 & 3 & 2 & 1 & - & - & -}
\leveltwelve{ -											& 6 & 5 & 4 & 4 & 3 & 3 & 2 & - & - & -}
\levelthirteen{ -										& 6 & 5 & 5 & 4 & 4 & 3 & 2 & 1 & - & -}
\levelfourteen{ -										& 6 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & - & -}
\levelfifteen{Aspect of the Dead 						& 6 & 5 & 5 & 5 & 4 & 4 & 3 & 2 & 1 & -}
\levelsixteen{ -										& 6 & 5 & 5 & 5 & 5 & 4 & 4 & 3 & 2 & -}
\levelseventeen{ -										& 6 & 5 & 5 & 5 & 5 & 4 & 4 & 3 & 2 & 1}
\leveleighteen{ -										& 6 & 5 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2}
\levelnineteen{ -										& 6 & 5 & 5 & 5 & 5 & 5 & 4 & 4 & 3 & 3}
\leveltwenty{ -	 										& 6 & 5 & 5 & 5 & 5 & 5 & 4 & 4 & 4 & 4}
\end{fullcastingclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} \currentclassname{} are proficient with the club, crossbow (light and heavy), dagger, scimitar, scythe, sickle, and staff. and proficient with light armor but not with shields of any type

\textbf{Bonus Language:} The Death Master gains Abyssal as a bonus language. All of his spells, along with most Death Master tomes and manuals, appear in that tongue.

\textbf{Rebuke Undead:} As an emissary of Undeath, a Death Master has the power to compel undead to serve him. He channels fell energy and uses it to turn the living dead into his pawns. The Death Master can attempt to rebuke undead a number of times per day equal to 3 + his Charisma modifier. A Death Master with 5 or more ranks in Knowledge (Undead) gains a +2 bonus on rebuking checks against undead.

\textbf{Spells:} The Death Master's exhaustive study of necromantic magic grants him the ability to use arcane spells. The Death Master can cast the spells given on the Death Master spells list. He must choose and prepare his spells ahead of time, as a wizard. To learn, prepare, or cast a spell, a Death Master must have an Intelligence score equal to at least 10 + the spell's level. The DC for a saving throw against the Death Master's spells equals 10 + the spell's level + the Death Master's Intelligence modifier. The Death Master receives bonus spells for having a high Intelligence score. Similar to a wizard, the Death Master keeps a series of spellbooks in which he scribes the formulas for his spells. He must choose and prepare his spells by getting a good night's sleep and studying his books for 1 hour. While studying, the Death Master chooses the spells he wants to prepare.

The Death Master's spells have a special material component that makes them easier to cast in armor. If the Death Master uses a vial of blood as a material component he can cast the spell without somatic components and thereby ignore the spell failure chance for casting in armor. This blood must come from an intelligent creature (Intelligence 3 or higher) that the Death Master sacrificed to his God. The Death Master can extract 8 vials from a Medium creature. Double this for each size category above Medium and halve it, to a minimum of 1, for each category below. This extracted blood remains viable for one day, but a gentle repose spell prolongs this time.

\textbf{Spellbooks:} The Death Master keeps a set of unholy tomes that record the blasphemous, arcane methods for his spells. His spellbooks function in all ways as a wizard's spellbooks, including size, capacity, and cost to add spells.

\textbf{Undead Minion:} A Death Master gains the services of an undead creature bestowed unto him by his Undeath Master, typically a wolf skeleton or a zombie troglodyte. With your DM's permission you can gain the services of a different skeleton or zombie creature with a total, post-template CR of 1 or lower.

The Death Master's minion gains new abilities as he gains levels. A minion's abilities depend on the Death Master's total level in this class. The Death Master gains this minion from the great undead legions of his God. It obeys his commands without fail, and even takes suicidal actions. The minion is as much a spy for his God as a servant for the Death Master. If destroyed, a new minion appears 24 hours later. The Death Master can also choose to dismiss his minion to gain a new one. In this case, the Death Master must wait 24 hours for the new minion to appear.

A Death Master can choose to gain the services of a more powerful undead servitor at higher levels. Subtract the level modifier listed for a minion from the Death Master's level to determine the abilities and bonuses it gains. For example, an 11th-level Death Master with a ghast minion grants it benefits as a 2nd-level Death Master.

Any ability that give him a Undead Minion stacks with this.

\textbf{Master of the Dead (Su):} As a herald of Undeath, the Death Master is the unquestioned master of the living dead. An undead creature must make a Will save (DC 10 + half the Death Master's level + his Charisma modifier) in order to attack him in any way. If this save fails, the undead creature cannot take any aggressive action against the Death Master for 24 hours. If the undead creature succeeds in this save, it can act normally for 24 hours. After this time, it must save again.

While under the effects of this ability, an undead creature cannot take any direct action against the Death Master, but it could order its minions to attack, cast spells to boost its allies who can attack the Death Master, and so on.

Undead creatures that lack Intelligence scores automatically fail this save unless another creature controls them, such as a cleric who channels negative energy. In this case, the creature that controls the unintelligent undead makes a save on its behalf

\textbf{Sustenance of the Dead (Su):} A 10th-level Death Master gains power from the negative energy that infuses undead creatures. Once per round as a free action the Death Master can draw energy from a single undead creature he controls. The undead creature must be within 60 feet of the Death Master. When the Death Master user this power, he reduces the undead creature to a pile of dust and gains 2 temporary hit points per Hit Die of the undead creature. These temporary hit points fade after 1 hour.

An undead creature with an Intelligence score can make a Will save (DC 10 + half the Death Master's level + his Charisma modifier) to avoid destruction. If the save succeeds, the Death Master gains no temporary hit points. The undead creature survives and is no longer under the Death Master's control. The Death Master can attempt to rebuke the newly independent creature as normal.

Undead creatures that lack Intelligence scores gain no saving throw against this ability.

\textbf{Apsect of the Dead (Su):} At 15th level, the Death Master has proven himself as a mighty servant of his God. As a reward, the lord of undead grants him several of the defenses and abilities of the living dead. The Death Master gains Darkvision with a range of 60 feet, Immunity to all Mind-Sffecting Effects, and Immunity against Poison, Sleep Effects, Paralysis, Stunning, Disease, and Death Effects.

\vspace*{15pt}

\begin{smallbasictable}{Death Master's Undead Minion}{l l l l}
\textbf{Death Master's Caster Level} & \textbf{Bonus HD} & \textbf{Str/Dex Bonus} & \textbf{Special}\\
1-4 & +0 & +0 & Turn resistance +4\\
5-8 & +2 & +2 & Unholy might\\
9-12 & +4 & +4 & Persistent corruption\\
13-16 & +6 & +6 & Link of the grave\\
17-20 & +8 & +8 & Relentless undead\\
\end{smallbasictable}

\vspace*{15pt}

\textbf{Undead Minion Basics:} Use the base statistics for a creature of the minion's kind, as given in the Monster Manual, but make the following changes.

Bonus Hit Dice: The undead minion gains the listed bonus hit dice. Advance its saving throws, base attack bonus, and so forth as per the Monster Manual It does not increase in size due to these bonus HD.

Str/Dex Bonus: The minion gains the listed bonus to both its Strength and Dexterity scores.

\textbf{Special Abilities:} As the Death Master gains levels, his undead minion gains a number of special abilities.

Turn Resistance +4: The undead minion gains this turn resistance in addition to any turn resistance it normally gains.

Unholy Might: Once per day as a standard action, the Death Master can channel unholy energy into his minion to allow it to fight with increased vigor. The Death Master must touch the minion to imbue it with this power. The minion gains a +4 bonus to Strength and a +2 bonus on all saves for a number of rounds equal to 5 + the Death Masters Wisdom modifier. If the minion is a zombie, it loses the single actions only drawback for the duration of this ability.

Persistent Corruption: The Death Master of this level is such a favored apostle of Orcus that the lord of undead returns a destroyed minion to him shortly after its destruction. The Death Master must only wait 1 hour for a replacement undead minion if his is destroyed. He must still wait 24 hours for a replacement undead minion if he releases his current one.

Link of the Grave: Once per day as a free action, the Death Master can cast a shield other spell that links him to his minion. This spell has one critical difference from its normal form. Treat the Death Master as the spell's target and the minion as the caster. Thus, if the Death Master suffers damage he shares the total with his minion, but not vice versa.

Relentless Undead: The Death Master's minion gains fast healing 3.

\vspace*{15pt}

\begin{smallbasictable}{Alternative Undead Minions}{l l l l}
\textbf{4th Level (Level -3)} & \textbf{7th Level (Level -6)} & \textbf{10th Level (Level -9)} & \textbf{16th Level (Level -15)}\\
Bugbear Zombie & Ogre Zombie & Gray Render Zombie & Spectre\\
Ghoul & Wyvern Zombie & Wight &\cellcolor{white}\\
Owlbear Skeleton & \cellcolor{white} \textbf{10th Level (Level -9)} & \cellcolor{white} \textbf{13th Level (Level -12)} &\cellcolor{white}\\
\textbf{7th Level (Level -6)} & \cellcolor{offyellow} Allip & \cellcolor{offyellow} Cloud Giant Skeleton &\cellcolor{white}\\
Chimera Skeleton & \cellcolor{white} Ettin Skeleton & \cellcolor{white} Mummy &\cellcolor{white}\\
Minotaur Zombie & \cellcolor{offyellow} Ghast & \cellcolor{offyellow} Wraith &\cellcolor{white}\\
\end{smallbasictable}

