%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Shadow Warrior}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tagline{Do not fear the darkness …Fear what the darkness hides."}

\textbf{Alignment:} Any. Shadow Warriors fight for any and all reasons, tho very little of them are true neutral as many do have a reason for fighting.

\textbf{Starting Gold:} 4d4x10 gp (100 Gold)

\textbf{Starting Age:} Simple

\textbf{Hit Die:} d8

\textbf{Class Skills:} The\currentclassname{}'s class skills (and the key ability for each skill) are \linkskill{Appraise} (Int), \linkskill{Balance} (Dex), \linkskill{Bluff} (Cha), \linkskill{Climb} (Str), \linkskill{Concentration} (Con), \linkskill{Disable Device} (Int), \linkskill{Disguise} (Cha), \linkskill{Escape Artist} (Dex), \linkskill{Gather Information} (Cha), \linkskill{Hide} (Dex), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Knowledge} (Planes) (Int), \linkskill{Knowledge} (Religion) (Int), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Search} (Int), \linkskill{Sense Motive} (Wis), \linkskill{Sleight of Hand} (Dex), \linkskill{Spot} (Wis), \linkskill{Survival} (Wis), \linkskill{Swim} (Str), \linkskill{Tumble} (Dex), and \linkskill{Use Rope} (Dex).


\textbf{Skills/Level:} 6 + Intelligence Bonus

\goodbab{}
\poorfor{}
\goodref{}
\poorwil{}

\begin{classtable}
\levelone{Claws of Darkness, Shadow Shroud, See the Shadows}
\leveltwo{Shadowstep +10, Hide in Plain Sight}
\levelthree{Dark Weave}
\levelfour{Draining Strike}
\levelfive{Darkstalker}
\levelsix{Shadowy Appendages, Shadowstep +20}
\levelseven{Shadow Razors}
\leveleight{Reach of Darkness}
\levelnine{Shadow Movement}
\levelten{Strike the Soul}
\leveleleven{Shadow Mire, Shadowstep +30}
\leveltwelve{Shadow Magic}
\levelthirteen{Shadow Shift}
\levelfourteen{Numbing Strike}
\levelfifteen{Shadow Leap}
\levelsixteen{Shadow Spawn, Shadowstep +40}
\levelseventeen{Death Strike}
\leveleighteen{Servant of the Night}
\levelnineteen{Shadow Discorporation}
\leveltwenty{Shadow Well}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} \currentclassname{}s are proficient in all simple weapons. They are not proficient in any armours.

\textbf{Claws of Darkness (Su):} As a free action, a Shadow Warrior can weave shadows to form a pair of horrific claws for themselves. These claws are treated as any other natural weapons, deal damage as appropriate for a creature of the Shadow Warrior’s size (1d6 for Medium creatures), and have a critical threat range of 19-20. These claws strike as magical weapons, allowing them to bypass some damage reduction and to hurt incorporeal creatures (though they still suffer the 50\% miss chance). The claws can be dismissed as a free action, and last until dismissed.

\textbf{Shadow Shroud (Su):} A Shadow Warrior is surrounded by a cloak of darkness that offers them protection. The Shadow Shroud gives them an Armor bonus to AC equal to 4 plus half Shadow Warrior levels. As an armor bonus, this does not stack with any armor that they might wear. The Shadow Shroud absorbs the light around it, causing the area within 60 feet of the Shadow Warrior to be dim. This does not interfere with vision, but it does allow creatures with light blindness to function normally. Shadow Shroud also suppresses any Light effects within 60 feet of the Shadow Warrior, but stronger spells such as Daylight are not affected. This ability can be turned off and on as a free action.

\textbf{See the Shadows (Su):} A Shadow Warrior can see perfectly in darkness of any kind, even that created by the darkness or deeper darkness spells.

\textbf{Shadowstep (Su):} A 2nd level Shadow Warrior can move partially within the Plane of Shadow, which grants him a +10 bonus to his movement speed. He gains a further +10 bonus to movement at levels 6, 11, and 16.

\textbf{Hide in Plain Sight (Ex):} A 2nd level Shadow Warrior can hide even while being observed.

\textbf{Dark Weave (Sp):} A 3rd level Shadow Warrior can cast \linkspell{Darkness} at will as a spell-like ability, with a caster level equal to his Shadow Warrior level. Unlike the normal \linkspell{Darkness}, this ability does not actually shed light; it merely dims it to the level of shadowy illumination. If the area is already that dark, nothing happens.

\textbf{Draining Strike (Su):} The natural weapons of a 4th level Shadow Warrior deal an extra 1d6 points of negative energy damage. At level 9, this extra damage increases to 2d6.

\textbf{Darkstalker (Ex):} A 5th level Shadow Warrior is undetectable by sensory abilities such as Scent or Blindsight. A successful Listen or Spot check still detects him as normal. If you have Lords of Madness, then you can just give him \linkfeat{Darkstalker} as a bonus feat instead, since it does the same thing.

\textbf{Shadowy Appendages (Su):} A 6th level Shadow Warrior can grow a pair of shadowy tentacles as a free action. In all ways, these tentacles are like the Shadow Warrior's Claws of Darkness, except that they only threaten a critical hit on a roll of 20, and deal 1d8 points of damage as a Medium creature (plus half the Shadow Warrior's Strength bonus). The Shadow Warrior can grow a further pair of tentacles at level 11 and 16, for a total of 6 tentacles, with the same statistics as the first. These tentacles (the ones gained at levels 6, 11, and 16) are secondary natural attacks, and as such attacks with them are made at a -5 penalty.

\textbf{Shadow Razors (Ex):} At 7th level, the threat range of a Shadow Warrior's claws is doubled to 17-20, and the critical damage of his tentacles becomes x3. If the Shadow Warrior takes the Improved Critical feat for his claws, the threat range becomes 15-20.

\textbf{Reach of Darkness (Su):} At 8th level, a Shadow Warrior adds 5 feet to the reach of all his natural weapons (including Claws of Darkness and Shadowy Appendages). He can still attack adjacent targets with them.

\textbf{Shadow Movement (Su):} At 9th level, a Shadow Warrior can move through the Plane of Shadow with ease. He is no longer bounded by the gravity when in the transitive planes, which allows him to do things like walk on air or up walls.

\textbf{Strike the Soul (Su):} At 10th level, a Shadow Warrior's natural weapons automatically bypass hardness and damage reduction, and can strike incorporeal creatures as if they had the Ghost Touch property. Furthermore, the Shadow Warrior's natural weapons inflict energy drain, Fortitude save negates (DC 10 + half Shadow Warrior levels + Charisma). 

\textit{Energy Drain:} Any Living creatures hit by the Shadow Warrior's natural weapons attack gain one negative level.

Creatures killed by the Shadows Warrior's energy drain ability become Shadows. These Shadows are under the control of the Shadow Warrior, as are any spawn they create.

\textbf{Shadow Mire (Su):} At 11th level, a Shadow Warrior turns the air for 60 feet around him into seeping, watery shadow. Moving within this area costs ten feet of movement for every 5 feet that a creature wishes to move. The Shadow Warrior is immune to this effect, as are any creatures he wishes to exclude from it. This ability can be activated and deactivated as a free action.

\textbf{Shadow Magic (Ex):} At 12th level, a Shadow Warrior has tied himself so fully to the Plane of Shadow that he can access its power directly, rather than working through normal magic. None of his Supernatural or Spell-Like abilities can be dispelled or are suppressed in an anti-magic field, and he cannot be detected by magical means, such as scrying. Furthermore, he can cast \linkspell{Darklight} as a spell like ability at will with a caster level equal to his Shadow Warrior level. If you don't have access to the Spell Compendium, treat this as \linkspell{Darkness}, but giving 50\% concealment.

\textbf{Shadow Shift (Sp):} A 13th level Shadow Warrior can cast \linkspell{Greater Blink} and \linkspell{Shadow Walk} at will as spell-like abilities, with a caster
level equal to his Shadow Warrior level. However, \linkspell{Dreater Blink} shifts him to the Plane of Shadow instead of the Ethereal Plane, if that ever matters.

\textbf{Numbing Strike (Su):} At 14th level, a Shadow Warrior's natural weapons deal an extra 1d6 points of cold damage, and any creature
hit by him at least twice in one round must make a Will save or be \linkspell{Slowed}, as the spell (DC 10 + half Shadow Warrior levels + Charisma). A creature already slowed by this ability must make a further Fortitude save or be paralyzed for one round.

\textbf{Shadow Leap (Su):} At 15th level, a Shadow Warrior gains the ability to teleport through the shadows. As a swift action, he can instantly move up to his movement speed in any direction.

\textbf{Shadow Spawn (Su):} At 16th level, any creature slain by the Shadows Warrior's energy drain ability becomes a Greater Shadow instead of a Shadow. These Greater Shadows are under the control of the Shadow Warrior, as are any spawn they create.

\textbf{Death Strike (Su):} Any creature hit at least twice in a round by a 17th level Shadow Warrior's natural weapons must make a Fortitude save or die instantly (DC 10 + half Shadow Warrior levels + Charisma). Creatures immune to instant death or death effects, such as undead, can't be killed in this way.

\textbf{Servant of the Night:} An 18th level Shadow Warrior is accompanied by a loyal Nightwalker, which does as he commands. If killed, the Nightwalker reforms the next night. The Nightwalker advances as the Shadow Warrior does.

\textbf{Shadow Discorporation (Su):} As an immediate action, a 19th level Shadow Warrior can cause his body to collapse into a mass of shifting shadows. While in this form, he is unable to make any attacks, but cannot be harmed in any way. This ability lasts until the beginning of his next turn.

\textbf{Shadow Well (Su):} A 20th level Shadow Warrior's command over the shadows has grown to such a level as to allow him to assault his enemies with horrific tentacles of blackness. Any creature affected by his Shadow Mire ability is grappled by the tentacles, which are treated as a Huge creature with a grapple check of 32 + Shadow Warrior's Charisma bonus. The tentacles deal energy drain each round to every creature they successfully grapple.
