%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Mercenary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Mercenaries are individuals skilled in fighting, usually a Mercenary, who was paid to fight on behalf of an individual, group, country, organization, or other military force. Mercenaries are located all throughout Faerûn.

\textbf{Alignment:} Any. Mercenaries can and do fight for any cause, must for money but sometimes for ideology or other reasons only known to the Mercenary.

\textbf{Starting Gold:} 8d4x10gp (200 gold)

\textbf{Starting Age:} Moderate

\textbf{Hit Die:} d8

\textbf{Class Skills:} The \currentclassname{}'s class skills (and the key ability for each skill) are \linkskill{Balance} (Dex), \linkskill{Climb} (Str), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Disguise} (Cha), \linkskill{Gather Information} (Cha), \linkskill{Handle Animal} (Cha), \linkskill{Hide} (Dex), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Knowledge} (Int), \linkskill{Speak Language} (N/A), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Perform} (Cha), \linkskill{Profession} (Wis), \linkskill{Ride} (Dex), \linkskill{Search} (Int), \linkskill{Sense Motive} (Wis), \linkskill{Sleight of Hand} (Dex), \linkskill{Spot} (Wis), \linkskill{Survival} (Wis), \linkskill{Swim} (Str), \linkskill{Tumble} (Dex).

\textbf{Skills/Level:} 4 + Intelligence Bonus

\modebab{}
\goodfor{}
\poorref{}
\poorwil{}

\begin{extraclasstable}{\textbf{Maneuvers}}
\levelone{Stances, Mercenary Maneuvers, Secrets of Battle & 1}
\leveltwo{Hardened Survivor & 1}
\levelthree{Wearing Shoes& 2}
\levelfour{Lucky & 2}
\levelfive{Veteran's Experience & 3}
\levelsix{Leader of Men & 3}
\levelseven{Boots Keep Walking & 4}
\leveleight{ - & 4}
\levelnine{Boots Keep Walking & 5}
\levelten{Meet Interesting People & 5}
\leveleleven{Boots Keep Walking & 6}
\leveltwelve{ - & 6}
\levelthirteen{Boots Keep Walking & 7}
\levelfourteen{Logistics Master & 7}
\levelfifteen{Going Places & 8}
\levelsixteen{ - & 8}
\levelseventeen{Boots Keep Walking & 9}
\leveleighteen{Mass Desertion & 9}
\levelnineteen{Boots Keep Walking & 10}
\leveltwenty{ - & 10}
\end{extraclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} \currentclassname{}s is proficient with all simple and martial weapons, as well as the racial weapons for their race. \currentclassname{}s is proficient with Light, Medium, and Heavy Armor in addition to Shields and Great Shields.

\textbf{Mercenary Maneuvers (Ex):} As a Mercenary gains class levels they learn how to perform amazing maneuvers of daring-do and general badassery which are collectively called "Maneuvers." A Maneuver takes a Standard Action. Many of the Mercenary's Stances specifically impact the Mercenary's special Mercenary Maneuvers, and that refers to these and not just any attack action or full attack they happen to make. A Mercenary has an Initiator level equal to their class level. A Mercenary learns one maneuver each odd-numbered Mercenary level, but they can also abandon any number of maneuvers they already learned whenever they gain a level of any class and learn new maneuvers that they qualify for. Most Mercenary Maneuvers allow the character to make a standard attack modified in some fashion. If they are using a double weapon with which they are proficient or two finesseable weapons, they may instead make one standard attack with each weapon (adding only half their Strength bonus to the off-hand weapon), but any special maneuver effects that trigger on damage only trigger once if either or both attacks hit.

\textbf{Secrets of Battle (Ex):} A Mercenary adds their Intelligence Modifier (if positive) to their attack rolls, up to a maximum bonus equal to their Mercenary Level.

\textbf{Stances (Ex):} While the Mercenary is not flatfooted, they may engage a Stance at the cost of one Swift Action per round. Each Stance is usually based on the unique fighting techniques of one of the world's armies that the Mercenary has trained in, fought with, or researched. Each Stance is procedurally generated, allowing the character to gain the benefit of their Intelligence bonus to something they don't normally get to do. Each Stance also needs a name, which can be generated on the chart at the end of this section.

\textbf{Basic Bonuses:}
\begin{itemize*}
\item Add Intelligence Modifier to weapon damage.
\item Add Intelligence Modifier to Armor Class.
\item Add Intelligence Modifier to Saving Throws.
\item Add Intelligence Modifier to Strength and Dexterity based Skill Checks.
\item Gain Spell Resistance of 5 + Level + Intelligence Modifier.
\end{itemize*}

\textbf{Hardened Survivor (Ex):} A 2nd level Mercenary has resigned themselves to living in crappy conditions on both sides of a siege, and resigned themselves to eating things that a less martially oriented person would refuse out of hand. They may add their Constitution modifier to their \linkskill{Survival} checks instead of their Wisdom Modifier. They also add their \linkskill{Survival} ranks to the amount of negative health they can take before dying. (ie. 5 ranks in Survival means they die at -15 Hit Points)

\textbf{Wearing Shoes (Ex):} A 3rd level Mercenary understands how people thinks and what they find normal. The Mercenary gains a bonus to Disguise equal to their Intelligence Modifier, and suffers no penalty for disguising themselves as a different race.

\textbf{Lucky (Ex):} It's amazing how a lucky veteran keeps coming back from amazingly dangerous situations. A 4th level Mercenary gains a Luck bonus to their Saving Throws equal to their Constitution Modifier, to a maximum of their Class Level.

\textbf{Veteran's Experience (Ex):} A 5th level Mercenary has seen crazy crap and come out craftier for it. They gain an Enhancement bonus to their Intelligence equal to one third of their character level (round up).

\textbf{Leader of Men:} At 6th level, a Mercenary gains Command as a bonus feat. If they already have Command, they can take another [Leadership] Feat that they qualify for instead.

\textbf{Boots Keep Walking (Ex):} At level 7 and again at levels 9, 11, 13, 17 and 19 a Mercenary's experience fighting on the battlefields of the Heavy Metalish terrain that dots the landscape grants them special abilities related to that terrain experience. Every time the Mercenary gains one of these Terrain-based abilities they also gain a cumulative +1 bonus to all Survival tests as they are able to generalize their specific experiences into relevancies in other circumstances.

\textbf{Terrain Powers:}
\begin{description*}
\item[Cave Crawler:] The Mercenary suffers no penalty for squeezing. The Mercenary's movement speed is not reduced during poor visibility.
\item[Cliff Jumper:] The Mercenary gains a Climb Speed equal to half their land speed. The Mercenary ignores difficult terrain caused by uneven stone.
\item[Ice Skater:] The Mercenary gains Energy Resistance to Cold equal to their Character Level. They ignore the effects of any decreased temperatures.
\item[Inferno Commando:] The Mercenary gains Energy Resistance to Fire equal to their Character Level. They ignore the effects of any increased temperatures.
\item[Jungle Fighter:] The Mercenary can move through difficult terrain caused by vegetation as if it wasn't there, counts cover from vegetation as if it was one stage better in both directions (so 50\% cover would provide them a +6 AC bonus but only a +2 AC bonus to enemies), and does not take damage or get entangled from enchanted vegetation such as entangle or briar web.
\item[Planar Champion:] The Mercenary ignores Planar Traits that would suck for them such as "Lawfully Aligned" or "Prison Plane" - not the Gravity or Time traits.
\item[Swamp Beast:] The Mercenary is able to ignore difficult terrain that is caused by an area being water logged. Also they are immune to the nauseated condition.
\item[Waste Warrior:] The Mercenary takes twice as long to dehydrate and takes half damage from dessication effects. Also they take no damage from and their visibility is not impaired by dust storms, smoke clouds, ash rains, and any similar stuff.
\end{description*}

\textbf{Meet Interesting People (Ex):} At 10th level, the Mercenary add their Intelligence Modifier to Charisma skills; this does stacks with Wearing Shoes ability(ie. add Intelligence Modifier twice).

\textbf{Logistics Master (Ex):} A 14th level Mercenary is a master of War and can manage supply lines intuitively. The Mercenary can use their Survival skill to manage Logistics on any scale from the personal to the Imperial.

\textbf{Going Places (Sp):} A 15th level Mercenary can follow anything to anywhere. By touching something from another plane, they may \linkspell{Planeshift} to the plane of the creature or object's origin. Since it is easy to touch yourself, a Mercenary can always return to their own plane of origin. This can also be used to banish things to their home plane of existence, if they fail a Will Save.

\textbf{Mass Desertion (Ex):} An 18th level Mercenary is a dreaded thing. When he takes to the field, enemies know their cause is hopeless. Enemies of CR 8 or less who see the Mercenary in the fray simply give up. They retreat or surrender as appropriate. This is not a fear effect, and extends to line of sight.

%%%
\subsubsection{Mercenary Maneuvers}
%%%

In order to take a specific Strike you must have an Initiator Level sufficient to use it. If there is a Save offered by a Mercenary Strike, the DC is 10 + half Character Level + Constitution Modifier.

\newcommand{\mercenarymaneuver}[3]{\textbf{#1} [Level #2] #3\medskip{}}

\mercenarymaneuver{Brutal Strike}{1}{The Mercenary hits someone super hard with a melee attack. The attack does an extra d6 of damage. This bonus increases to 2d6 at 3rd level, 3d6 at 4th level, 4d6 at 6th level, 5d6 at 7th level, 7d6 at 8th level, 9d6 at 9th level, 11d6 at 10th level, 14d6 at 11th level, 16d6 at 12th level, 20d6 at 13th level, 100 points at 14th level, 110 points at 15th level, 125 points at 16th level, 150 points at 17th level, 175 points at 18th level, 200 points at 19th level, and 250 points of damage at 20th level.}

\mercenarymaneuver{Turtle World}{1}{The Mercenary attacks normally but hides themselves from harm. The Solider makes a standard attack and has energy resistance to all energy types and DR/- equal to their Constitution Modifier plus their Character level until the beginning of their next turn if the attack inflicts damage.}

\mercenarymaneuver{Looting Strike}{1}{The Mercenary stabs a fool and pockets their things. The Mercenary makes a standard melee attack and if it inflicts damage they can force the target to drop a weapon or other carried item. The Mercenary can grab and store that item if they wish.}

\mercenarymaneuver{Blinding Blow}{3}{The Mercenary strikes a foe in their eyes or whatever they see with. Thy make a standard attack and if they inflict damage the target must make a Fortitude Save or be blinded.}

\mercenarymaneuver{Runaround}{3}{The Mercenary runs around and stabs someone from an unconventional direction. The Mercenary moves their speed and then makes a standard melee attack at +2 to-hit. The Mercenary gains a +2 bonus to AC until the beginning of their next turn.}

\mercenarymaneuver{Knockdown}{3}{The Mercenary strikes someone in a manner that knocks them right down. The Mercenary makes a standard attack and if it inflicts damage, the target becomes prone.}

\mercenarymaneuver{Whirlwind}{5}{The Mercenary flips out and stabs everyone. The Mercenary makes a standard melee attack against every opponent they can reach. They may gain no more bonus cleave attacks than they have Intelligence Modifier.}

\mercenarymaneuver{Executioner}{5}{The Mercenary chops a dude's head right off and spits down the hole in the stump. The Mercenary makes a standard melee attack and if he does any damage the target makes a Fortitude Save or they die.}

\mercenarymaneuver{Delaying Tactics}{5}{The Mercenary feints and draws things out, unraveling time. The Mercenary makes a standard attack. Every creature adjacent to the Mercenary is slowed for Level/Rounds.}

\mercenarymaneuver{Mind Thwack}{7}{The Mercenary beats someone in the brain so hard that it creates a psychic resonance the incapacitates others. The Mercenary makes a standard attack against a living, non-mindless creature and if he does any damage, all creatures except the Mercenary within 10' of the target must make a Will save or be stunned for a d4 rounds.}

\mercenarymaneuver{Lingering Strike}{7}{The Mercenary hits the target with a cruel and lingering wound that disrupts their concentration. The Mercenary makes a standard attack. The attack does double damage, and is considered to be ongoing damage for purposes of Concentration checks made in the following round.}

\mercenarymaneuver{Hurl Away}{7}{The Mercenary strikes an opponent and hurls them away from themselves. The Mercenary makes a standard melee attack, and if it does any damage the target is also pushed away 5' for every point of Constition bonus the Mercenary has. This works like a successful Bullrush except that the Mercenary doesn't need to move to keep the victim moving.}

\mercenarymaneuver{Dimensional Strike}{9}{The Mercenary reaches into the ether and tears the target a new one. The Mercenary sees the invisible and then makes a standard attack that ignore Incorporeality and can strike Ethereal creatures. If the attack does any damage, the target is moved to the plane of existence that the Mercenary is on and is no longer incorporeal for the next 2d4 rounds.}

\mercenarymaneuver{Meteor Smash}{9}{The Mercenary strikes the ground so hard that everything just fucking explodes. All other creatures within 30' suffer d8/level of physical bludgeoning damage, Reflex Save for half.}

\mercenarymaneuver{Demoralizing Strike}{9}{The Mercenary hits a target so ugly that it freaks out all of their allies. If the target takes any damage they are sickened for the next minute. All enemies within line of sight must make a Will save or become shakened for one round.}

\mercenarymaneuver{Critical Strike}{11}{The Mercenary strikes an opponent perfectly. The Mercenary makes a standard attack, and if it hits it is a critical as if it had rolled a natural 20 and then confirmed.}

\mercenarymaneuver{Hydra Strike}{11}{The Mercenary makes a flurry of attacks. The character makes a number of standard attacks equal to their Intelligence Modifier. These don't even have to be against the same target. Every time they get a critical hit, they get an additional attack.}

\mercenarymaneuver{Blade Rush}{11}{The Mercenary runs around his opponents and jacks them up. The Mercenary moves their full move without provoking attacks of opportunity and makes a standard melee attack against every opponent who is within their threatened area at any point during their move. Each attack inflicts bonus damage equal to the maximum damage inflicted by the weapon's damage die (for example: 8 damage for a longsword or kriegsmesser). The character cannot gain bonus attacks from Cleave during this maneuver.}

\mercenarymaneuver{Doom Tunnel}{13}{The Mercenary hacks a corridor through whatever happens to be in front of him, whether that be air, rock or other people. He may move out to his full charge range and attack everyone who is in his path. If he fails to kill a target, they are shoved aside so he can keep moving. Any nonliving thing in the path is Disintegrated, as per the spell.}

\mercenarymaneuver{Heaven Piercer}{13}{The Mercenary stabs the sky hard enough to split it open and cause death to rain down upon everyone around. This requires line of sight to the sky, and causes all within 50 feet to take 1d8 Electricity damage per level (Reflex half). Additionally, the general other-dimensional doom raining down pushes creatures over, negates ranged attacks, and impedes flight within 50' of the Mercenary until his next turn as per a Hurricane-Force Wind. In some planes of existence, a wounded sky may leak damage types other than lightning, such as fire or acid.}

\mercenarymaneuver{Earth Shaker}{13}{The Mercenary strikes the ground and the ground strikes everyone else. All other creatures touching the ground within 60' of the Mercenary take 1d8 of Bludgeoning damage per level (Fortitude Half). Those creatures that fail their saves are also partially buried in dirt. They are prone and entangled until they can make an Escape Artist or Size Modified Strength test with a DC of 15 + the Mercenary's Constitution modifier as a Full Round Action (or burrow or teleport out).}

\mercenarymaneuver{Banishing Strike}{15}{The Mercenary smashes the target out of existence. The Mercenary makes a standard attack, and if the target suffers any damage it is sent to its home plane, where it is then dimensional anchored for a day. The Mercenary may travel with the target if they choose.}

\mercenarymaneuver{Harrying Strike}{15}{The Mercenary may take a 5' step that teleports to a space adjacent to a creature that was within short range of the Mercenary last turn. The Mercenary need not know where the target has gone since then, and can follow any distance to any plane of existence without fail. The Mercenary then makes a standard attack.}

\mercenarymaneuver{Hamster Strike}{15}{The Mercenary strikes the target in such a manner that they become a small rodent. The Mercenary makes a standard attack, and if any damage is inflicted, the target is now a harmless hamster, as per baleful polymorph. Some Mercenaries learn similar attacks that transform the target into other things.}

\mercenarymaneuver{Perfect Killer}{17}{The Mercenary strikes an enemy and they die. The Mercenary makes a standard attack against a target, if the target suffers any damage it dies. This is a [Death] effect.}

\mercenarymaneuver{Extra Strike}{17}{The Mercenary makes a standard attack as a free action. This may be used once per round, and may be used on other creatures' initiative counts.}

\mercenarymaneuver{World Slaying Strike}{17}{The Mercenary attacks every creature they can see. The Mercenary makes a standard attack, and this attack is resolved against every target they choose to designate out to line of sight. Make one attack roll and compare to each target's AC, but if miss chances apply, roll for each separately.}

%%%
\subsubsection{Naming Your Stances}
%%%

When you name your styles, be sure to have the representative species name in there somewhere, and also generate an adjective and a noun to name the stance. The racial word can go in the first, second, or third position depending on what sounds better. So when making a Drow style, you could have the "Underhanded Grandeur of the Drow" or the "Drow Invincible Method" or the "Informal Drow Approach".

\vspace*{15pt}

\begin{basictable}{Random Mercenary Stance Names}{l l l l l l}
\textbf{Roll or Choose} & \textbf{Adjective} & \textbf{Noun} & \textbf{Roll or Choose} & \textbf{Adjective} & \textbf{Noun}\\
1 & Rising & Stance & 11 & Awesome & Maneuver\\
2 & Sweltering & Dance & 12 & Splendid & Pattern\\
3 & Sneaky & Technique & 13 & Informal & Mode\\
4 & Underhanded & Style & 14 & Shadow & Method\\
5 & Virtuous & Grandeur & 15 & Sexy & Mean\\
6 & Wonderful & Defense & 16 & Impenetrable & System\\
7 & Glorious & Manner & 17 & Invincible & Way\\
8 & Fantastic & Attack & 18 & Inflammable & Approach\\
9 & Dark & Idiosyncrasy & 19 & Sordid & Attitude\\
10 & Wicked & Tactic & 20 & Wrathful & Craft\\
\end{basictable}