%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Kobold}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Kobolds are often characterized as filthy little reptiles barely better than goblins. They’re malicious but of little actual menace. Catch kobolds in their lairs, where they are almost certainly hard at work mining, and such a description might be fitting. No one ever suspected that being underestimated was the kobolds’ goal.

Kobolds are meticulous creatures with sorcery in their blood, a variety of reptile with a strong work ethic. Discounted as pests or worse by many others, kobolds are a long-suffering race with many talents and clever tricks. Only the foolish overlook the threat that kobolds actually pose.

\begin{multicols}{2}

\begin{itemize*}
\item Small size
\item 30ft movement.
\item Humanoid Type (Dragonblood and Reptilian subtype)
\item Darkvision 60ft
\item -4 Strength, +2 Dexterity, -2 Constitution
\item All kobolds add \linkskill{Craft} (trapmaking) to their list of class skills
\item +2 racial bonus on \linkskill{Craft} (Trapmaking), \linkskill{Profession} (Miner), and \linkskill{Search} checks.
\item +1 Natural Armor bonus.
\item Daylight Sensitivity: While in brightly lit surroundings (such as a \linkspell{daylight} spell), a Kobold suffers a -2 penalty to attack rolls and precision-based skill checks.
\item Alignment: Usually lawful evil
\item Favored Classes: \linkclass{Sorcerer} and \linkclass{Rogue}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
6 & +1d3 & +1d4 & +2d4\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
2'1'' & 1'10'' & \multicolumn{2}{c}{+2d4}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 40 lb. & \cellcolor{white} 30 lb. & \multicolumn{2}{c}{\cellcolor{white} X 1 lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Kobold Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Clan & Draconic(Yipyak) & \multicolumn{1}{p{5cm}}{\raggedright{}Elven, Dwarven, Gnome, Goblin, Terran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Daylight Adaptation}, \linkfeat{Dragonwrought}, \linkfeat{Oral History}}\\
\end{smallbasictable}

\pagebreak