%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Half-Illithid}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Half-Illithids are the progeny of mind flayers and various other creatures. Most often, such progeny are formed through magical tampering with the reproductive process of the host creature, rather than through direct mating.

\textbf{Alignment:} Always Evil.

\textbf{Hit Die:} d8

\textbf{Class Skills:} The \currentclassname{} can choose any five skills to be class skills.

\textbf{Skills/Level:} 2 + Intelligence Bonus

\modebab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{classtable}
\levelone{\multicolumn{1}{p{6.5cm}}{\raggedright +2 Wisdom, +2 Charisma, Natural Armor +1, Extract, Psionics}}
\leveltwo{\multicolumn{1}{p{6.5cm}}{\raggedright +2 Intelligence +2 Wisdom, Improved Grab, Psionics, Spell Resistance}}
\levelthree{\multicolumn{1}{p{6.5cm}}{\raggedright +2 Intelligence, +2 Charisma, Mind Blast, Psionics, Spell Resistance, Tentacle Attack}}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} A Half-Illithid gains no proficiency any arms or armours.

\textbf{Ability Score:} All ability score change are inherit bonus. Half-Illithid gains +2 Wisdom, +2 Charisma at 1st level, +2 Intelligence +2 Wisdom at 2nd level, and at 3rd level +2 Intelligence, +2 Charisma.
 
\textbf{Natural Armor Bonus (Ex):} At 1st level, a Half-Illithid gains Natural Armor Bonus of +1.
 
 \textbf{Extract (Ex):} At 1st level a Half-Illithid that begins its turn with all four tentacles attached and wins a grapple check automatically extracts the opponent’s brain, instantly killing that creature.
 
This power is useless against constructs, elementals, oozes, plants, and undead. Extraction is not instantly fatal to foes with multiple heads, such as ettins and hydras.

A Half-Illithid can grab a Huge or larger creature, but only if it can somehow reach the foe’s head. If a Half-Illithid begins its turn with at least one tentacle attached, it can try to attach its remaining tentacles with a single grapple check. The opponent can escape with a single successful grapple check or an Escape Artist check, but the Half-Illithid gets a +2 circumstance bonus for every tentacle that was attached at the beginning of the opponent’s turn.

\textbf{Psionics (Sp):} A Half-Illithid with an Intelligence or Wisdom score of 8 or higher after the ability score adjustments noted below possesses the psionic abilities as given below. Caster level 8th; save DC 10 + spell level + Cha modifier.

\begin{multicolsbasictable}{c*{2}{c}}

\textbf{Paragon Level} & \textbf{Psionic Abilities}\\
1st & \linkspell{Detect thoughts} 3/day, and \linkspell{Suggestion} 1/day\\
2nd & \linkspell{Levitate} 1/day, and \linkspell{Suggestion} 3/day\\
3rd & \linkspell{Levitate} 3/day, and \linkspell{Charm Monster} 1/day\\
\end{multicolsbasictable}

\textbf{Spell Resistance (Ex):} At 2nd Level a Half-Illithid gains Spell Resistance 5, and 10 Spell Resistancre at 3rd Level.

\textbf{Improved Grab (Ex):} 2nd Level Half-Illithid gains Improved Grab, to use this ability, a Half-Illithid must hit a Small, Medium, or Large creature with its tentacle attack. It can then attempt to start a grapple as a free action without provoking an attack of opportunity. If it wins the grapple check, it establishes a hold and attaches the tentacle to the opponent’s head.

\setlength{\intextsep}{-5pt}
\begin{wraptable}{O}{2in}
\rowcolors{1}{white}{offyellow}
\begin{tabular}{c c}
\multicolumn{2}{c}{\textbf{Tentacle Damage by Size}}\\
Tiny & 1d2\\
Small & 1d3\\
Medium & 1d4\\
Large & 1d6\\
Huge & 1d8\\
\end{tabular}
\end{wraptable}

\textbf{Mind Blast (Sp):} 3rd level Half-Illithids can Mind Blast once per day, a Half-Illithid can produce a Mind Blast in a cone 40 feet long. Anyone caught in this area must succeed on a Will save (DC 10 + 1/2 Half-Illithid’s Hit Dice + Cha modifier) or be stunned for 1d4 rounds. This ability is the equivalent of a 4th-level spell.

\textbf{Tentacle Attack:} At 3rd Level the Half-Illithid's Tentacle Attack increase Damage by one size.





