%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Highborn Drow}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Only about one out of 20 drow are gifted with special powers, overwhelming majority of these exceptional drow are female, and as a result, drow society tends to be matriarchal in nature.

\textbf{Alignment:} Usually evil

\textbf{Hit Die:} d6

\textbf{Class Skills:} The \currentclassname{} can choose any five skills to be class skills.

\textbf{Skills/Level:} 2 + Intelligence Bonus

\modebab{}
\poorfor{}
\goodref{}
\poorwil{}

\begin{classtable}
\levelone{Darkvision 120ft, Spell-like Abilites, +2 Intelligence}
\leveltwo{Spell Resistance,  Spell-like Abilites}
\levelthree{Spell Resistance, +2 Charisma}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} A Highborn Drow gains no armor or weapon proficiencys.

\textbf{Ability Score:} A Highborn Drow get a +2 Intelligence at 1st level and +2 Charisma at 3rd level.

\textbf{Darkvision:} At 1st level a Highborn Drow get \linkability{Darkvision} 120ft.

\textbf{Spell Resistance:} A Highborn Drow has spell resistance equal to 5 + hit dices at 2nd level, and 11 + hit dices at 3rd level.

\begin{multicolsbasictable}{c*{2}{c}}

\textbf{Paragon Level} & \textbf{Spell-like Abilities}\\
1st & \linkspell{Darkness} 1/day, and \linkspell{Detect Magic} 1/day\\
2nd & \linkspell{Detect Good} 1/day, and \linkspell{Levitate} 1/day\\
\end{multicolsbasictable}

\textbf{Spell-like Abilites:} At 1st Level, a Highborn Drow gets \linkspell{Darkness}, and \linkspell{Detect Magic} as spell-like abilites using hit dices at caster level.

At 2nd Level, a Highborn Drow gets \linkspell{Detect Good}, and \linkspell{Detect Magic} as spell-like abilites using hit dices at caster level.


