%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Kuo-Toa}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Kuo-toa (meaning "original masters" in their native tongue) were a debased, piscine race of warm-blooded and amphibious creatures that dwelt in the Underdark. Sinister secrets lurked below the surface of their alien minds, for the kuo-toa were fanatics plagued by mental instability that saw things others couldn't and worshiped gods that didn't exist — at least until they believed hard enough.

\textbf{Alignment:} Often Neutral Evil

\textbf{Hit Die:} d8

\textbf{Class Skills:} The \currentclassname{} can choose any five skills to be class skills.

\textbf{Skills/Level:} 2 + Intelligence Bonus

\goodbab{}
\poorfor{}
\goodref{}
\goodwil{}

\begin{classtable}
\levelone{\multicolumn{1}{p{6.5cm}}{\raggedright +2 Intelligence +2 Wisdom, Electricity Resistance 5, Natural Armor +4}}
\leveltwo{\multicolumn{1}{p{6.5cm}}{\raggedright +2 Strength, +2 Constitution, Electricity Resistance 10, Natural Armor +6, Lightning Bolt}}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} A Kuo-Toa gains proficiency with Light Armor and Simple Weapons. A kuo-toa also may treat pincer staffs as martial weapons rather than exotic weapons.

\textbf{Ability Score:} Kuo-toas are strong, hardy, and wise, but they have a sinister reputation. All ability score change are inherit bonus.
 
 \textbf{Electricity Resistance(Ex):} At 1st level, a Kuo-Toa gains Resistance to Electricity 5; The Resistance increases to 10 at 2nd Level.
 
 \textbf{Natural Armor Bonus (Ex):} At 1st level, a Kuo-Toa gains Natural Armor Bonus of +4, and +6 at 2nd.
 
\textbf{Lightning Bolt (Su):} At 2nd Level, Two or more kuo-toa clerics (whips) with this ability can operating together can generate a stroke of lightning every 1d4 rounds. The whips must join hands to launch the bolt but need only remain within 30 feet of one another while it builds. The resulting lightning bolt deals 1d6 points of damage per whip, but a successful Reflex save halves this amount (DC 11 + highest Wisdom modifier among the participating whips + number of whips).