%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Urdunnir}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Urdunnirs see the world as a work of living beauty, walking through stone and earth much as a diver might explore the wonders of the ocean depths. The Children of Dumathoin regard themselves as particularly blessed, for they are not forced to cling to the exterior of Dumathoin’s creation like other races but can wander through the heart of the world itself in an endless search to uncover the Silent Keeper’s hidden secrets (gems).

\textbf{Alignment:} Usually Neutral

\textbf{Hit Die:} d6

\textbf{Class Skills:} The Urdunnir can choose any five skills to be class skills.

\textbf{Skills/Level:} 2 + Intelligence Bonus

\modebab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{classtable}
\levelone{Stone Walk}
\leveltwo{Stone Shape}
\levelthree{Shape Metal}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} A Urdunnir gains no armor or weapon proficiencys.

\textbf{Stone Walk (Su):} At 1st level an Urdunnirs can pass through stone and earth as if it were air. They can carry up to twice their own body weight with them in this manner. Urdunnirs (and anyone carried with them) cannot breathe while within stone or earth and must hold their breath while traveling in this manner.

\textbf{Stone Shape (Sp):} At level 2 an Urdunnir gain \linkspell{Stone Shape} at will as an 8th-level sorcerer.

\textbf{Shape Metal (Sp):} At 3rd level an Urdunnir gain Shape Metal as a spell-like ablility as an 8th-level sorcerer once per round. This power works just like the \linkspell{Shape Metal} spell, except that urdunnirs can only affect 5 cubic feet of metal. Using this ability is a full-round action.