%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Werecat}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Werecats can take three different forms: Human Form, Cat Form, and Hybrid Form. In their Human Form, they are sensuous, slender and hedonistic. In their Cat Form, Werecats take the guise of common House Cats. Their Hybrid Form appears as Humanoid with fur, Cat's face or other feline features.

Werecats are often lithe and self-indulgent. They pass on the Gift of Ailuranthropy by biting foes. These shapechangers liked to communicate with cats, dire cats, and even Big cats such as lions. Being adept in charming, bluffing and disguising are something Werecats greatly take advantage of.

\textbf{Alignment:} Usually Chaotic Good.

\textbf{Hit Die:} d8

\textbf{Class Skills:} The \currentclassname{} can choose any ten skills to be class skills.

\textbf{Skills/Level:} 4 + Intelligence Bonus

\poorbab{}
\poorfor{}
\goodref{}
\poorwil{}

\begin{classtable}
\levelone{\multicolumn{1}{p{10cm}}{\raggedright{}DR 5/Silver, \linkability{Alternate Form} (Hybrid Form), \linkability{Low-Light Vision}, \linkfeat{Stealthy}, \linkfeat{Weapon Finesse}}}
\leveltwo{Gift of Ailuranthropy, +2 Wisdom, Natural Armor +1, \linkability{Scent}}
\levelthree{DR 10/Silver, \linkability{Alternate Form} (Cat Form),  Natural Armor +2}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} \currentclassname{}s are not proficient with any weapons or armor.

\textbf{Spells:} \currentclassname{} levels are added to one of your major spell casting class, for caster level; If two or more spell casting class you choose what class but must be the same class for all \currentclassname{} levels; If a minor spell casting class was choosen (ie. \linkclass{Ranger}/\linkclass{Paladin}) and you multiclass in \linkclass{Druid} or \linkclass{Cleric} the \currentclassname{} levels will move to the major of the minor you had choosen.

\textbf{\linkability{Damage Reduction} X/Silver (Ex):} At 1st and 3rd level, a Werecat gets \linkability{Damage Reduction} 5/Silver at 1st and 10/Silver at 3rd, when in Hybrid or Cat Form.

\setlength{\intextsep}{-5pt}
\begin{wraptable}{O}{2in}
\rowcolors{1}{white}{offyellow}
\begin{tabular}{c c c c}
Size & Claw & \& & Bite\\
Tiny & 1d2 && 1d3\\
Small & 1d3 && 1d4\\
Medium & 1d4 && 1d6\\
Large & 1d6 && 1d8\\
Huge & 2d4 && 2d6\\
\end{tabular}
\end{wraptable}

\textbf{\linkability{Alternate Form} (Su):} At 1st and 3rd level, a Werecat can alternate their form to a Hybrid Cat Form and a Cat Form. Changing to or from Cat or Hybrid Form is a standard action. They cannot cast spells with verbal, somatic, or material components while in Cat Form, or spells with verbal components while in Hybrid Form

\textit{Hybrid Form} is a mix of their Humanoid and Cat Forms, which in they are still the same size as their Humanoid form. In Hybrid Form they receives -4 Str, +6 Dex, +2 Con, Two Claws, and a Bite attack.

\textit{Cat Form} looks like a normal House Cat, but is one size category below thier normal one. In Cat Form they receives -4 Str, +6 Dex, +2 Con, +10 base land speed, Two Claws, and a Bite attack.

A slain Werecat reverts to its humanoid form, although it remains dead. Separated body parts retain their animal form, however.

\textbf{Low-Light Vision (Ex):} At level 1 a Werecat gets \linkability{Low-Light Vision} in all of their forms.

\textbf{+2 Wisdom:} At Level 2 the Werecat receives +2 Wisdom as a Inherit Bonus in all Forms.

\textbf{Natural Armor:} A 2nd and 3rd level, a Werecat grans a Natural Armor Bonus of +1 at 2nd and +2 at 3rd with in Hybrid or Cat Form. The Bonus stacks with any Inherit Natural Armor Bonus they may have.

\textbf{Gift of Ailuranthropy (Su):} At 2nd level a Werecat can spread the Gift of Ailuranthropy or Gift of the Catfolk. Any Humanoid or Giant hit by their Bite attack must make Fortitude Save (DC 10 +1/Werecat Level + Werecat Wis Modifier) or contract Ailuranthropy.

Any Ailuranthropes (Werecats) who has not took levels in Werecat changes form on every full moon, in which they are not aware of what happenes intill dawn back in Humanoid Form. They may make a DC 25 Will Save to keep awareness during the events but may not want to and can choose to voluntarily fail the save. Note with a successful save they still do not have control of themself, only aware of what they are doing, and may affect their alignment. GM should follow Chaotic Good for their envets.

\textbf{Scent (Ex):}  At level 2 a Werecat gets \linkability{Scent} in all forms.

A Werecat can detect opponets by sense of smell, within 30ft. Strong scents, such as smoke or rotting garbage, can be detected at 60ft, and Overpowering Scents, such as skunk musk or troglodyte stench, at 90ft.

The creature detects another creature’s presence but not its specific location. Noting the direction of the scent is a move action. If it moves within 5 feet of the scent’s source, the creature can pinpoint that source.

A creature with the \linkfeat{Track} feat and the Scent ability can follow tracks by smell, making a Wisdom check to find or follow a track. The typical DC for a fresh trail is 10. The DC increases or decreases depending on how strong the quarry’s odor is, the number of creatures, and the age of the trail. For each hour that the trail is cold, the DC increases by 2. The ability otherwise follows the rules for the \linkfeat{Track} feat. Creatures tracking by scent ignore the effects of surface conditions and poor visibility.

Water, particularly running water, ruins a trail for air-breathing creatures. Water-breathing creatures that have the scent ability, however, can use it in the water easily.

False, powerful odors can easily mask other scents. The presence of such an odor completely spoils the ability to properly detect or identify creatures, and the base Survival DC to track becomes 20 rather than 10.																							