%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Classes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\section{Core Classes}
%%%

\input{classes/classes-pc/core-classes/assassin}
\pagebreak
\input{classes/classes-pc/core-classes/barbarian}
\pagebreak
\input{classes/classes-pc/core-classes/bard}
\pagebreak
\input{classes/classes-pc/core-classes/cleric}
\pagebreak
\input{classes/classes-pc/core-classes/druid}
\pagebreak
\input{classes/classes-pc/core-classes/fighter}
\pagebreak
\input{classes/classes-pc/core-classes/knight}
\pagebreak
\input{classes/classes-pc/core-classes/monk}
\pagebreak
\input{classes/classes-pc/core-classes/paladin}
\pagebreak
\input{classes/classes-pc/core-classes/ranger}
\pagebreak
\input{classes/classes-pc/core-classes/rogue}
\pagebreak
\input{classes/classes-pc/core-classes/samurai}
\pagebreak
\input{classes/classes-pc/core-classes/sorcerer}
\pagebreak
\input{classes/classes-pc/core-classes/wizard}
\pagebreak

%%%
\section{Additional PC Classes}
%%%

\input{classes/classes-pc/additional-pc-classes/blackguard}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/crusader}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/death-master}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/dragonfire-adept}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/fire-mage}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/jester}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/marshall}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/monster-tamer}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/soldier}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/soulborn}
\pagebreak
\input{classes/classes-pc/additional-pc-classes/spirit-shaman}
\pagebreak
%\input{classes/classes-pc/additional-pc-classes/thief-acrobat}
%\pagebreak
%\input{classes/classes-pc/additional-pc-classes/totemist}
%\pagebreak
\input{classes/classes-pc/additional-pc-classes/warlock}
\pagebreak


%%%
\section{Monster Classes}
%%%

\input{classes/monster-classes/Slaymate}
\pagebreak

%%%
\section{Spellcasting Prestige Classes}
%%%

\input{classes/prestige-classes/spellcasting-classes/heartless-mage}
\pagebreak
\input{classes/prestige-classes/spellcasting-classes/lich}
\pagebreak
\input{classes/prestige-classes/spellcasting-classes/master-specialist}
\pagebreak
\input{classes/prestige-classes/spellcasting-classes/master-transmogrifist}
\pagebreak
\input{classes/prestige-classes/spellcasting-classes/pale-master}
\pagebreak

%%%
\section{Martial Prestige Classes}
%%%
\input{classes/prestige-classes/martial-classes/death-knight}
\pagebreak

%%%
\section{Racial Prestige Classes}
%%%
\input{classes/prestige-classes/racial-classes/yathrinshee}
\pagebreak

%%%
\section{Paragon Classes}
%%%

Racial paragons are, as their name suggests, nearly ideal examples of the strengths and abilities of the character’s race. Unlike members of other classes, however, racial paragons are more than merely powerful individuals. They are strong in all the ways that their race is strong, while still vulnerable in the ways that their race is vulnerable. Beyond that, they possess powers or capabilities that supersede those of normal members of their race. Obviously, a character can only take levels in a paragon class associated with his race.

Paragon Class Levels can be added to Caster Level for all Spellcasting Classes she takes.

Unlike standard character classes, paragon classes have prerequisites of being a member of the appropriate race.

Needing to be at least level 3 for 1st level of paragon, 6th for 2nd level of paragon, 9th for 3rd level of paragon.

\input{classes/paragon-classess/half-illithid}
\pagebreak
\input{classes/paragon-classess/highborn-drow}
\pagebreak
\input{classes/paragon-classess/kuo-toa}
\pagebreak
\input{classes/paragon-classess/Urdunnir}
\pagebreak
\input{classes/paragon-classess/werecat}
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multiclass Characters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A character may add new classes as he or she progresses in level, thus becoming 
a multiclass character. The class abilities from a character's different classes 
combine to determine a multiclass character's overall abilities. Multiclassing 
improves a character's versatility at the expense of focus.



%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Class And Level Features}
%%%%%%%%%%%%%%%%%%%%%%%%%

As a general rule, the abilities of a multiclass character are the sum of the abilities 
of each of the character's classes.

\textbf{\gameterm{Level}:} "\gameterm{Character Level}" is a character's total number of levels. It is used to determine when feats and ability score boosts are gained.

"\gameterm{Class Level}" is a character's level in a particular class. For a character whose levels are all in the same class, character level and class level are the same.

\textbf{\gameterm{Hit Points}:} A character gains hit points from each class as his or her class level increases, adding the new hit points to the previous total. 

\textbf{\gameterm{Base Attack Bonus}:} Add the base attack bonuses acquired for each class to get the character's base attack bonus. A resulting value of +6 or higher provides the character with multiple attacks. 

\textbf{\gameterm{Saving Throws}:} You keep any good base saves from all your classes, ie. you start as a \linkclass{Fighter}, and multiclass into \linkclass{Wizard} you gain good Will and good Fort saves.

\textbf{\gameterm{Skills}:} If a skill is a class skill for any of a multiclass character's classes, then character level determines a skill's maximum rank. (The maximum rank for a class skill is 3 + character level.)

If a skill is not a class skill for any of a multiclass character's classes, the maximum rank for that skill is one-half the maximum for a class skill.

\textbf{Class Features:} A multiclass character gets all the class features of all his or her classes but must also suffer the consequences of the special restrictions of all his or her classes.

\textbf{Feats:} A multiclass character gains feats based on character levels, regardless of individual class level

\textbf{Ability Increases:} A multiclass character gains ability score increases based on character level, regardless of individual class level.

\textbf{Spells:} The character gains spells from all of his or her spellcasting classes and keeps a separate spell list for each class. If a spell's effect is based on the class level of the caster, the player must keep track of which class's spell list the character is casting the spell from.

\pagebreak