%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Religion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The gods are many. A few, such as Pelor (god of the sun), have grand temples that sponsor mighty processions through the streets on high holy days. Others, such as Erythnul (god of slaughter), have temples only in hidden places or evil lands. While the gods most strongly make their presence felt through their clerics, they also have lay followers who more or less attempt to live up to their deities’ standards. The typical person has a deity whom he considers to be his patron. Still, it is only prudent to be respectful toward and even pray to other deities when the time is right. Before setting out on a journey, a follower of Pelor might leave a small sacrifice at a wayside shrine to Fharlanghn (god of roads) to improve his chances of having a safe journey. As long as one’s own deity is not at odds with the others in such an act of piety, such simple practices are common. In times of tribulation, however, some people recite dark prayers to evil deities. Such prayers are best muttered under one’s breath, lest others overhear

Deities rule the various aspects of human existence: good and evil, law and chaos, life and death, knowledge and nature. In addition, various nonhuman races have racial deities of their own. A character may not be a cleric of a racial deity unless he is of the right race, but he may worship such a deity and live according to that deity’s guidance. For a deity who is not tied to a particular race (such as Pelor), a cleric’s race is not an issue. Deities of certain monster types are identified in the Monster Manual. Many more deities than those described here or mentioned in the Monster Manual also exist.

\input{religion/deities}
\pagebreak

\pagebreak