%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Death Knight}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Those who take up the black sword of the Death Knights in the name of powerful evil gods are not all undead. They aren't even
all evil, since sometimes evil gods simply curse warriors in order to screw with them. But a lot of them are evil and undead, and that
gives the Death Knight his classic image

\textbf{Prerequisites:} 
\begin{description*}
\item[\hspace*{1.4cm}BAB:] +6.
\item[\hspace*{1.4cm}Skills:] \linkskill{Knowledge} (Undeath) 4 ranks.
\item[\hspace*{1.4cm}Special:] Must have proficiency with all martial weapons.
\item[\hspace*{1.4cm}Special:] Must have had nonviolent contact with a Fiend.
\end{description*}

\textbf{Alignment:} Usually Chaotic Evil.

\textbf{Hit Die:} d6

\textbf{Class Skills:} The Death Knight's class skills are \linkskill{Climb} (Str), \linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Knowledge} (Int), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Spot} (Wis), \linkskill{Swim} (Str).

\textbf{Skills/Level:} 4 + Intelligence Bonus

\goodbab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{classtable}
\levelone{Sword of Death, Life and Death}
\leveltwo{Army of the Dead}
\levelthree{Sphere: Bone}
\levelfour{Bonus Feat}
\levelfive{Sphere: Fire}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} The Death Knight gains no proficiency with armor or weapons.

\textbf{Sword of Death (Su):} A Death Knight can transform his blade into a black instrument of destruction. His melee attacks inflict 2d6 of Unholy damage against living creatures.

\textbf{Life and Death:} A Death Knight is transform into a Vampire, Ghoul, Revenant, or Swordwraith upon becoming a Death Knight. In addition, a Death Knight may qualify for and use Necromantic Feats using his Base Attack Bonus instead of a Caster level.

\textbf{Army of the Dead (Su):} A 2nd level Death Knight may Raise Undead as per \linkspell{Animate Dead} or \linkspell{Create Undead} with a Caster level equal to his hit dice.

\textbf{Spheres:} At 3rd level, a Death Knight gains the Sphere of \linksphere{Bone}. At 5th level, he gains the Sphere of \linksphere{Fire}.

\textbf{Bonus Feat:} At 4th level a Death Knight gains a bonus feat. This may be any [Combat] feat or [Fiend] feat he meets the prerequisites for.



