\featentry{Dragonwrought}{[Regional]}
\dragonwroughtfeat
{You were born a Dragonwrought Kobold, proof of your race’s innate connection to dragons.}
{Sorcerer.}
{You are a dragon wrought kobold. Your type is dragon rather than humanoid, and you lose the dragonblood subtype. You retain all your other subtypes and your kobold racial traits. Your scales become tinted with a color that matches that of your draconic heritage. As a dragon, you are immune to magic sleep and paralysis effects. You have darkvision out to 60 feet and low-light vision. You gain a Path/Class skill and a +2 racial bonus on the skill indicated for your draconic heritage on the table below.}
{You have wings that aid your jumping, granting a +10 racial bonus on Jump checks.
In addition, you can use your wings to glide, negating damage from a fall from any height and allowing 20 feet of forward travel for every 5 feet of descent. You glide at a speed of 30 feet with average maneuverability. Even if your maneuverability improves, you can’t hover while gliding. You can’t glide while carrying a medium or heavy load.
If you become unconscious or helpless while in midair, your wings naturally unfurl, and powerful ligaments stiffen them. You descend in a tight corkscrew and take only 1d6 points of falling damage, no matter what the actual distance of the fall.}
{You can fly at a speed of 30 feet (average maneuverability). You can’t fly while carrying a medium or heavy load or while fatigued or exhausted.
You can safely fly for a number of consecutive rounds equal to your Constitution modifier (minimum 1 round). You can exert yourself to fly for up to twice as long, but then you’re fatigued at the end of the flight. You are likewise fatigued after spending a total of more than 10 minutes per day flying. Because you can glide before, after, and between rounds of actual flight, you can remain aloft for extended periods, even if you can only use flight for 1 round at a time without becoming fatigued.}
{you have enough stamina and prowess to fly for longer periods. You can fly at a speed of 30 feet (average maneuverability), and flying requires no more exertion than walking or running.
You can make a dive attack. A dive attack works like a charge, but you must fl y a minimum of 30 feet and descend at least 10 feet. You can make a dive attack only when wielding a piercing weapon; if the attack hits, it deals double damage.
You can use the run action while flying, provided you fly in a straight line.}


\end{multicols}

\begin{smallbasictable}{Dragonwrought}{l c c c}
\textbf{Dragon Kind} & \textbf{Descriptor} & \textbf{Path/Class Skill} & \textbf{Spells Known}\\
Amethyst & Force & \linkskill{Diplomacy} & \linkspell{Delay posion}, \linkspell{Invisibility}, \linkspell{Suggestion}\\
Battle & Sonic & \linkskill{Perform} & \linkspell{Aid}, \linkspell{Heroism}, \linkspell{Protection from evil}\\
Black & Acid & \linkskill{Hide} &\\
Blue & Electricity & \linkskill{Hide} &\\
Brass & Fire & \linkskill{Gather Information} &\\
Bronze & Electricity & \linkskill{Survival} &\\
Brown & Acid & \linkskill{Listen} &\\
Chaos & Compulsion & \linkskill{Bluff} &\\
Chiang Lung & None & \linkskill{Swim} &\\
Copper & Acid & \linkskill{Hide} &\\
Crystal & Cold & \linkskill{Diplomacy} &\\
Deep & Charm & \linkskill{Spot} &\\
Emerald & Sonic & \linkskill{Knowledge} (Local) &\\
Ethereal & None & \linkskill{Escape Artist} &\\
Fang & None & \linkskill{Listen} &\\
Force & Force & \linkskill{Spot} &\\
Gold & Fire & \linkskill{Heal} & \linkspell{Bless}, \linkspell{Daylight}, \linkspell{Dispel Evil}\\
Green & Acid & \linkskill{Move Silently} &\\
Howling & Sonic & \linkskill{Survival} &\\
Li Lung & Earth & \linkskill{Hide} &\\
Lung Wang & Fire & \linkskill{Swim} &\\
Oceanus & Electricity & \linkskill{Swim} &Races of the Dragon pg.103\\
Pan Lung & None & \linkskill{Diplomacy} &\\
Platinum & Any one energy type & \linkskill{Concentration} &\\
Prismatic & Light & \linkskill{Diplomacy} &\\
Pyroclastic & Fire or Sonic & \linkskill{Listen} &\\
Radiant & Light & \linkskill{Spot} &\\
Red & Fire & \linkskill{Appraise} &\\
Rust & None & \linkskill{Search} &\\
Sand & Fire & \linkskill{Survival} &\\
Sapphire & Electricity & \linkskill{Knowledge} (Dungeoneering) &\\
Shadow & Energy Drain & \linkskill{Escape Artist} &\\
Shen Lung & Electricity & \linkskill{Spot} &\\
Silver & Cold & \linkskill{Disguise} &\\
Song & Electricity & \linkskill{Perform} (Sing) &\\
Styx & Poison or Disease & \linkskill{Swim} &\\
Tarterian & Force & \linkskill{Escape Artist} &\\
T'ien Lung & None & \linkskill{Diplomacy} &\\
Tun mi Lung & Electricity & \linkskill{Swim} &\\
Topaz & Cold & \linkskill{Swim} &\\
White & Cold & \linkskill{Hide} &\\
Yu Lung & None & \linkskill{Swim} &\\
\end{smallbasictable}

\begin{multicols}{2}