%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Rock Gnome}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Rock Gnomes are the Gnomes that most people are familiar with, so much so that when someone says “a Gnome,” he or she is almost always speaking of a Rock Gnome. Unlike their reclusive cousins, the Deep Gnomes and the Forest Gnomes, the Rock Gnomes are an inquisitive and loquacious people. They are renowned throughout Faerûn as technicians, alchemists, and inventors, as well as illusionists of the highest order. They do not care much for living in larger cities, where their talents are in high demand, and prefer the rolling hills of the countryside. But anywhere they find themselves, they display an amazing zest for  life and all the pleasures it holds.

Rock Gnomes are far friendlier and more outgoing than the other Gnome kindreds. They are well known for their love of jokes and pranks, as well as their fondness for finely made things. As with all Gnomes, they adore gems of all kinds, but Rock Gnomes have a particular passion for the purity and perfection of the diamond.

\begin{multicols}{2}

\begin{itemize*}
\item Small sized.
\item 20ft movement.
\item Humanoid Type (Gnome subtype)
\item \linkability{Low-Light Vision}
\item +2 Constitution, -2 Strength.
\item Weapon Familiarity: Rock Gnomes may treat gnome hooked hammers as martial weapons rather than exotic weapons.
\item +2 racial bonus on saving throws against Illusions.
\item Add +1 to the Difficulty Class for all saving throws against illusion spells cast by the Rock Gnome. This adjustment stacks with those from similar effects.
\item +1 racial bonus on attack rolls against kobolds and goblinoids.
\item +4 dodge bonus to Armor Class against monsters of the giant type.
\item +2 racial bonus on \linkskill{Listen} checks.
\item +2 racial bonus on \linkskill{Craft} (alchemy) checks.
\item Spell-Like Abilities: at-will -- \linkspell{speak with animals} (burrowing mammal only, duration 1 minute). A Rock Gnome with a Charisma score of at least 10 also has the following spell-like abilities: 1/day -- \linkspell{dancing lights, ghost sound, prestidigitation}. Caster level 1st; save DC 10 + Gnome's Cha modifier + spell level.
\item Alignment: Usually neutral good
\item Favored Classes: \linkclass{Bard}, \linkclass{Wizard}. 
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
40 & +4d6 & +6d6 & +9d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
3'0'' & 2'10'' & \multicolumn{2}{c}{+2d4}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 40 lb. & \cellcolor{white} 35 lb. & \multicolumn{2}{c}{\cellcolor{white}X 1 lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Rock Gnome Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
\multicolumn{1}{p{2cm}}{\raggedright{}The Great Dale} & Damaran, Gnome & \multicolumn{1}{p{5cm}}{\raggedright{}Draconic, Elven, Gnoll, Goblin, Orc, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Animal Friends}, \linkfeat{Forester}, \linkfeat{Magic in the Blood}}\\
\multicolumn{1}{p{2cm}}{\raggedright{}Lantan} & Gnome, Lantanese & \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Chondathan, Draconic, Dwarven, Ignan, Illuskan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Education}, \linkfeat{Fearless}, \linkfeat{Mercantile Background}}\\
\multicolumn{1}{p{2cm}}{\raggedright{}Thesk} & Aglarondan, Gnome & \multicolumn{1}{p{5cm}}{\raggedright{}Damaran, Draconic, Elven, Goblin, Orc, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Artist}, \linkfeat{Magic in the Blood}, \linkfeat{Smooth Talk}}\\
\multicolumn{1}{p{2cm}}{\raggedright{}The Western Heartlands} & Gnome, Chondathan & \multicolumn{1}{p{5cm}}{\raggedright{}Draconic, Dwarven, Goblin, Illuskan, Sylvan, Terran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Artist}, \linkfeat{Discipline}, \linkfeat{Strong Soul}}\\
\end{smallbasictable}

\pagebreak