%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Slaymate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A Slaymate is a young child who has died because of neglect or abuse by their parents or guardians. The hatred and/or despair of the child sometimes is strong enough to bring back the child as a Slaymate. Most Slaymates are female, but it's not unheard of for boys to become Slaymates.

Once a child becomes a Slaymate, their skin turns an unnatural shade of pale, and they have an almost constant look of sadness. Otherwise they have the twisted appearance of a child.

Slaymates often seek out other creatures to serve as their new “parents”, such as necromancers or larger, stronger undead. Both spellcasters and the walking dead appreciate the slaymate’s abilities to bolster their trades and serve to protect the pathetic, horrific slaymate in exchange for these powers. A slaymate’s behavior reflects a disturbing innocence and cruelty that they themself have suffered, often inflicting harm upon animals or things smaller than themselves.

\textbf{Creating a Slaymate:} Slaymate is a unique class that is added to any living Humanoid child, and must be taken at first level. A Slaymate is created when a child is neglected to the point of death, however not all cases of neglect will create a Slaymate.

\textbf{Alignment:} Evil; A Slaymate's mind is twisted by the abuse they have suffered.

\textbf{Starting Gold:} 2d4x10 gp (50 gold)

\textbf{Starting Age:} Special; Half of complex of base creature.

\textbf{Hit Die:} d12

\textbf{Class Skills:} The \currentclassname{}'s class skills are \linkskill{Hide} (Dex), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Spot} (Wis)

\textbf{Skills/Level:} 2 + Intelligence Bonus

\poorbab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{classtable}
\levelone{Slaymate, Natural Armor}
\leveltwo{Pale Wasting}
\levelthree{Natural Armor}
\levelfour{Pale Aura}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} A Slaymate gains no proficiency with any armor or weapons.

\textbf{Slaymate:} A Slaymate is a undead child. Slaymate gains the Undead type with the Unliving (subtype) keeping any subtype of their base race; being a child their size changes to one lower than their base creature (ie. Small for Humans and Elfs).

\textbf{Natural Armor:} A Slaymate's twisted form offers it some defends. At first and third levels a Slaymate gains +2 Natural Armor.

\textbf{Pale Wasting (Su):} The Rotting mouth of a Slaymate has a special disease that it uses to defend it self. At Level 2 a Slaymate gains a Bite attack 1d3+Str plus Pale Wasting; 
 Pale Wasting is a supernatural disease Fortitude 10+Cha mod+Character level, incubation period 1 day; damage 1d6 Con and 1d6 Str.
 
 \textbf{Pale Aura (Su):} A Slaymate as a special aura that boosts Necromancy. At Level 4 A Slaymate produces an invisible aura in a 10-foot radius around itself. Any creature (Including itself) within the aura that uses a metamagic feat on a spell from the school of necromancy can prepare or use the spell as if it took up a spell slot one level lower than what the metamagic necromancy spell would normally require to a minimum of the spell's base level.