%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Assassin Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}

\subsection{0-Level Assassin Spells (Cantrips)}
\begin{description*}
\item[\linkspell{Detect Poison}:] Detects poison in one creature or small object.
\item[\linkspell{Disrupt Undead}:] Deals 1d6 damage to one undead.
\item[\linkspell{Ghost Sound}:] Figment sounds.
\item[\linkspell{Touch of Fatigue}:] Touch attack fatigues target.
\end{description*}

\subsection{1st-Level Assassin Spells}
\begin{description*}
\item[\linkspell{Cause Fear}:] One creature of 5 HD or less flees for 1d4 rounds.
\item[\linkspell{Chill Touch}:] One touch/level deals 1d6 damage and possibly 1 Str damage.
\item[\linkspell{Color Spray}:] Knocks unconscious, blinds, and/or stuns 1d6 weak creatures.
\item[\linkspell{Comprehend Languages}:] You understand all spoken and written languages.
\item[\linkspell{Detect Secret Doors}:] Reveals hidden doors within 60 ft.
\item[\linkspell{Detect Undead}:] Reveals undead within 60 ft.
\item[\linkspell{Disguise Self}:] Changes your appearance.
\item[\linkspell{Identify}:] Determines properties of magic item.
\item[\linkspell{Nystul’s Magic Aura}:] Alters object’s magic aura.
\item[\linkspell{Ray of Enfeeblement}:] Ray deals 1d6 +1 per two levels Str damage.
\item[\linkspell{Silent Image}:] Creates minor illusion of your design.
\item[\linkspell{True Strike}:] +20 on your next attack roll.
\item[\linkspell{Unseen Servant}:] Invisible force obeys your commands.
\item[\linkspell{Ventriloquism}:] Throws voice for 1 min./level.
\end{description*}

\subsection{2nd-Level Assassin Spells}
\begin{description*}
\item[\linkspell{Blindness/Deafness}:] Makes subject blinded or deafened.
\item[\linkspell{Blur}:] Attacks miss subject 20\% of the time.
\item[\linkspell{Command Undead}:] Undead creature obeys your commands.
\item[\linkspell{Detect Thoughts}:] Allows “listening” to surface thoughts.
\item[\linkspell{False Life}:] Gain 1d10 temporary hp +1/level (max +10).
\item[\linkspell{Ghoul Touch}:] Paralyzes one subject, which exudes stench that makes those nearby sickened.
\item[\linkspell{Hypnotic Pattern}:] Fascinates (2d4 + level) HD of creatures.
\item[\linkspell{Invisibility}:] Subject is invisible for 1 min./level or until it attacks.
\item[\linkspell{Leomund’s Trap}:] Makes item seem trapped.
\item[\linkspell{Locate Object}:] Senses direction toward object (specific or type).
\item[\linkspell{Magic Mouth}:] Speaks once when triggered.
\item[\linkspell{Minor Image}:] As \linkspell{Silent Image}, plus some sound.
\item[\linkspell{Mirror Image}:] Creates decoy duplicates of you (1d4 +1 per three levels, max 8).
\item[\linkspell{Misdirection}:] Misleads divinations for one creature or object.
\item[\linkspell{Scare}:] Panics creatures of less than 6 HD.
\item[\linkspell{See Invisibility}:] Reveals invisible creatures or objects.
\item[\linkspell{Spectral Hand}:] Creates disembodied glowing hand to deliver touch attacks.
\end{description*}

\subsection{3rd-Level Assassin Spells}
\begin{description*}
\item[\linkspell{Arcane Sight}:] Magical auras become visible to you.
\item[\linkspell{Clairaudience/Clairvoyance}:] Hear or see at a distance for 1 min./level.
\item[\linkspell{Displacement}:] Attacks miss subject 50\%.
\item[\linkspell{Gentle Repose}:] Preserves one corpse.
\item[\linkspell{Halt Undead}:] Immobilizes undead for 1 round/level.
\item[\linkspell{Illusory Script}:] Only intended reader can decipher.
\item[\linkspell{Invisibility Sphere}:] Makes everyone within 10 ft. invisible.
\item[\linkspell{Major Image}:] As \linkspell{Silent Image}, plus sound, smell and thermal effects.
\item[\linkspell{Ray of Exhaustion}:] Ray makes subject exhausted.
\item[\linkspell{Tongues}:] Speak any language.
\item[\linkspell{Vampiric Touch}:] Touch deals 1d6/two levels damage; caster gains damage as hp.
\end{description*}

\subsection{4th-Level Assassin Spells}
\begin{description*}
\item[\linkspell{Animate Dead}:] Creates undead skeletons and zombies.
\item[\linkspell{Arcane Eye}:] Invisible floating eye moves 30 ft./round.
\item[\linkspell{Bestow Curse}:] –6 to an ability score; –4 on attack rolls, saves, and checks; or 50\% chance of losing each action.
\item[\linkspell{Contagion}:] Infects subject with chosen disease.
\item[\linkspell{Detect Scrying}:] Alerts you of magical eavesdropping.
\item[\linkspell{Enervation}:] Subject gains 1d4 negative levels.
\item[\linkspell{Fear}:] Subjects within cone flee for 1 round/level.
\item[\linkspell{Hallucinatory Terrain}:] Makes one type of terrain appear like another (field into forest, or the like).
\item[\linkspell{Illusory Wall}:] Wall, floor, or ceiling looks real, but anything can pass through.
\item[\linkspell{Invisibility, Greater}:] As \linkspell{Invisibility}, but subject can attack and stay invisible.
\item[\linkspell{Locate Creature}:] Indicates direction to familiar creature.
\item[\linkspell{Phantasmal Killer}:] Fearsome illusion kills subject or deals 3d6 damage.
\item[\linkspell{Rainbow Pattern}:] Lights fascinate 24 HD of creatures.
\item[\linkspell{Scrying}:] Spies on subject from a distance.
\item[\linkspell{Shadow Conjuration}:] Mimics conjuration below 4th level, but only 20\% real.
\end{description*}

\subsection{5th-Level Assassin Spells}
\begin{description*}
\item[\linkspell{Blight}:] Withers one plant or deals 1d6/level damage to plant creature.
\item[\linkspell{Contact Other Plane}:] Lets you ask question of extraplanar entity.
\item[\linkspell{Dream}:] Sends message to anyone sleeping.
\item[\linkspell{False Vision}:] Fools scrying with an illusion.
\item[\linkspell{Magic Jar}:] Enables possession of another creature.
\item[\linkspell{Mirage Arcana}:] As \linkspell{Hallucinatory Terrain}, plus structures.
\item[\linkspell{Nightmare}:] Sends vision dealing 1d10 damage, fatigue.
\item[\linkspell{Persistent Image}:] As \linkspell{Major Image}, but no concentration required.
\item[\linkspell{Prying Eyes}:] 1d4 +1/level floating eyes scout for you.
\item[\linkspell{Rary’s Telepathic Bond}:] Link lets allies communicate.
\item[\linkspell{Seeming}:] Changes appearance of one person per two levels.
\item[\linkspell{Shadow Evocation}:] Mimics evocation below 5th level, but only 20\% real.
\item[\linkspell{Symbol of Pain}:] Triggered rune wracks nearby creatures with pain.
\item[\linkspell{Waves of Fatigue}:] Several targets become fatigued.
\end{description*}

\subsection{6th-Level Assassin Spells}
\begin{description*}
\item[\linkspell{Analyze Dweomer}:] Reveals magical aspects of subject.
\item[\linkspell{Circle of Death}:] Kills 1d4/level HD of creatures.
\item[\linkspell{Create Undead}:] Creates ghouls, ghasts, mummies, or mohrgs.
\item[\linkspell{Eyebite}:] Target becomes panicked, sickened, and comatose.
\item[\linkspell{Legend Lore}:] Lets you learn tales about a person, place, or thing.
\item[\linkspell{Mislead}:] Turns you invisible and creates illusory double.
\item[\linkspell{Permanent Image}:] Includes sight, sound, and smell.
\item[\linkspell{Programmed Image}:] As \linkspell{Major Image}, plus triggered by event.
\item[\linkspell{Shadow Walk}:] Step into shadow to travel rapidly.
\item[\linkspell{Symbol of Fear}:] Triggered rune panics nearby creatures.
\item[\linkspell{True Seeing}:] Lets you see all things as they really are.
\item[\linkspell{Undeath to Death}:] Destroys 1d4/level HD of undead (max 20d4).
\item[\linkspell{Veil}:] Changes appearance of group of creatures.
\end{description*}

\end{multicols}