%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Bard Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}

\subsection{0-Level Bard Spells (Cantrips)}
\begin{description*}
\item[\linkspell{Dancing Lights}:] Creates torches or other lights.
\item[\linkspell{Daze}:] Humanoid creature of 4 HD or less loses next action.
\item[\linkspell{Detect Magic}:] Detects spells and magic items within 60 ft.
\item[\linkspell{Flare}:] \linkcondition{Dazzles} one creature (–1 on attack rolls).
\item[\linkspell{Ghost Sound}:] Figment sounds.
\item[\linkspell{Know Direction}:] You discern north.
\item[\linkspell{Light}:] Object shines like a torch.
\item[\linkspell{Lullaby}:] Makes subject drowsy; –5 on Spot and Listen checks, –2 on Will saves against \linkcondition{Sleep}.
\item[\linkspell{Mage Hand}:] 5-pound telekinesis.
\item[\linkspell{Mending}:] Makes minor repairs on an object.
\item[\linkspell{Message}:] Whispered conversation at distance.
\item[\linkspell{Open/Close}:] Opens or closes small or light things.
\item[\linkspell{Prestidigitation}:] Performs minor tricks.
\item[\linkspell{Read Magic}:] Read scrolls and spellbooks.
\item[\linkspell{Resistance}:] Subject gains +1 on saving throws.
\item[\linkspell{Summon Instrument}:] Summons one instrument of the caster’s choice.
\end{description*}

\subsection{1st-Level Bard Spells}
\begin{description*}
\item[\linkspell{Alarm}:] Wards an area for 2 hours/level.
\item[\linkspell{Animate Rope}:] Makes a rope move at your command.
\item[\linkspell{Cause Fear}:] One creature of 5 HD or less flees for 1d4 rounds.
\item[\linkspell{Charm Person}:] Makes one person your friend.
\item[\linkspell{Comprehend Languages}:] You understand all spoken and written languages.
\item[\linkspell{Cure Light Wounds}:] Cures 1d8 damage +1/level (max +5).
\item[\linkspell{Detect Secret Doors}:] Reveals hidden doors within 60 ft.
\item[\linkspell{Disguise Self}:] Changes your appearance.
\item[\linkspell{Erase}:] Mundane or magical writing vanishes.
\item[\linkspell{Expeditious Retreat}:] Your speed increases by 30 ft.
\item[\linkspell{Feather Fall}:] Objects or creatures fall slowly.
\item[\linkspell{Grease}:] Makes 10-ft. square or one object slippery.
\item[\linkspell{Hypnotism}:] Fascinates 2d4 HD of creatures.
\item[\linkspell{Identify}:] Determines properties of magic item.
\item[\linkspell{Lesser Confusion}:] One creature is \linkcondition{Confused} for 1 round.
\item[\linkspell{Magic Mouth}:] Speaks once when triggered.
\item[\linkspell{Nystul’s Magic Aura}:] Alters object’s magic aura.
\item[\linkspell{Obscure Object}:] Masks object against scrying.
\item[\linkspell{Remove Fear}:] Suppresses fear or gives +4 on saves against fear for one subject + one per four levels.
\item[\linkspell{Silent Image}:] Creates minor illusion of your design.
\item[\linkspell{Sleep}:] Puts 4 HD of creatures into magical slumber.
\item[\linkspell{Summon Monster I}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Hideous Laughter}:] Subject loses actions for 1 round/level.
\item[\linkspell{Undetectable Alignment}:] Conceals alignment for 24 hours.
\item[\linkspell{Unseen Servant}:] Invisible force obeys your commands.
\item[\linkspell{Ventriloquism}:] Throws voice for 1 min./level.
\end{description*}

\subsection{2nd-Level Bard Spells}
\begin{description*}
\item[\linkspell{Alter Self}:] Assume form of a similar creature.
\item[\linkspell{Animal Messenger}:] Sends a Tiny animal to a specific place.
\item[\linkspell{Animal Trance}:] Fascinates 2d6 HD of animals.
\item[\linkspell{Blindness/Deafness}:] Makes subject blind or deaf.
\item[\linkspell{Blur}:] Attacks miss subject 20\% of the time.
\item[\linkspell{Calm Emotions}:] Calms creatures, negating emotion effects.
\item[\linkspell{Cat’s Grace}:] Subject gains +4 to Dex for 1 min./level.
\item[\linkspell{Cure Moderate Wounds}:] Cures 2d8 damage +1/level (max +10).
\item[\linkspell{Darkness}:] 20-ft. radius of supernatural shadow.
\item[\linkspell{Daze Monster}:] Living creature of 6 HD or less loses next action.
\item[\linkspell{Delay Poison}:] Stops poison from harming subject for 1 hour/ level.
\item[\linkspell{Detect Thoughts}:] Allows “listening” to surface thoughts.
\item[\linkspell{Eagle’s Splendor}:] Subject gains +4 to Cha for 1 min./level.
\item[\linkspell{Enthrall}:] Captivates all within 100 ft. + 10 ft./level.
\item[\linkspell{Fox’s Cunning}:] Subject gains +4 to Int for 1 min./level.
\item[\linkspell{Glitterdust}:] Blinds creatures, outlines invisible creatures.
\item[\linkspell{Heroism}:] Gives +2 on attack rolls, saves, skill checks.
\item[\linkspell{Hold Person}:] Paralyzes one humanoid for 1 round/level.
\item[\linkspell{Hypnotic Pattern}:] Fascinates (2d4 + level) HD of creatures.
\item[\linkspell{Invisibility}:] Subject is invisible for 1 min./level or until it attacks.
\item[\linkspell{Locate Object}:] Senses direction toward object (specific or type).
\item[\linkspell{Minor Image}:] As \linkspell{Silent Image}, plus some sound.
\item[\linkspell{Mirror Image}:] Creates decoy duplicates of you (1d4 +1 per three levels, max 8).
\item[\linkspell{Misdirection}:] Misleads divinations for one creature or object.
\item[\linkspell{Pyrotechnics}:] Turns fire into blinding light or choking smoke.
\item[\linkspell{Rage}:] Gives +2 to Str and Con, +1 on Will saves, –2 to AC.
\item[\linkspell{Scare}:] Panics creatures of less than 6 HD.
\item[\linkspell{Shatter}:] Sonic vibration damages objects or crystalline creatures.
\item[\linkspell{Silence}:] Negates sound in 15-ft. radius.
\item[\linkspell{Sound Burst}:] Deals 1d8 sonic damage to subjects; may stun them.
\item[\linkspell{Suggestion}:] Compels subject to follow stated course of action.
\item[\linkspell{Summon Monster II}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Summon Swarm}:] Summons swarm of bats, rats, or spiders.
\item[\linkspell{Tongues}:] Speak any language.
\item[\linkspell{Whispering Wind}:] Sends a short message 1 mile/level.
\end{description*}

\subsection{3rd-Level Bard Spells}
\begin{description*}
\item[\linkspell{Blink}:] You randomly vanish and reappear for 1 round/level.
\item[\linkspell{Charm Monster}:] Makes monster believe it is your ally.
\item[\linkspell{Clairaudience/Clairvoyance}:] Hear or see at a distance for 1 min./level.
\item[\linkspell{Confusion}:] Subjects behave oddly for 1 round/level.
\item[\linkspell{Crushing Despair}:] Subjects take –2 on attack rolls, damage rolls, saves, and checks.
\item[\linkspell{Cure Serious Wounds}:] Cures 3d8 damage +1/level (max +15).
\item[\linkspell{Daylight}:] 60-ft. radius of bright light.
\item[\linkspell{Deep Slumber}:] Puts 10 HD of creatures to sleep.
\item[\linkspell{Dispel Magic}:] Cancels magical spells and effects.
\item[\linkspell{Displacement}:] Attacks miss subject 50%.
\item[\linkspell{Fear}:] Subjects within cone flee for 1 round/level.
\item[\linkspell{Gaseous Form}:] Subject becomes insubstantial and can fly slowly.
\item[\linkspell{Geas, Lesser}:] Commands subject of 7 HD or less.
\item[\linkspell{Glibness}:] You gain +30 bonus on Bluff checks, and your lies can escape magical discernment.
\item[\linkspell{Good Hope}:] Subjects gain +2 on attack rolls, damage rolls, saves, and checks.
\item[\linkspell{Haste}:] One creature/level moves faster, +1 on attack rolls, AC, and Reflex saves.
\item[\linkspell{Illusory Script}:] Only intended reader can decipher.
\item[\linkspell{Invisibility Sphere}:] Makes everyone within 10 ft. invisible.
\item[\linkspell{Leomund’s Tiny Hut}:] Creates shelter for ten creatures.
\item[\linkspell{Major Image}:] As \linkspell{Silent Image}, plus sound, smell and thermal effects.
\item[\linkspell{Phantom Steed}:] Magic horse appears for 1 hour/level.
\item[\linkspell{Remove Curse}:] Frees object or person from curse.
\item[\linkspell{Scrying}:] Spies on subject from a distance.
\item[\linkspell{Sculpt Sound}:] Creates new sounds or changes existing ones.
\item[\linkspell{Secret Page}:] Changes one page to hide its real content.
\item[\linkspell{See Invisibility}:] Reveals invisible creatures or objects.
\item[\linkspell{Sepia Snake Sigil}:] Creates text symbol that immobilizes reader.
\item[\linkspell{Slow}:] One subject/level takes only one action/round, –2 to AC and attack rolls.
\item[\linkspell{Speak with Animals}:] You can communicate with animals.
\item[\linkspell{Summon Monster III}:] Calls extraplanar creature to fight for you.
\end{description*}

\subsection{4th-Level Bard Spells}
\begin{description*}
\item[\linkspell{Break Enchantment}:] Frees subjects from enchantments, alterations, curses, and petrification.
\item[\linkspell{Cure Critical Wounds}:] Cures 4d8 damage +1/level (max +20).
\item[\linkspell{Detect Scrying}:] Alerts you of magical eavesdropping.
\item[\linkspell{Dimension Door}:] Teleports you short distance.
\item[\linkspell{Dominate Person}:] Controls humanoid telepathically.
\item[\linkspell{Freedom of Movement}:] Subject moves normally despite impediments.
\item[\linkspell{Hallucinatory Terrain}:] Makes one type of terrain appear like another (field into forest, or the like).
\item[\linkspell{Hold Monster}:] As \linkspell{Hold Person}, but any creature.
\item[\linkspell{Invisibility, Greater}:] As \linkspell{Invisibility}, but subject can attack and stay invisible.
\item[\linkspell{Legend Lore}:] Lets you learn tales about a person, place, or thing.
\item[\linkspell{Leomund’s Secure Shelter}:] Creates sturdy cottage.
\item[\linkspell{Locate Creature}:] Indicates direction to familiar creature.
\item[\linkspell{Modify Memory}:] Changes 5 minutes of subject’s memories.
\item[\linkspell{Neutralize Poison}:] Immunizes subject against poison, detoxifies venom in or on subject.
\item[\linkspell{Rainbow Pattern}:] Lights fascinate 24 HD of creatures.
\item[\linkspell{Repel Vermin}:] Insects, spiders, and other vermin stay 10 ft. away.
\item[\linkspell{Shadow Conjuration}:] Mimics conjuring below 4th level, but only 20\% real.
\item[\linkspell{Shout}:] Deafens all within cone and deals 5d6 sonic damage.
\item[\linkspell{Speak with Plants}:] You can talk to normal plants and plant creatures.
\item[\linkspell{Summon Monster IV}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Zone of Silence}:] Keeps eavesdroppers from overhearing conversations.
\end{description*}

\subsection{5th-Level Bard Spells}
\begin{description*}
\item[\linkspell{Cure Light Wounds, Mass}:] Cures 1d8 damage +1/level for many creatures.
\item[\linkspell{Dispel Magic, Greater}:] As dispel magic, but +20 on check.
\item[\linkspell{Dream}:] Sends message to anyone sleeping.
\item[\linkspell{False Vision}:] Fools scrying with an illusion.
\item[\linkspell{Heroism, Greater}:] Gives +4 bonus on attack rolls, saves, skill checks; immunity to fear; temporary hp.
\item[\linkspell{Mind Fog}:] Subjects in fog get –10 to Wis and Will checks.
\item[\linkspell{Mirage Arcana}:] As hallucinatory terrain, plus structures.
\item[\linkspell{Mislead}:] Turns you invisible and creates illusory double.
\item[\linkspell{Nightmare}:] Sends vision dealing 1d10 damage, fatigue.
\item[\linkspell{Persistent Image}:] As major image, but no concentration required.
\item[\linkspell{Seeming}:] Changes appearance of one person per two levels.
\item[\linkspell{Shadow Evocation}:] Mimics evocation of lower than 5th level, but only 20\% real.
\item[\linkspell{Shadow Walk}:] Step into shadow to travel rapidly.
\item[\linkspell{Song of Discord}:] Forces targets to attack each other.
\item[\linkspell{Suggestion, Mass}:] As suggestion, plus one subject/level.
\item[\linkspell{Summon Monster V}:] Calls extraplanar creature to fight for you.
\end{description*}

\subsection{6th-Level Bard Spells}
\begin{description*}
\item[\linkspell{Analyze Dweomer}:] Reveals magical aspects of subject.
\item[\linkspell{Animate Objects}:] Objects attack your foes.
\item[\linkspell{Cat’s Grace, Mass}:] As cat’s grace, affects one subject/level.
\item[\linkspell{Charm Monster, Mass}:] As charm monster, but all within 30 ft.
\item[\linkspell{Cure Moderate Wounds, Mass}:] Cures 2d8 damage +1/level for many creatures.
\item[\linkspell{Eagle’s Splendor, Mass}:] As eagle’s splendor, affects one subject/level.
\item[\linkspell{Eyebite}:] Target becomes panicked, sickened, and comatose.
\item[\linkspell{Find the Path}:] Shows most direct way to a location.
\item[\linkspell{Fox’s Cunning, Mass}:] As fox’s cunning, affects one subject/level.
\item[\linkspell{Geas/Quest}:] As lesser geas, plus it affects any creature.
\item[\linkspell{Heroes’ Feast}:] Food for one creature/level cures and grants combat bonuses.
\item[\linkspell{Otto’s Irresistible Dance}:] Forces subject to dance.
\item[\linkspell{Permanent Image}:] Includes sight, sound, and smell.
\item[\linkspell{Programmed Image}:] As major image, plus triggered by event.
\item[\linkspell{Project Image}:] Illusory double can talk and cast spells.
\item[\linkspell{Scrying, Greater}:] As scrying, but faster and longer.
\item[\linkspell{Shout, Greater}:] Devastating yell deals 10d6 sonic damage; stuns creatures, damages objects.
\item[\linkspell{Summon Monster VI}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Sympathetic Vibration}:] Deals 2d10 damage/round to freestanding structure.
\item[\linkspell{Veil}:] Changes appearance of group of creatures.
\end{description*}

\end{multicols}