%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cleric Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}

\subsection{0-Level Cleric Spells (Orisons)}
\begin{description*}
\item[\linkspell{Create Water}:] Creates 2 gallons/level of pure water.
\item[\linkspell{Cure Minor Wounds}:] Cures 1 point of damage.
\item[\linkspell{Detect Magic}:] Detects spells and magic items within 60 ft.
\item[\linkspell{Detect Poison}:] Detects poison in one creature or object.
\item[\linkspell{Guidance}:] +1 on one attack roll, saving throw, or skill check.
\item[\linkspell{Inflict Minor Wounds}:] Touch attack, 1 point of damage.
\item[\linkspell{Light}:] Object shines like a torch.
\item[\linkspell{Mending}:] Makes minor repairs on an object.
\item[\linkspell{Purify Food and Drink}:] Purifies 1 cu. ft./level of food or water.
\item[\linkspell{Read Magic}:] Read scrolls and spellbooks.
\item[\linkspell{Resistance}:] Subject gains +1 on saving throws.
\item[\linkspell{Virtue}:] Subject gains 1 temporary hp.
\end{description*}

\subsection{1st-Level Cleric Spells}
\begin{description*}
\item[\linkspell{Bane}:] Enemies take –1 on attack rolls and saves against fear.
\item[\linkspell{Bless}:] Allies gain +1 on attack rolls and saves against fear.
\item[\linkspell{Bless Water}:] Makes holy water.
\item[\linkspell{Cause Fear}:] One creature of 5 HD or less flees for 1d4 rounds.
\item[\linkspell{Command}:] One subject obeys selected command for 1 round.
\item[\linkspell{Comprehend Languages}:] You understand all spoken and written languages.
\item[\linkspell{Cure Light Wounds}:] Cures 1d8 damage +1/level (max +5).
\item[\linkspell{Curse Water}:] Makes unholy water.
\item[\linkspell{Deathwatch}:] Reveals how near death subjects within 30 ft. are.
\item[\linkspell{Detect Chaos/Evil/Good/Law}:] Reveals creatures, spells, or objects of selected alignment.
\item[\linkspell{Detect Undead}:] Reveals undead within 60 ft.
\item[\linkspell{Divine Favor}:] You gain +1 per three levels on attack and damage rolls.
\item[\linkspell{Doom}:] One subject takes –2 on attack rolls, damage rolls, saves, and checks.
\item[\linkspell{Endure Elements}:] Exist comfortably in hot or cold environments.
\item[\linkspell{Entropic Shield}:] Ranged attacks against you have 20\% miss chance.
\item[\linkspell{Hide from Undead}:] Undead can’t perceive one subject/level.
\item[\linkspell{Inflict Light Wounds}:] Touch deals 1d8 damage +1/level (max +5).
\item[\linkspell{Magic Stone}:] Three stones gain +1 on attack, deal 1d6 +1 damage.
\item[\linkspell{Magic Weapon}:] Weapon gains +1 bonus.
\item[\linkspell{Obscuring Mist}:] Fog surrounds you.
\item[\linkspell{Protection from Chaos/Evil/Good/Law}:] +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item[\linkspell{Remove Fear}:] Suppresses fear or gives +4 on saves against fear for one subject + one per four levels.
\item[\linkspell{Sanctuary}:] Opponents can’t attack you, and you can’t attack.
\item[\linkspell{Shield of Faith}:] Aura grants +2 or higher deflection bonus.
\item[\linkspell{Summon Monster I}:] Calls extraplanar creature to fight for you.
\end{description*}

\subsection{2nd-Level Cleric Spells}
\begin{description*}
\item[\linkspell{Aid}:] +1 on attack rolls and saves against fear, 1d8 temporary hp +1/level (max +10).
\item[\linkspell{Align Weapon}:] Weapon becomes good, evil, lawful, or chaotic.
\item[\linkspell{Augury}:] Learns whether an action will be good or bad.
\item[\linkspell{Bear’s Endurance}:] Subject gains +4 to Con for 1 min./level.
\item[\linkspell{Bull’s Strength}:] Subject gains +4 to Str for 1 min./level.
\item[\linkspell{Calm Emotions}:] Calms creatures, negating emotion effects.
\item[\linkspell{Consecrate}:] Fills area with positive energy, making undead weaker.
\item[\linkspell{Cure Moderate Wounds}:] Cures 2d8 damage +1/level (max +10).
\item[\linkspell{Darkness}:] 20-ft. radius of supernatural shadow.
\item[\linkspell{Death Knell}:] Kills dying creature; you gain 1d8 temporary hp, +2 to Str, and +1 level.
\item[\linkspell{Delay Poison}:] Stops poison from harming subject for 1 hour/level.
\item[\linkspell{Desecrate}:] Fills area with negative energy, making undead stronger.
\item[\linkspell{Eagle’s Splendor}:] Subject gains +4 to Cha for 1 min./level.
\item[\linkspell{Enthrall}:] Captivates all within 100 ft. + 10 ft./level.
\item[\linkspell{Find Traps}:] Notice traps as a rogue does.
\item[\linkspell{Gentle Repose}:] Preserves one corpse.
\item[\linkspell{Hold Person}:] Paralyzes one humanoid for 1 round/level.
\item[\linkspell{Inflict Moderate Wounds}:] Touch attack, 2d8 damage +1/level (max +10).
\item[\linkspell{Make Whole}:] Repairs an object.
\item[\linkspell{Owl’s Wisdom}:] Subject gains +4 to Wis for 1 min./level.
\item[\linkspell{Remove Paralysis}:] Frees one or more creatures from paralysis or slow effect.
\item[\linkspell{Resist Energy}:] Ignores 10 (or more) points of damage/attack from specified energy type.
\item[\linkspell{Restoration, Lesser}:] Dispels magical ability penalty or repairs 1d4 ability damage.
\item[\linkspell{Shatter}:] Sonic vibration damages objects or crystalline creatures.
\item[\linkspell{Shield Other}:] You take half of subject’s damage.
\item[\linkspell{Silence}:] Negates sound in 15-ft. radius.
\item[\linkspell{Sound Burst}:] Deals 1d8 sonic damage to subjects; may stun them.
\item[\linkspell{Spiritual Weapon}:] Magic weapon attacks on its own.
\item[\linkspell{Status}:] Monitors condition, position of allies.
\item[\linkspell{Summon Monster II}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Undetectable Alignment}:] Conceals alignment for 24 hours.
\item[\linkspell{Zone of Truth}:] Subjects within range cannot lie.
\end{description*}

\subsection{3rd-Level Cleric Spells}
\begin{description*}
\item[\linkspell{Animate Dead}:] Creates undead skeletons and zombies.
\item[\linkspell{Bestow Curse}:] –6 to an ability score; –4 on attack rolls, saves, and checks; or 50\% chance of losing each action.
\item[\linkspell{Blindness/Deafness}:] Makes subject blinded or deafened.
\item[\linkspell{Contagion}:] Infects subject with chosen disease.
\item[\linkspell{Continual Flame}:] Makes a permanent, heatless torch.
\item[\linkspell{Create Food and Water}:] Feeds three humans (or one horse)/level.
\item[\linkspell{Cure Serious Wounds}:] Cures 3d8 damage +1/level (max +15).
\item[\linkspell{Daylight}:] 60-ft. radius of bright light.
\item[\linkspell{Deeper Darkness}:] Object sheds supernatural shadow in 60-ft. radius.
\item[\linkspell{Dispel Magic}:] Cancels spells and magical effects.
\item[\linkspell{Glyph of Warding}:] Inscription harms those who pass it.
\item[\linkspell{Helping Hand}:] Ghostly hand leads subject to you.
\item[\linkspell{Inflict Serious Wounds}:] Touch attack, 3d8 damage +1/level (max +15).
\item[\linkspell{Invisibility Purge}:] Dispels invisibility within 5 ft./level.
\item[\linkspell{Locate Object}:] Senses direction toward object (specific or type).
\item[\linkspell{Magic Circle against Chaos/Evil/Good/Law}:] As protection spells, but 10-ft. radius and 10 min./level.
\item[\linkspell{Magic Vestment}:] Armor or shield gains +1 enhancement per four level
\item[\linkspell{Meld into Stone}:] You and your gear merge with stone.
\item[\linkspell{Obscure Object}:] Masks object against scrying.
\item[\linkspell{Prayer}:] Allies +1 bonus on most rolls, enemies –1 penalty.
\item[\linkspell{Protection from Energy}:] Absorb 12 points/level of damage from one kind of energy.
\item[\linkspell{Remove Blindness/Deafness}:] Cures normal or magical conditions.
\item[\linkspell{Remove Curse}:] Frees object or person from curse.
\item[\linkspell{Remove Disease}:] Cures all diseases affecting subject.
\item[\linkspell{Searing Light}:] Ray deals 1d8/two levels damage, more against undead.
\item[\linkspell{Speak with Dead}:] Corpse answers one question/two levels.
\item[\linkspell{Stone Shape}:] Sculpts stone into any shape.
\item[\linkspell{Summon Monster III}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Water Breathing}:] Subjects can breathe underwater.
\item[\linkspell{Water Walk}:] Subject treads on water as if solid.
\item[\linkspell{Wind Wall}:] Deflects arrows, smaller creatures, and gases.
\end{description*}

\subsection{4th-Level Cleric Spells}
\begin{description*}
\item[\linkspell{Air Walk}:] Subject treads on air as if solid (climb at 45-degree angle).
\item[\linkspell{Control Water}:] Raises or lowers bodies of water.
\item[\linkspell{Cure Critical Wounds}:] Cures 4d8 damage +1/level (max +20).
\item[\linkspell{Death Ward}:] Grants immunity to death spells and negative energy effects.
\item[\linkspell{Dimensional Anchor}:] Bars extradimensional movement.
\item[\linkspell{Discern Lies}:] Reveals deliberate falsehoods.
\item[\linkspell{Dismissal}:] Forces a creature to return to native plane.
\item[\linkspell{Divination}:] Provides useful advice for specific proposed actions.
\item[\linkspell{Divine Power}:] You gain attack bonus, +6 to Str, and 1 hp/level.
\item[\linkspell{Freedom of Movement}:] Subject moves normally despite impediments.
\item[\linkspell{Giant Vermin}:] Turns centipedes, scorpions, or spiders into giant vermin.
\item[\linkspell{Imbue with Spell Ability}:] Transfer spells to subject.
\item[\linkspell{Inflict Critical Wounds}:] Touch attack, 4d8 damage +1/level (max +20).
\item[\linkspell{Magic Weapon, Greater}:] +1 bonus/four levels (max +5).
\item[\linkspell{Neutralize Poison}:] Immunizes subject against poison, detoxifies venom in or on subject.
\item[\linkspell{Planar Ally, Lesser}:] Exchange services with a 6 HD extraplanar creature.
\item[\linkspell{Poison}:] Touch deals 1d10 Con damage, repeats in 1 min.
\item[\linkspell{Repel Vermin}:] Insects, spiders, and other vermin stay 10 ft. away.
\item[\linkspell{Restoration}:] Restores level and ability score drains.
\item[\linkspell{Sending}:] Delivers short message anywhere, instantly.
\item[\linkspell{Spell Immunity}:] Subject is immune to one spell per four levels.
\item[\linkspell{Summon Monster IV}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Tongues}:] Speak any language.
\end{description*}

\subsection{5th-Level Cleric Spells}
\begin{description*}
\item[\linkspell{Atonement}:] Removes burden of misdeeds from subject.
\item[\linkspell{Break Enchantment}:] Frees subjects from enchantments, alterations, curses, and petrification.
\item[\linkspell{Command, Greater}:] As command, but affects one subject/level.
\item[\linkspell{Commune}:] Deity answers one yes-or-no question/level.
\item[\linkspell{Cure Light Wounds, Mass}:] Cures 1d8 damage +1/level for many creatures.
\item[\linkspell{Dispel Chaos/Evil/Good/Law}:] +4 bonus against attacks.
\item[\linkspell{Disrupting Weapon}:] Melee weapon destroys undead.
\item[\linkspell{Flame Strike}:] Smite foes with divine fire (1d6/level damage).
\item[\linkspell{Hallow}:] Designates location as holy.
\item[\linkspell{Inflict Light Wounds, Mass}:] Deals 1d8 damage +1/level to many creatures.
\item[\linkspell{Insect Plague}:] Locust swarms attack creatures.
\item[\linkspell{Mark of Justice}:] Designates action that will trigger curse on subject.
\item[\linkspell{Plane Shift}:] As many as eight subjects travel to another plane.
\item[\linkspell{Raise Dead}:] Restores life to subject who died as long as one day/level ago.
\item[\linkspell{Righteous Might}:] Your size increases, and you gain combat bonuses.
\item[\linkspell{Scrying}:] Spies on subject from a distance.
\item[\linkspell{Slay Living}:] Touch attack kills subject.
\item[\linkspell{Spell Resistance}:] Subject gains SR 12 + level.
\item[\linkspell{Summon Monster V}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Symbol of Pain}:] Triggered rune wracks nearby creatures with pain.
\item[\linkspell{Symbol of Sleep}:] Triggered rune puts nearby creatures into catatonic slumber.
\item[\linkspell{True Seeing}:] Lets you see all things as they really are.
\item[\linkspell{Unhallow}:] Designates location as unholy.
\item[\linkspell{Wall of Stone}:] Creates a stone wall that can be shaped.
\end{description*}

\subsection{6th-Level Cleric Spells}
\begin{description*}
\item[\linkspell{Animate Objects}:] Objects attack your foes.
\item[\linkspell{Antilife Shell}:] 10-ft. field hedges out living creatures.
\item[\linkspell{Banishment}:] Banishes 2 HD/level of extraplanar creatures.
\item[\linkspell{Bear’s Endurance, Mass}:] As bear’s endurance, affects one subject/level.
\item[\linkspell{Blade Barrier}:] Wall of blades deals 1d6/level damage.
\item[\linkspell{Bull’s Strength, Mass}:] As bull’s strength, affects one subject/level.
\item[\linkspell{Create Undead}:] Create ghouls, ghasts, mummies, or mohrgs.
\item[\linkspell{Cure Moderate Wounds, Mass}:] Cures 2d8 damage +1/level for many creatures.
\item[\linkspell{Dispel Magic, Greater}:] As dispel magic, but up to +20 on check.
\item[\linkspell{Eagle’s Splendor, Mass}:] As eagle’s splendor, affects one subject/level.
\item[\linkspell{Find the Path}:] Shows most direct way to a location.
\item[\linkspell{Forbiddance}:] Blocks planar travel, damages creatures of different alignment.
\item[\linkspell{Geas/Quest}:] As lesser geas, plus it affects any creature.
\item[\linkspell{Glyph of Warding, Greater}:] As glyph of warding, but up to 10d8 damage or 6th-level spell.
\item[\linkspell{Harm}:] Deals 10 points/level damage to target.
\item[\linkspell{Heal}:] Cures 10 points/level of damage, all diseases and mental conditions.
\item[\linkspell{Heroes’ Feast}:] Food for one creature/level cures and grants combat bonuses.
\item[\linkspell{Inflict Moderate Wounds, Mass}:] Deals 2d8 damage +1/level to many creatures.
\item[\linkspell{Owl’s Wisdom, Mass}:] As owl’s wisdom, affects one subject/level.
\item[\linkspell{Planar Ally}:] As lesser planar ally, but up to 12 HD.
\item[\linkspell{Summon Monster VI}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Symbol of Fear}:] Triggered rune panics nearby creatures.
\item[\linkspell{Symbol of Persuasion}:] Triggered rune charms nearby creatures.
\item[\linkspell{Undeath to Death}:] Destroys 1d4 HD/level undead (max 20d4).
\item[\linkspell{Wind Walk}:] You and your allies turn vaporous and travel fast.
\item[\linkspell{Word of Recall}:] Teleports you back to designated place.
\end{description*}

\subsection{7th-Level Cleric Spells}
\begin{description*}
\item[\linkspell{Blasphemy}:] Kills, paralyzes, weakens, or dazes nonevil subjects.
\item[\linkspell{Control Weather}:] Changes weather in local area.
\item[\linkspell{Cure Serious Wounds, Mass}:] Cures 3d8 damage +1/level for many creatures.
\item[\linkspell{Destruction}:] Kills subject and destroys remains.
\item[\linkspell{Dictum}:] Kills, paralyzes, slows, or deafens nonlawful subjects.
\item[\linkspell{Ethereal Jaunt}:] You become ethereal for 1 round/level.
\item[\linkspell{Holy Word}:] Kills, paralyzes, blinds, or deafens nongood subjects.
\item[\linkspell{Inflict Serious Wounds, Mass}:] Deals 3d8 damage +1/level to many creatures.
\item[\linkspell{Refuge}:] Alters item to transport its possessor to you.
\item[\linkspell{Regenerate}:] Subject’s severed limbs grow back, cures 4d8 damage +1/level (max +35).
\item[\linkspell{Repulsion}:] Creatures can’t approach you.
\item[\linkspell{Restoration, Greater}:] As restoration, plus restores all levels and ability scores.
\item[\linkspell{Resurrection}:] Fully restore dead subject.
\item[\linkspell{Scrying, Greater}:] As scrying, but faster and longer.
\item[\linkspell{Summon Monster VII}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Symbol of Stunning}:] Triggered rune stuns nearby creatures.
\item[\linkspell{Symbol of Weakness}:] Triggered rune weakens nearby creatures.
\item[\linkspell{Word of Chaos}:] Kills, confuses, stuns, or deafens nonchaotic subjects.
\end{description*}

\subsection{8th-Level Cleric Spells}
\begin{description*}
\item[\linkspell{Antimagic Field}:] Negates magic within 10 ft.
\item[\linkspell{Cloak of Chaos}:] +4 to AC, +4 resistance, and SR 25 against lawful spells.
\item[\linkspell{Create Greater Undead}:] Create shadows, wraiths, spectres, or devourers.
\item[\linkspell{Cure Critical Wounds, Mass}:] Cures 4d8 damage +1/level for many creatures.
\item[\linkspell{Dimensional Lock}:] Teleportation and interplanar travel blocked for one day/level.
\item[\linkspell{Discern Location}:] Reveals exact location of creature or object.
\item[\linkspell{Earthquake}:] Intense tremor shakes 5-ft./level radius.
\item[\linkspell{Fire Storm}:] Deals 1d6/level fire damage.
\item[\linkspell{Holy Aura}:] +4 to AC, +4 resistance, and SR 25 against evil spells.
\item[\linkspell{Planar Ally, Greater}:] As lesser planar ally, but up to 18 HD.
\item[\linkspell{Inflict Critical Wounds, Mass}:] Deals 4d8 damage +1/level to many creatures.
\item[\linkspell{Shield of Law}:] +4 to AC, +4 resistance, and SR 25 against chaotic spells.
\item[\linkspell{Spell Immunity, Greater}:] As spell immunity, but up to 8th-level spells.
\item[\linkspell{Summon Monster VIII}:] Calls extraplanar creature to fight for you.
\item[\linkspell{Symbol of Death}:] Triggered rune slays nearby creatures.
\item[\linkspell{Symbol of Insanity}:] Triggered rune renders nearby creatures insane.
\item[\linkspell{Unholy Aura}:] +4 to AC, +4 resistance, and SR 25 against good spells.
\end{description*}

\subsection{9th-Level Cleric Spells}
\begin{description*}
\item[\linkspell{Astral Projection}:] Projects you and companions onto Astral Plane.
\item[\linkspell{Energy Drain}:] Subject gains 2d4 negative levels.
\item[\linkspell{Etherealness}:] Travel to Ethereal Plane with companions.
\item[\linkspell{Gate}:] Connects two planes for travel or summoning.
\item[\linkspell{Heal, Mass}:] As heal, but with several subjects.
\item[\linkspell{Implosion}:] Kills one creature/round.
\item[\linkspell{Miracle}:] Requests a deity’s intercession.
\item[\linkspell{Soul Bind}:] Traps newly dead soul to prevent resurrection.
\item[\linkspell{Storm of Vengeance}:] Storm rains acid, lightning, and hail.
\item[\linkspell{Summon Monster IX}:] Calls extraplanar creature to fight for you.
\item[\linkspell{True Resurrection}:] As resurrection, plus remains aren’t needed.
\end{description*}

\end{multicols}