%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Death Master Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}

\subsection{0-Level Death Master Spells (Cantrips)}
\begin{description*}
\item[\linkspell{Arcane Mark}:] Inscribes a personal rune (visible or invisible).
\item[\linkspell{Dancing Lights}:] Creates torches or other lights.
\item[\linkspell{Daze}:] Humanoid creature of 4 HD or less loses next action.
\item[\linkspell{Detect Magic}:] Detects spells and magic items within 60 ft.
\item[\linkspell{Detect Poison}:] Detects poison in one creature or object.
\item[\linkspell{Disrupt Undead}:] Deals ld6 damage to one undead.
\item[\linkspell{Flare}:] Dazzles one creature (-1 penalty on attack rolls).
\item[\linkspell{Ghost Sound}:] Figment sounds.
\item[\linkspell{Inflict Minor Wounds}:] Touch attack, 1 point of damage.
\item[\linkspell{Light}:] Object shines like a torch.
\item[\linkspell{Mage Hand}:] 5-pound telekinesis.
\item[\linkspell{Mending}:] Makes minor repairs on an object.
\item[\linkspell{Prestidigitation}:] Performs minor tricks.
\item[\linkspell{Ray of Frost}:] Ray deals ld3 cold damage
\item[\linkspell{Read Magic}:] Read scrolls and spellbooks.
\item[\linkspell{Resistance}:] Subject gains +1 on saving throws.
\item[\linkspell{Touch of Fatigue}:] Touch attack fatigues target.
\item[\linkspell{Virtue}:] Subject gains 1 temporary hp.
\end{description*}

\subsection{1st-Level Death Master Spells}
\begin{description*}
\item[\linkspell{Alarm}:] Wards an area for 2 hours/level.
\item[\linkspell{Bane}:] Enemies take - 1 on attack rolls and saves against fear.
\item[\linkspell{Cause Fear}:] One creature of 5 HD or less flees for 1d4 rounds.
\item[\linkspell{Chill Touch}:] One touch/level deals ld6 damage and possibly 1 Str damage.
\item[\linkspell{Command}:] One subject obeys selected command for 1 round
\item[\linkspell{Comprehend Languages}:] You understand all spoken and written languages.
\item[\linkspell{Curse Water}:] Makes unholy water.
\item[\linkspell{Deathwatch}:] Reveals how near death subjects within 30 ft. are.
\item[\linkspell{Detect Chaos/Evil/Good/Law}:] Reveals creatures, spells, or objects of selected alignment.
\item[\linkspell{Detect Undead}:] Reveals undead within 60 ft.
\item[\linkspell{Doom}:] One subject takes -2 on attack rolls, damage rolls, saves, and checks.
\item[\linkspell{Entropic Shield}:] Ranged attacks against you have 20\% miss chance.
\item[\linkspell{Expeditious Retreat}:] Your speed increases by 30 ft.
\item[\linkspell{Grease}:] Makes 10-ft. square or one object slippery.
\item[\linkspell{Hide from Undead}:] Undead can't perceive one subject/level.
\item[\linkspell{Identify}:] Determines properties of magic item.
\item[\linkspell{Inflict Light Wounds}:] Touch deals ld8 damage +1/ level (max +5).
\item[\linkspell{Magic Fang}:] One natural weapon of subject creature gets +1 on attack and damage rolls.
\item[\linkspell{Magic Stone}:] Three stones gain +1 on attack rolls, deal ld6+1 damage.
\item[\linkspell{Magic Weapon}:] Weapon gains +1 bonus.
\item[\linkspell{Obscuring Mist}:] Fog surrounds you.
\item[\linkspell{Protection from Good}:] +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item[\linkspell{Ray of Enfeeblement}:] Ray deals ld6 +1 per two levels Str damage.
\item[\linkspell{Sanctuary}:] Opponents can't attack you, and you can't attack.
\item[\linkspell{Shield}:] Invisible disc gives +4 to AC, blocks magic missiles
\item[\linkspell{Shocking Grasp}:] Touch delivers ld6/level electricity damage (max 5d6).
\item[\linkspell{Unseen Servant}:] Invisible force obeys your commands.
\end{description*}

\subsection{2nd-Level Death Master Spells}
\begin{description*}
\item[\linkspell{Align Weapon}:] Weapon becomes good, evil, lawful, or chaotic.
\item[\linkspell{Alter Self}:] Assume form of a similar creature.
\item[\linkspell{Animate Dead}:] Creates undead skeletons and zombies.
\item[\linkspell{Blindness/Deafness}:] Makes subject blinded or deafened.
\item[\linkspell{Blur}:] Attacks miss subject 20\% of the time.
\item[\linkspell{Chill Metal}:] Cold metal damages those who touch it.
\item[\linkspell{Command Undead}:] Undead creature obeys your commands.
\item[\linkspell{Darkness}:] 20-ft. radius of supernatural shadow.
\item[\linkspell{Darkvision}:] See 60 ft. in total darkness.
\item[\linkspell{Daze Monster}:] Living creature of 6 HD or less loses next action.
\item[\linkspell{Death Knell}:] Kills dying creature; you gain 1d8 temporary hp, +2 to Str, and +1 level.
\item[\linkspell{Desecrate}:] Fills area with negative energy, making undead stronger.
\item[\linkspell{Detect Thoughts}:] Allows "listening" to surface thoughts.
\item[\linkspell{False Life}:] Gain 1d10 temporary hp +1/level (max +10).
\item[\linkspell{Fog Cloud}:] Fog obscures vision.
\item[\linkspell{Gentle Repose}:] Preserves one corpse.
\item[\linkspell{Ghoul Touch}:] Paralyzes one subject, which exudes stench.
\item[\linkspell{Tasha's Hideous Laughter}:] Subject loses actions for 1 round/level.
\item[\linkspell{Hold Person}:] Paralyzes one humanoid for 1 round/level.
\item[\linkspell{Inflict Moderate Wounds}:] Touch attack, 2d8 damage +1/level (max +10).
\item[\linkspell{Locate Object}:] Senses direction toward object (specific or type).
\item[\linkspell{Make Whole}:] Repairs an object.
\item[\linkspell{Misdirection}:] Misleads divinations for one creature or object.
\item[\linkspell{Resist Energy}:] Ignores first 10 (or more) points of damage/attack from specified energy type.
\item[\linkspell{Restoration, Lesser}:] Dispels magical ability penalty or repairs 1d4 ability damage.
\item[\linkspell{Scare}:] Panics creatures of less than 6 HD.
\item[\linkspell{See Invisibility}:] Reveals invisible creatures or objects.
\item[\linkspell{Shatter}:] Sonic vibration damages objects or crystalline creatures.
\item[\linkspell{Silence}:] Negates sound in 20-ft. radius.
\item[\linkspell{Soften Earth and Stone}:] Turns stone to clay or dirt to sand or mud.
\item[\linkspell{Spectral Hand}:] Creates disembodied glowing hand to deliver touch attacks.
\item[\linkspell{Spider Climb}:] Grants ability to walk on walls and ceilings.
\item[\linkspell{Summon Swarm}:] Summons swarm of bats, rats, or spiders.
\item[\linkspell{Touch of Idiocy}:] Subject takes ld6 points of Int, Wis, and Cha damage.
\item[\linkspell{Undetectable Alignment}:] Conceals alignment for 24 hours.
\item[\linkspell{Web}:] Fills 20-ft.-radius spread with sticky spiderwebs.
\end{description*}

\subsection{3rd-Level Death Master Spells}
\begin{description*}
\item[\linkspell{Arcane Sight}:] Magical auras become visible to you.
\item[\linkspell{Bestow Curse}:] -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action.
\item[\linkspell{Contagion}:] Infects subject with chosen disease.
\item[\linkspell{Deep Slumber}:] Puts 10 HD of creatures to sleep.
\item[\linkspell{Deeper Darkness}:] Object sheds supernatural shadow in 60-ft. radius.
\item[\linkspell{Diminish Plants}:] Reduces size or blights growth of normal plants.
\item[\linkspell{Dispel Magic}:] Cancels magical spells and effects.
\item[\linkspell{Gaseous Form}:] Subject becomes insubstantial and can fly slowly.
\item[\linkspell{Halt Undead}:] Immobilizes undead for 1 round/level.
\item[\linkspell{Inflict Serious Wounds}:] Touch attack, 3d8 damage +1/level (max +15).
\item[\linkspell{Magic Circle Against Good}:] As protection spells, but 10-ft. radius and 10 min/level.
\item[\linkspell{Magic Fang, Greater}:] One natural weapon of subject creature gets +1/four levels on attack and damage rolls (max +5).
\item[\linkspell{Magic Weapon, Greater}:] +1/four levels (max +5).
\item[\linkspell{Meld into Stone}:] You and your gear merge with stone.
\item[\linkspell{Phantom Steed}:] Magic horse appears for 1 hour/level.
\item[\linkspell{Poison}:] Touch deals 1d10 Con damage, repeats in 1 min.
\item[\linkspell{Protection from Energy}:] Absorb 12 points/level of damage from one kind of energy.
\item[\linkspell{Ray of Exhaustion}:] Ray makes subject exhausted.
\item[\linkspell{Remove Curse}:] Frees object or person from curse.
\item[\linkspell{Slow}:] One subject/level takes only one action/round, - 1 to AC, reflex saves, and attack rolls.
\item[\linkspell{Speak with Dead}:] Corpse answers one question/ two levels.
\item[\linkspell{Stinking Cloud}:] Nauseating vapors, 1 round/level.
\item[\linkspell{Stone Shape}:] Sculpts stone into any shape.
\item[\linkspell{Vampiric Touch}:] Touch deals ld6/two levels damage; caster gains damage as hp.
\item[\linkspell{Wind Wall}:] Deflects arrows, smaller creatures, and gases.
\end{description*}

\subsection{4th-Level Death Master Spells}
\begin{description*}
\item[\linkspell{Arcane Eye}:] Invisible floating eye moves 30 ft./round.
\item[\linkspell{Charm Monster}:] Makes monster believe it is your ally.
\item[\linkspell{Crushing Despair}:] Subjects take -2 on attack rolls, damage rolls, saves, and checks.
\item[\linkspell{Death Ward}:] Grants immunity to death spells and negative energy effects.
\item[\linkspell{Detect Scrying}:] Alerts you of magical eavesdropping.
\item[\linkspell{Dimension Door}:] Teleports you a short distance.
\item[\linkspell{Dimensional Anchor}:] Bars extradimensional movement.
\item[\linkspell{Enervation}:] Subject gains ld4 negative levels.
\item[\linkspell{Evard's Black Tentacles}:] Tentacles grapple all within 20-ft. spread.
\item[\linkspell{Fear}:] Subjects within cone flee for 1 round/level.
\item[\linkspell{Giant Vermin}:] Turns centipedes, scorpions, or spiders into giant vermin.
\item[\linkspell{Globe of Invulnerability, Lesser}:] Stops 1st- through 3rd-level spell effects.
\item[\linkspell{Ice Storm}:] Hail deals 5d6 damage in cylinder 40 ft. across.
\item[\linkspell{Inflict Critical Wounds}:] Touch attack, 4d8 damage +1/level (max +20).
\item[\linkspell{Phantasmal Killer}:] Fearsome illusion kills subject or deals 3d6 damage.
\item[\linkspell{Scrying}:] Spies on subject from a distance.
\item[\linkspell{Solid Fog}:] Blocks vision and slows movement.
\item[\linkspell{Stoneskin}:] Ignore 10 points of damage per attack.
\item[\linkspell{Tongues}:] Speak any language.
\item[\linkspell{Wall of Ice}:] Ice plane creates wall with 15 hp +1/level, or hemisphere can trap creatures inside.
\end{description*}

\subsection{5th-Level Death Master Spells}
\begin{description*}
\item[\linkspell{Baleful Polymorph}:] Transforms subject into harmless animal.
\item[\linkspell{Blight}:] Withers one plant or deals 1d6/level damage to plant creature.
\item[\linkspell{Cloudkill}:] Kills 3 HD or less; 4-6 HD save or die, 6+ HD take Con damage.
\item[\linkspell{Command, Greater}:] As command, but affects one subject/level.
\item[\linkspell{Cone of Cold}:] 1d6/level cold damage.
\item[\linkspell{Create Undead}:] Create ghouls, ghasts, mummies, or mohrgs.
\item[\linkspell{Dispel Good}:] +4 bonus against attacks.
\item[\linkspell{Dominate Person}:] Controls humanoid telepathically.
\item[\linkspell{Hold Monster}:] As hold person, but any creature
\item[\linkspell{Inflict Light Wounds, Mass}:] Deals ld8 damage +1/ level to many creatures.
\item[\linkspell{Insect Plague}:] Locust swarms attack creatures.
\item[\linkspell{Magic Jar}:] Enables possession of another creature.
\item[\linkspell{Nightmare}:] Sends vision dealing 1d10 damage, fatigue.
\item[\linkspell{Slay Living}:] Touch attack kills subject.
\item[\linkspell{Symbol of Pain}:] Triggered rune wracks nearby creatures with pain.
\item[\linkspell{Unhallow}:] Designates location as unholy.
\item[\linkspell{Wall of Stone}:] Creates a stone wall that can be shaped.
\item[\linkspell{Waves of Fatigue}:] Several targets become fatigued.
\end{description*}

\subsection{6th-Level Death Master Spells}
\begin{description*}
\item[\linkspell{Acid Fog}:] Fog deals acid damage.
\item[\linkspell{Antilife Shell}:] 10-ft.-radius field hedges out living creatures.
\item[\linkspell{Blade Barrier}:] Wall of blades deals ld6/level damage.
\item[\linkspell{Circle of Death}:] Kills ld4/level HD of creatures.
\item[\linkspell{Control Undead}:] Undead don't attack you while under your command.
\item[\linkspell{Dispel Magic, Greater}:] As \linkspell{Dispel Magic}, but up to +20 on check.
\item[\linkspell{Eyebite}:] Target becomes panicked, sickened, and comatose.
\item[\linkspell{Harm}:] Deals 10 points/level damage to target.
\item[\linkspell{Inflict Moderate Wounds, Mass}:] Deals 2d8 damage +1/level to many creatures.
\item[\linkspell{Move Earth}:] Digs trenches and builds hills.
\item[\linkspell{Shadow Walk}:] Step into shadow to travel rapidly.
\item[\linkspell{Symbol of Fear}:] Triggered rune panics nearby creatures.
\item[\linkspell{Undeath to Death}:] Destroys ld4 HD/level undead (max 20d4).
\item[\linkspell{Word of Recall}:] \linkspell{Teleports} you back to designated place
\end{description*}

\subsection{7th-Level Death Master Spells}
\begin{description*}
\item[\linkspell{Arcane Sight, Greater}:] As \linkspell{Arcane Sight}, but also reveals magic effects on creatures and objects.
\item[\linkspell{Blasphemy}:] Kills, paralyzes, weakens, or dazes nonevil subjects.
\item[\linkspell{Creeping Doom}:] Swarms of centipedes attack at your command.
\item[\linkspell{Destruction}:] Kills subject and destroys remains.
\item[\linkspell{Ethereal Jaunt}:] You become ethereal for 1 round/level
\item[\linkspell{Finger of Death}:] Kills one subject.
\item[\linkspell{Hold Person, Mass}:] As \linkspell{Hold Person}, but all within 30 ft.
\item[\linkspell{Inflict Serious Wounds, Mass}:] Deals 3d8 damage +1/level to many creatures.
\item[\linkspell{Power Word Blind}:] Blinds creature with 200 hp or less.
\item[\linkspell{Repulsion}:] Creatures can't approach you.
\item[\linkspell{Scrying, Greater}:] As \linkspell{Scrying}, but faster and longer.
\item[\linkspell{Symbol of Stunning}:] Triggered rune stuns nearby creatures.
\item[\linkspell{Symbol of Weakness}:] Triggered rune weakens nearby creatures.
\item[\linkspell{True Seeing}:] Lets you see all things as they really are.
\item[\linkspell{Waves of Exhaustion}:] Several targets become exhausted.
\item[\linkspell{Word of Chaos}:] Kills, confuses, stuns, or deafens nonchaotic subjects.
\end{description*}

\subsection{8th-Level Death Master Spells}
\begin{description*}
\item[\linkspell{Antimagic Field}:] Negates magic within 10 ft.
\item[\linkspell{Antipathy}:] Object or location affected by spell repels certain creatures.
\item[\linkspell{Charm Monster, Mass}:] As \linkspell{Charm Monster}, but all within 30 ft.
\item[\linkspell{Clone}:] Duplicate awakens when original dies.
\item[\linkspell{Create Greater Undead}:] Create shadows, wraiths, spectres, or devourers.
\item[\linkspell{Discern Location}:] Reveals exact location of creature or object.
\item[\linkspell{Inflict Critical Wounds, Mass}:] Deals 4d8 damage +1/level to many creatures.
\item[\linkspell{Iron Body}:] Your body becomes living iron.
\item[\linkspell{Maze}:] Traps subject in extradimensional maze.
\item[\linkspell{Mind Blank}:] Subject is immune to mental/emotional magic and scrying.
\item[\linkspell{Power Word Stun}:] Stuns creature with 150 hp or less.
\item[\linkspell{Symbol of Death}:] Triggered rune slays nearby creatures.
\item[\linkspell{Temporal Stasis}:] Puts subject into suspended animation.
\item[\linkspell{Trap the Soul}:] Imprisons subject within gem.
\item[\linkspell{Unholy Aura}:] +4 to AC, +4 resistance, and SR 25 against good spells.
\end{description*}

\subsection{9th-Level Death Master Spells}
\begin{description*}
\item[\linkspell{Astral Projection}:] Projects you and companions onto Astral Plane.
\item[\linkspell{Dominate Monster}:] As \linkspell{Dominate Person}, but any creature.
\item[\linkspell{Energy Drain}:] Subject gains 2d4 negative levels.
\item[\linkspell{Etherealness}:] Travel to Ethereal Plane with companions.
\item[\linkspell{Foresight}:] "Sixth sense" warns of impending danger.
\item[\linkspell{Hold Monster, Mass}:] As \linkspell{Hold Monster}, but all within 30 ft.
\item[\linkspell{Implosion}:] Kills one creature/round.
\item[\linkspell{Power Word Kill}:] Kills one creature with 100 hp or less.
\item[\linkspell{Shapechange}:] Transforms you into any creature, and change forms once per round.
\item[\linkspell{Soul Bind}:] Traps newly dead soul to prevent resurrection.
\item[\linkspell{Wail of the Banshee}:] Kills one creature/level.
\item[\linkspell{Weird}:] As \linkspell{Phantasmal Killer}, but affects all within 30 ft.
\end{description*}

\end{multicols}