%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Druid Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}

\subsection{0-Level Druid Spells (Orisons)}
\begin{description*}
\item[\linkspell{Create Water}:] Creates 2 gallons/level of pure water.
\item[\linkspell{Cure Minor Wounds}:] Cures 1 point of damage.
\item[\linkspell{Detect Magic}:] Detects spells and magic items within 60 ft.
\item[\linkspell{Detect Poison}:] Detects poison in one creature or object.
\item[\linkspell{Flare}:] Dazzles one creature (–1 penalty on attack rolls).
\item[\linkspell{Guidance}:] +1 on one attack roll, saving throw, or skill check.
\item[\linkspell{Know Direction}:] You discern north.
\item[\linkspell{Light}:] Object shines like a torch.
\item[\linkspell{Mending}:] Makes minor repairs on an object.
\item[\linkspell{Purify Food and Drink}:] Purifies 1 cu. ft./level of food or water.
\item[\linkspell{Read Magic}:] Read scrolls and spellbooks.
\item[\linkspell{Resistance}:] Subject gains +1 bonus on saving throws.
\item[\linkspell{Virtue}:] Subject gains 1 temporary hp.
\end{description*}

\subsection{1st-Level Druid Spells}
\begin{description*}
\item[\linkspell{Calm Animals}:] Calms (2d4 + level) HD of animals.
\item[\linkspell{Charm Animal}:] Makes one animal your friend.
\item[\linkspell{Cure Light Wounds}:] Cures 1d8 damage +1/level (max +5).
\item[\linkspell{Detect Animals or Plants}:] Detects kinds of animals or plants.
\item[\linkspell{Detect Snares and Pits}:] Reveals natural or primitive traps.
\item[\linkspell{Endure Elements}:] Exist comfortably in hot or cold environments.
\item[\linkspell{Entangle}:] Plants entangle everyone in 40-ft.-radius.
\item[\linkspell{Faerie Fire}:] Outlines subjects with light, canceling blur, concealment, and the like.
\item[\linkspell{Goodberry}:] 2d4 berries each cure 1 hp (max 8 hp/24 hours).
\item[\linkspell{Hide from Animals}:] Animals can’t perceive one subject/level.
\item[\linkspell{Jump}:] Subject gets bonus on Jump checks.
\item[\linkspell{Longstrider}:] Your speed increases by 10 ft.
\item[\linkspell{Magic Fang}:] One natural weapon of subject creature gets +1 on attack and damage rolls.
\item[\linkspell{Magic Stone}:] Three stones gain +1 on attack rolls, deal 1d6+1 damage.
\item[\linkspell{Obscuring Mist}:] Fog surrounds you.
\item[\linkspell{Pass without Trace}:] One subject/level leaves no tracks.
\item[\linkspell{Produce Flame}:] 1d6 damage +1/level, touch or thrown.
\item[\linkspell{Shillelagh}:] Cudgel or quarterstaff becomes +1 weapon (1d10 damage) for 1 min./level.
\item[\linkspell{Speak with Animals}:] You can communicate with animals.
\item[\linkspell{Summon Nature’s Ally I}:] Calls creature to fight.
\end{description*}

\subsection{2nd-Level Druid Spells}
\begin{description*}
\item[\linkspell{Animal Messenger}:] Sends a Tiny animal to a specific place.
\item[\linkspell{Animal Trance}:] Fascinates 2d6 HD of animals.
\item[\linkspell{Barkskin}:] Grants +2 (or higher) enhancement to natural armor.
\item[\linkspell{Bear’s Endurance}:] Subject gains +4 to Con for 1 min./level.
\item[\linkspell{Bull’s Strength}:] Subject gains +4 to Str for 1 min./level.
\item[\linkspell{Cat’s Grace}:] Subject gains +4 to Dex for 1 min./level.
\item[\linkspell{Chill Metal}:] Cold metal damages those who touch it.
\item[\linkspell{Delay Poison}:] Stops poison from harming subject for 1 hour/level.
\item[\linkspell{Fire Trap}:] Opened object deals 1d4 +1/level damage.
\item[\linkspell{Flame Blade}:] Touch attack deals 1d8 +1/two levels damage.
\item[\linkspell{Flaming Sphere}:] Creates rolling ball of fire, 2d6 damage, lasts 1 round/level.
\item[\linkspell{Fog Cloud}:] Fog obscures vision.
\item[\linkspell{Gust of Wind}:] Blows away or knocks down smaller creatures.
\item[\linkspell{Heat Metal}:] Make metal so hot it damages those who touch it.
\item[\linkspell{Hold Animal}:] Paralyzes one animal for 1 round/level.
\item[\linkspell{Owl’s Wisdom}:] Subject gains +4 to Wis for 1 min./level.
\item[\linkspell{Reduce Animal}:] Shrinks one willing animal.
\item[\linkspell{Resist Energy}:] Ignores 10 (or more) points of damage/attack from specified energy type.
\item[\linkspell{Restoration, Lesser}:] Dispels magical ability penalty or repairs 1d4 ability damage.
\item[\linkspell{Soften Earth and Stone}:] Turns stone to clay or dirt to sand or mud.
\item[\linkspell{Spider Climb}:] Grants ability to walk on walls and ceilings.
\item[\linkspell{Summon Nature’s Ally II}:] Calls creature to fight.
\item[\linkspell{Summon Swarm}:] Summons swarm of bats, rats, or spiders.
\item[\linkspell{Tree Shape}:] You look exactly like a tree for 1 hour/level.
\item[\linkspell{Warp Wood}:] Bends wood (shaft, handle, door, plank).
\item[\linkspell{Wood Shape}:] Rearranges wooden objects to suit you.
\end{description*}

\subsection{3rd-Level Druid Spells}
\begin{description*}
\item[\linkspell{Call Lightning}:] Calls down lightning bolts (3d6 per bolt) from sky.
\item[\linkspell{Contagion}:] Infects subject with chosen disease.
\item[\linkspell{Cure Moderate Wounds}:] Cures 2d8 damage +1/level (max +10).
\item[\linkspell{Daylight}:] 60-ft. radius of bright light.
\item[\linkspell{Diminish Plants}:] Reduces size or blights growth of normal plants.
\item[\linkspell{Dominate Animal}:] Subject animal obeys silent mental commands.
\item[\linkspell{Magic Fang, Greater}:] One natural weapon of subject creature gets +1/three levels on attack and damage rolls (max +5).
\item[\linkspell{Meld into Stone}:] You and your gear merge with stone.
\item[\linkspell{Neutralize Poison}:] Immunizes subject against poison, detoxifies venom in or on subject.
\item[\linkspell{Plant Growth}:] Grows vegetation, improves crops.
\item[\linkspell{Poison}:] Touch deals 1d10 Con damage, repeats in 1 min.
\item[\linkspell{Protection from Energy}:] Absorb 12 points/level of damage from one kind of energy.
\item[\linkspell{Quench}:] Extinguishes nonmagical fires or one magic item.
\item[\linkspell{Remove Disease}:] Cures all diseases affecting subject.
\item[\linkspell{Sleet Storm}:] Hampers vision and movement.
\item[\linkspell{Snare}:] Creates a magic booby trap.
\item[\linkspell{Speak with Plants}:] You can talk to normal plants and plant creatures.
\item[\linkspell{Spike Growth}:] Creatures in area take 1d4 damage, may be slowed.
\item[\linkspell{Stone Shape}:] Sculpts stone into any shape.
\item[\linkspell{Summon Nature’s Ally III}:] Calls creature to fight.
\item[\linkspell{Water Breathing}:] Subjects can breathe underwater.
\item[\linkspell{Wind Wall}:] Deflects arrows, smaller creatures, and gases.
\end{description*}

\subsection{4th-Level Druid Spells}
\begin{description*}
\item[\linkspell{Air Walk}:] Subject treads on air as if solid (climb at 45-degree angle).
\item[\linkspell{Antiplant Shell}:] Keeps animated plants at bay.
\item[\linkspell{Blight}:] Withers one plant or deals 1d6/level damage to plant creature.
\item[\linkspell{Command Plants}:] Sway the actions of one or more plant creatures.
\item[\linkspell{Control Water}:] Raises or lowers bodies of water.
\item[\linkspell{Cure Serious Wounds}:] Cures 3d8 damage +1/level (max +15).
\item[\linkspell{Dispel Magic}:] Cancels spells and magical effects.
\item[\linkspell{Flame Strike}:] Smite foes with divine fire (1d6/level damage).
\item[\linkspell{Freedom of Movement}:] Subject moves normally despite impediments.
\item[\linkspell{Giant Vermin}:] Turns centipedes, scorpions, or spiders into giant vermin.
\item[\linkspell{Ice Storm}:] Hail deals 5d6 damage in cylinder 40 ft. across.
\item[\linkspell{Reincarnate}:] Brings dead subject back in a random body.
\item[\linkspell{Repel Vermin}:] Insects, spiders, and other vermin stay 10 ft. away.
\item[\linkspell{Rusting Grasp}:] Your touch corrodes iron and alloys.
\item[\linkspell{Scrying}:] Spies on subject from a distance.
\item[\linkspell{Spike Stones}:] Creatures in area take 1d8 damage, may be slowed.
\item[\linkspell{Summon Nature’s Ally IV}:] Calls creature to fight.
\end{description*}

\subsection{5th-Level Druid Spells}
\begin{description*}
\item[\linkspell{Animal Growth}:] Animal Growth
\item[\linkspell{Atonement}:] Atonement
\item[\linkspell{Awaken}:] Awaken
\item[\linkspell{Baleful Polymorph}:] Baleful Polymorph
\item[\linkspell{Call Lightning Storm}:] Call Lightning Storm
\item[\linkspell{Commune with Nature}:] Commune with Nature
\item[\linkspell{Control Winds}:] Control Winds
\item[\linkspell{Cure Critical Wounds}:] Cure Critical Wounds
\item[\linkspell{Death Ward}:] Grants immunity to all death spells and negative energy effects.
\item[\linkspell{Hallow}:] Designates location as holy.
\item[\linkspell{Insect Plague}:] Locust swarms attack creatures.
\item[\linkspell{Stoneskin}:] Ignore 10 points of damage per attack.
\item[\linkspell{Summon Nature’s Ally V}:] Calls creature to fight.
\item[\linkspell{Transmute Mud to Rock}:] Transforms two 10-ft. cubes per level.
\item[\linkspell{Transmute Rock to Mud}:] Transforms two 10-ft. cubes per level.
\item[\linkspell{Tree Stride}:] Step from one tree to another far away.
\item[\linkspell{Unhallow}:] Designates location as unholy.
\item[\linkspell{Wall of Fire}:] Deals 2d4 fire damage out to 10 ft. and 1d4 out to 20 ft. Passing through wall deals 2d6 damage +1/level.
\item[\linkspell{Wall of Thorns}:] Thorns damage anyone who tries to pass.
\end{description*}

\subsection{6th-Level Druid Spells}
\begin{description*}
\item[\linkspell{Antilife Shell}:] 10-ft.-radius field hedges out living creatures.
\item[\linkspell{Bear’s Endurance, Mass}:] As bear’s endurance, affects one subject/level.
\item[\linkspell{Bull’s Strength, Mass}:] As bull’s strength, affects one subject/level.
\item[\linkspell{Cat’s Grace, Mass}:] As cat’s grace, affects one subject/level.
\item[\linkspell{Cure Light Wounds, Mass}:] Cures 1d8 damage +1/level for many creatures.
\item[\linkspell{Dispel Magic, Greater}:] As dispel magic, but +20 on check.
\item[\linkspell{Find the Path}:] Shows most direct way to a location.
\item[\linkspell{Fire Seeds}:] Acorns and berries become grenades and bombs.
\item[\linkspell{Ironwood}:] Magic wood is strong as steel.
\item[\linkspell{Liveoak}:] Oak becomes treant guardian.
\item[\linkspell{Move Earth}:] Digs trenches and builds hills.
\item[\linkspell{Owl’s Wisdom, Mass}:] As owl’s wisdom, affects one subject/level.
\item[\linkspell{Repel Wood}:] Pushes away wooden objects.
\item[\linkspell{Spellstaff}:] Stores one spell in wooden quarterstaff.
\item[\linkspell{Stone Tell}:] Talk to natural or worked stone.
\item[\linkspell{Summon Nature’s Ally VI}:] Calls creature to fight.
\item[\linkspell{Transport via Plants}:] Move instantly from one plant to another of the same kind.
\item[\linkspell{Wall of Stone}:]  Creates a stone wall that can be shaped.
\end{description*}

\subsection{7th-Level Druid Spells}
\begin{description*}
\item[\linkspell{Animate Plants}:] One or more plants animate and fight for you.
\item[\linkspell{Changestaff}:] Your staff becomes a treant on command.
\item[\linkspell{Control Weather}:] Changes weather in local area.
\item[\linkspell{Creeping Doom}:] Swarms of centipedes attack at your command.
\item[\linkspell{Cure Moderate Wounds, Mass}:] Cures 2d8 damage +1/level for many creatures.
\item[\linkspell{Fire Storm}:] Deals 1d6/level fire damage.
\item[\linkspell{Heal}:] Cures 10 points/level of damage, all diseases and mental conditions.
\item[\linkspell{Scrying, Greater}:] As scrying, but faster and longer.
\item[\linkspell{Summon Nature’s Ally VII}:] Calls creature to fight.
\item[\linkspell{Sunbeam}:] Beam blinds and deals 4d6 damage.
\item[\linkspell{Transmute Metal to Wood}:] Metal within 40 ft. becomes wood.
\item[\linkspell{True Seeing}:] Lets you see all things as they really are.
\item[\linkspell{Wind Walk}:] You and your allies turn vaporous and travel fast.
\end{description*}

\subsection{8th-Level Druid Spells}
\begin{description*}
\item[\linkspell{Animal Shapes}:] One ally/level polymorphs into chosen animal.
\item[\linkspell{Control Plants}:] Control actions of one or more plant creatures.
\item[\linkspell{Cure Serious Wounds, Mass}:] Cures 3d8 damage +1/level for many creatures.
\item[\linkspell{Earthquake}:] Intense tremor shakes 5-ft./level radius.
\item[\linkspell{Finger of Death}:] Kills one subject.
\item[\linkspell{Repel Metal or Stone}:] Pushes away metal and stone.
\item[\linkspell{Reverse Gravity}:] Objects and creatures fall upward.
\item[\linkspell{Summon Nature’s Ally VIII}:] Calls creature to fight.
\item[\linkspell{Sunburst}:] Blinds all within 10 ft., deals 6d6 damage.
\item[\linkspell{Whirlwind}:] Cyclone deals damage and can pick up creatures.
\item[\linkspell{Word of Recall}:] Teleports you back to designated place.
\end{description*}

\subsection{9th-Level Druid Spells}
\begin{description*}
\item[\linkspell{Antipathy}:] Object or location affected by spell repels certain creatures.
\item[\linkspell{Cure Critical Wounds, Mass}:] Cures 4d8 damage +1/level for many creatures.
\item[\linkspell{Elemental Swarm}:] Summons multiple elementals.
\item[\linkspell{Foresight}:] “Sixth sense” warns of impending danger.
\item[\linkspell{Regenerate}:] Subject’s severed limbs grow back, cures 4d8 damage +1/level (max +35).
\item[\linkspell{Shambler}:] Summons 1d4+2 shambling mounds to fight for you.
\item[\linkspell{Shapechange}:] Transforms you into any creature, and change forms once per round.
\item[\linkspell{Storm of Vengeance}:] Storm rains acid, lightning, and hail.
\item[\linkspell{Summon Nature’s Ally IX}:] Calls creature to fight.
\item[\linkspell{Sympathy}:] Object or location attracts certain creatures.
\end{description*}

\end{multicols}