%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Jester Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}

\subsection{0-Level Jester Spells (Cantrips)}
\begin{description*}
\item[\linkspell{Alarm}:] Wards an area for 2 hours/level.
\item[\linkspell{Detect Magic}:] Detects spells and magic items within 60 ft.
\item[\linkspell{Detect Poison}:] Detects poison in one creature or small object.
\item[\linkspell{Grease}:] Makes 10-ft. square or one object slippery.
\item[\linkspell{Unseen Servant}:] Invisible force obeys your commands.
\item[\linkspell{Ventriloquism}:] Throws voice for 1 min./level.
\end{description*}

\subsection{1st-Level Jester Spells}
\begin{description*}
\item[\linkspell{Fire Trap}:] Opened object deals 1d4 damage +1/level.
\item[\linkspell{Glitterdust}:] Blinds creatures, outlines invisible creatures.
\item[\linkspell{Magic Mouth}:] Speaks once when triggered.
\item[\linkspell{Misdirection}:] Misleads divinations for one creature or object.
\item[\linkspell{Pyrotechnics}:] Turns fire into blinding light or choking smoke.
\item[\linkspell{Reduce Person}:] Humanoid creature halves in size.
\item[\linkspell{Scattering Trap}:] Imbue one 5-ft. square/2 levels with teleport trap.
\item[\linkspell{Sleet Storm}:] Hampers vision and movement.
\item[\linkspell{Hideous Laughter}:] Subject loses actions for 1 round/level.
\item[\linkspell{Touch of Idiocy}:] Subject takes 1d6 points of Int, Wis, and Cha damage.
\end{description*}

\subsection{2nd-Level Jester Spells}
\begin{description*}
\item[\linkspell{Baleful Transposition}:] Two subjects switch places.
\item[\linkspell{Explosive Runes}:] Deals 6d6 damage when read.
\item[\linkspell{Glyph of Warding}:] Inscription harms those who pass it.
\item[\linkspell{Rage}:] Subjects gains +2 to Str and Con, +1 on Will saves, –2 to AC.
\item[\linkspell{Rope Trick}:] As many as eight creatures hide in extradimensional space.
\item[\linkspell{Secret Page}:] Changes one page to hide its real content.
\item[\linkspell{Sepia Snake Sigil}:] Creates text symbol that immobilizes reader.
\end{description*}

\subsection{3rd-Level Jester Spells}
\begin{description*}
\item[\linkspell{Feeblemind}:] Subject’s Int and Cha drop to 1.
\item[\linkspell{Globe of Invulnerability, Lesser}:] Stops 1st- through 3rd-level spell effects.
\item[\linkspell{Modify Memory}:] Changes 5 minutes of subject’s memories.
\item[\linkspell{Mordenkainen’s Faithful Hound}:] Phantom dog can guard, attack.
\item[\linkspell{Nightmare}:] Sends vision dealing 1d10 damage, fatigue.
\item[\linkspell{Servant Horde}:] Create 2d6 \linkspell{Unseen Servant}s +1/level (max +15).
\item[\linkspell{Shrink Item}:] Object shrinks to one-sixteenth size.
\end{description*}

\subsection{4th-Level Jester Spells}
\begin{description*}
\item[\linkspell{Globe of Invulnerability}:] As \linkspell{Globe of Invulnerability, Lesser}, plus 4th-level spell effects.
\item[\linkspell{Glyph of Warding, Greater}:] As \linkspell{Glyph of Warding}, but up to 10d8 damage or 6th-level spell.
\item[\linkspell{Insect Plague}:] Locust swarms attack creatures.
\item[\linkspell{Persistent Image}:] As \linkspell{Major Image}, but no concentration required.
\item[\linkspell{Symbol of Weakness}:] Triggered rune weakens nearby creatures.
\item[\linkspell{Tree Shape}:] You look exactly like a tree for 1 hour/level.
\end{description*}

\subsection{5th-Level Jester Spells}
\begin{description*}
\item[\linkspell{Bigby’s Interposing Hand}:] Hand provides cover against one opponent.
\item[\linkspell{Energy Immunity}:] Subject has immunity to damage from one kind of energy.
\item[\linkspell{Eyebite}:] Target becomes panicked, sickened, and comatose.
\item[\linkspell{Repulsion}:] Creatures can’t approach you.
\item[\linkspell{Screen}:] Illusion hides area from vision, scrying.
\item[\linkspell{Symbol of Insanity}:] Triggered rune renders nearby creatures insane.
\item[\linkspell{Telekinesis}:] Moves object, attacks creature, or hurls object or creature.
\end{description*}

\subsection{6th-Level Jester Spells}
\begin{description*}
\item[\linkspell{Creeping Doom}:] Swarms of centipedes attack at your command.
\item[\linkspell{Insanity}:] Subject suffers continuous confusion.
\item[\linkspell{Refuge}:] Alters item to transport its possessor to you.
\item[\linkspell{Symbol of Sleep}:] Triggered rune puts nearby creatures into catatonic slumber.
\item[\linkspell{Symbol of Stunning}:] Triggered rune stuns nearby creatures.
\item[\linkspell{Temporal Stasis}:] Puts subject into suspended animation.
\end{description*}

\end{multicols}