%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spirit Shaman Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}

\subsection{0-Level Spirit Shaman Spells (Orisons)}
\begin{description*}
\item[\linkspell{Alarm}:] Wards an area for 2 hours/level.
\item[\linkspell{Cure Minor Wounds}:] Cures 1d8 damage +1/level (max +5).
\item[\linkspell{Detect Magic}:] Detects spells and magic items within 60 ft.
\item[\linkspell{Dancing Lights}:] Creates torches or other lights.
\item[\linkspell{Prestidigitation}:] Performs minor tricks.
\item[\linkspell{Light}:] Object shines like a torch.
\item[\linkspell{Darkness}:] 20-ft. radius of supernatural shadow.
\item[\linkspell{Detect Poison}:] Detects poison in one creature or object.
\end{description*}

\subsection{1st-Level Spirit Shaman Spells}
\begin{description*}
\item[\linkspell{Animate Fire}:] Turn a Small or smaller quantity of fire into an animated object.
\item[\linkspell{Charm Person}:] Makes one person your friend.
\item[\linkspell{Cure Light Wounds}:] Cures 1d8 damage +1/level (max +5).
\item[\linkspell{Disguise Self}:] Changes your appearance.
\item[\linkspell{Endue Elements}:] Exist comfortably in hot or cold environments. 
\item[\linkspell{Entangle}:] Plants entangle everyone in 40-ft.-radius circle.
\item[\linkspell{Pass Without Trace}:] One subject/level leaves no tracks.
\item[\linkspell{Protection from Chaos}:] +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item[\linkspell{Protection from Law}:] +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
\item[\linkspell{Sleep}:] Puts 4 HD of creatures into magical slumber. 
\end{description*}

\subsection{2nd-Level Spirit Shaman Spells}
\begin{description*}
\item[\linkspell{Blink}:] You randomly vanish and reappear for 1 round/level.
\item[\linkspell{Control Plants}:] Control actions of one or more plant creatures.
\item[\linkspell{Detect Thoughts}:] Allows “listening” to surface thoughts.
\item[\linkspell{Ethereal Jaunt}:] You become ethereal for 1 round/level.
\item[\linkspell{Glitterdust}:] Blinds creatures, outlines invisible creatures. 
\item[\linkspell{Hideous Laughter}:] Subject loses actions for 1 round/level.
\item[\linkspell{Invisibility}:] Subject is invisible for 1 min./level or until it attacks.
\item[\linkspell{See Invisibility}:] Reveals invisible creatures or objects.
\item[\linkspell{Stone Tell}:] Talk to natural or worked stone.
\item[\linkspell{Treestride}:] Step from one tree to another far away.
\item[\linkspell{Warp Wood}:] Bends wood (shaft, handle, door, plank).
\item[\linkspell{Wood Shape}:] Rearranges wooden objects to suit you. 
\end{description*}

\subsection{3rd-Level Spirit Shaman Spells}
\begin{description*}
\item[\linkspell{Animate Objects}:] Objects attack your foes.
\item[\linkspell{Animate Plants}:] One or more trees animate and fight for you.
\item[\linkspell{Clairvoyance}:] Hear or see at a distance for 1 min./level.
\item[\linkspell{Consecrate}:] Fills area with positive energy, making undead weaker.
\item[\linkspell{Deep Slumber}:] Puts 10 HD of creatures to sleep. 
\item[\linkspell{Desecrate}:] Fills area with negative energy, making undead stronger.
\item[\linkspell{Etherealness}:] Travel to Ethereal Plane with companions.
\item[\linkspell{Invisibility, Greater}:] As \linkspell{Invisibility}, but subject can attack and stay invisible.
\item[\linkspell{Magic Circle Against Chaos}:] As \linkspell{Protection} spells, but 10-ft. radius and 10 min./level.
\item[\linkspell{Magic Circle Against Law}:] As \linkspell{Protection} spells, but 10-ft. radius and 10 min./level. 
\item[\linkspell{Plant Growth}:] Grows vegetation, improves crops.
\item[\linkspell{Remove Disease}:] Cures all diseases affecting subject.
\item[\linkspell{Transport via Plants}:] Move instantly from one plant to another of the same kind. 
\end{description*}

\subsection{4th-Level Spirit Shaman Spells}
\begin{description*}
\item[\linkspell{Baleful Polymorph}:] Transforms subject into harmless animal.
\item[\linkspell{Charm Monster}:] Makes monster believe it is your ally.
\item[\linkspell{Command Plants}:] Sway the actions of one or more plant creatures.
\item[\linkspell{Dimension Door}:] Teleports you short distance.
\item[\linkspell{Dimensional Anchor}:] Bars extradimensional movement. 
\item[\linkspell{Feeblemind}:] Subject’s Int and Cha drop to 1.
\item[\linkspell{Neutralize Poison}:] Immunizes subject against poison, detoxifies venom in or on subject.
\item[\linkspell{Resurrection}:] Fully restore dead subject.
\item[\linkspell{Scrying}:] Spies on subject from a distance.
\item[\linkspell{Stone Shape}:] Sculpts stone into any shape. 
\item[\linkspell{True Seeing}:] Lets you see all things as they really are.
\end{description*}

\subsection{5th-Level Spirit Shaman Spells}
\begin{description*}
\item[\linkspell{Break Enchantment}:] Frees subjects from enchantments, alterations, curses, and petrification.
\item[\linkspell{Circle of Death}:] Kills 1d4/level HD of creatures.
\item[\linkspell{Find the Path}:] Shows most direct way to a location.
\item[\linkspell{Magic Jar}:] Enables possession of another creature.
\item[\linkspell{Move Earth}:] Digs trenches and build hills. 
\item[\linkspell{Plane Shift}:] As many as eight subjects travel to another plane.
\item[\linkspell{Regenerate}:] Subject’s severed limbs grow back, cures 4d8 damage +1/level (max +35).
\item[\linkspell{Repel Wood}:] Pushes away wooden objects.
\item[\linkspell{Wall of Thorns}:] Thorns damage anyone who tries to pass.
\end{description*}

\subsection{6th-Level Spirit Shaman Spells}
\begin{description*}
\item[\linkspell{Hallow}:] Designates location as holy.
\item[\linkspell{Heal}:] Cures 10 points/level of damage, all diseases and mental conditions.
\item[\linkspell{Insanity}:] Subject suffers continuous \linkspell{Confusion}.
\item[\linkspell{Otto’s Irresistible Dance}:] Forces subject to dance.
\item[\linkspell{Nightmare}:] Sends vision dealing 1d10 damage, fatigue. 
\item[\linkspell{Unhallow}:] Designates location as unholy.
\end{description*}

\subsection{7th-Level Spirit Shaman Spells}
\begin{description*}
\item[\linkspell{Dimensional Lock}:] Teleportation and interplanar travel blocked for one day/level.
\item[\linkspell{Finger of Death}:] Kills one subject.
\item[\linkspell{Foresight}:] “Sixth sense” warns of impending danger.
\end{description*}

\subsection{8th-Level Spirit Shaman Spells}
\begin{description*}
\item[\linkspell{Charm Monster, Mass}:] As \linkspell{Charm Monster}, but all within 30 ft.
\item[\linkspell{Maze}:] Traps subject in extradimensional maze.
\item[\linkspell{Mind Blank}:] Subject is immune to mental/emotional magic and scrying.
\end{description*}

\subsection{9th-Level Spirit Shaman Spells}
\begin{description*}
\item[\linkspell{Heal, Mass}:] As \linkspell{Heal}, but with several subjects.
\item[\linkspell{Soul Bind}:] Traps newly dead soul to prevent \linkspell{Resurrection}.
\item[\linkspell{Trap the Soul}:] Imprisons subject within gem.
\item[\linkspell{Weird}:] As \linkspell{Phantasmal Killer}, but affects all within 30 ft.
\end{description*}

\end{multicols}