%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Lightfoot Halfling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The folk of Faer没n are more familiar with the Lightfoot Halfling than with either of the other two subraces, primarily because the Lightfoots are the most numerous and widely traveled of all the Halflings. Nearly every human community of any size larger than a village has at least a few Halfling residents. When most Faer没nians think of Halflings, the Lightfoots are the people that most often leap to mind.

Most Lightfoot Halflings trace their family ancestry back to the days when a great tribe of their subrace populated the territory known today as Luiren. Following the events of the Hin Ghostwars, the majority of the Lightfoot Halflings departed their homeland and spread out across northern Faer没n in a great diaspora. Though some Lightfoot Halflings remained in Luiren, the subrace has become ubiquitous throughout the settled lands of Faer没n.

\begin{multicols}{2}

\begin{itemize*}
\item Small sized.
\item 20ft movement.
\item Humanoid Type (Halfling subtype)
\item +2 Dexterity, -2 Strength.
\item +2 racial bonus on \linkskill{Climb}, \linkskill{Jump}, and \linkskill{Move Silently} checks.
\item +1 racial bonus on all saving throws.
\item +2 morale bonus on saving throws against Fear
\item +1 racial bonus on attack rolls with thrown weapons and slings.
\item +2 racial bonus on \linkskill{Listen} checks.
\item Alignment: Usually neutral
\item Favored Classes: \linkclass{Rogue} and \linkclass{Bard}.
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
20 & +1d6 & +1d8 & +2d8\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
2'8'' & 2'6'' & \multicolumn{2}{c}{+2d8}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 30 lb. & \cellcolor{white} 25 lb. & \multicolumn{2}{c}{\cellcolor{white} X 1 lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Lightfoot Halfling Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Amn & Chondathan, Halfling & \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Draconic, Giant, Illuskan, Orc, Shaaran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Cosmopolitan}, \linkfeat{Mercantile Background}, \linkfeat{Silver Palm}}\\
Calimshan & Alzhedo, Halfling & \multicolumn{1}{p{5cm}}{\raggedright{}Auran, Chondathan, Draconic, Ignan, Shaaran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Mercantile Background}, \linkfeat{Nobody's Fool}, \linkfeat{Street Smart}}\\
Luiren & Halfling & \multicolumn{1}{p{5cm}}{\raggedright{}Dambrathan, Durpari, Dwarven, Elven, Gnoll, Halruaan, Shaaran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Nobody's Fool}, \linkfeat{Surefooted}, \linkfeat{Strong Soul}}\\
The North & Halfling, Illuskan & \multicolumn{1}{p{5cm}}{\raggedright{}Chondathan, Dwarven, Elven, Giant, Orc} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Foe Hunter} (Orc), \linkfeat{Nobody's Fool}, \linkfeat{Swift and Silent}}\\
The Western Heartlands & Chondathan, Halfling & \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Dwarven, Gnome, Goblin, Illuskan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fearless}, \linkfeat{Luck of Heroes}, \linkfeat{Nobody's Fool}}\\
\end{smallbasictable}

\pagebreak