%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Master Transmogrifist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Perhaps none of an arcane spellcaster’s mighty powers is so versatile, useful, or spectacular as the ability to change into something else entirely. The Master Transmogrifist is a sorcerer or wizard who has chosen to specialize in spells that change his form. The \linkspell{Polymorph} spell and other shapechanging transmutations offer the Master Transmogrifist the ability to become a fearsome juggernaut of physical battle, a swiftflying traveler, or the perfect spy.

\textbf{Prerequisites:} 
\begin{description*}
\item[\hspace*{1.5cm}Alignment:] Any nonlawful.
\item[\hspace*{1.5cm}Skills:] \linkskill{Bluff} 2 ranks, \linkskill{Disguise} 5 ranks.
\item[\hspace*{1.5cm}Feat:] \linkfeat{Eschew Materials}.
\item[\hspace*{1.5cm}Spells:] Able to cast \linkspell{Alter Self} and \linkspell{Polymorph}.
\end{description*}

\textbf{Alignment:} Any nonlawful.

\textbf{Hit Die:} d4

\textbf{Class Skills:} The \currentclassname{}'s class skills are \linkskill{Bluff} (Cha), \linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Disguise} (Cha), \linkskill{Knowledge} Arcana (Int), \linkskill{Profession} (Wis), \linkskill{Spellcraft} (Int)

\textbf{Skills/Level:} 2 + Intelligence Bonus

\poorbab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{extraclasstable}{\textbf{Spellcasting}}
\levelone{\multicolumn{1}{p{5cm}}{\raggedright{} Extended Change, Favored Shape} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\leveltwo{\multicolumn{1}{p{5cm}}{\raggedright{} Manifest Senses} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelthree{\multicolumn{1}{p{5cm}}{\raggedright{} Battle Mastery +2} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelfour{\multicolumn{1}{p{5cm}}{\raggedright{} Effortless Change} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelfive{\multicolumn{1}{p{5cm}}{\raggedright{} Shapechanger} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelsix{\multicolumn{1}{p{5cm}}{\raggedright{} Battle Mastery +4} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelseven{\multicolumn{1}{p{5cm}}{\raggedright{} Reflexive Change} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\leveleight{\multicolumn{1}{p{5cm}}{\raggedright{} Manifest Qualities} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelnine{\multicolumn{1}{p{5cm}}{\raggedright{} Battle Mastery +6} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelten{\multicolumn{1}{p{5cm}}{\raggedright{} Infinite Variety} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\end{extraclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} The Master Transmogrifist gains no Proficiency with any arms or armours.

\textbf{Spellcasting:} A Master Transmogrifist gains new spells per day (and spells known, if applicable) as if he had also gained a level in an arcane spellcasting class to which he belonged before adding the prestige class level. He does not, however, gain any other benefit a character of that class would have gained (improved chance of turning or destroying Undead, metamagic or item creation feats, and so on). If he had more than one arcane spellcasting class before becoming a Master Transmogrifist, he must decide to which class to add new spells to when entering Master Transmogrifist Class.


\textbf{Extended Change (Ex):} A Master Transmogrifist gains the benefit of the \linkfeat{Extend Spell} feat on any transmutation spell he casts to change into one of his favored shapes (see below). This benefit does not increase the spell’s level or casting time, or require any special preparation. Spells that can benefit from this ability include \linkspell{Alter Self}, \linkspell{Polymorph}, \linkspell{Polymorph Any Object}, and \linkspell{Shapechange}.

\textbf{Favored Shape (Su):} A Master Transmogrifist chooses three favored shapes at 1st level. A favored shape is a specific kind of creature whose form he can assume by means of the \linkspell{Polymorph} spell. He cannot choose a creature of his own type (humanoid, most likely) as a favored shape.

For example, an 8th-level human sorcerer/1st-level Master Transmogrifist might choose pegasus, umber hulk, and bronze dragon as his favored shapes, though because of the Hit Dice restriction, he could become only a very young bronze dragon.

A Master Transmogrifist gains a number of advantages with his favored shapes, as noted in the following class feature descriptions. At every odd-numbered level beyond 1st, a Master Transmogrifist gains one additional favored shape. Thus, he has four at 3rd level, five at 5th level, six at 7th level, and seven at 9th level. Furthermore, once per Master Transmogrifist level beyond 1st, a character can choose to lose a previously chosen favored shape and select a replacement.

\textbf{Manifest Senses (Su):} At 2nd level and higher, a Master Transmogrifist gains the senses of his favored shape when he assumes its form. Senses include extraordinary special qualities such as \linkability{Blindsense}, \linkability{Blindsight}, \linkability{Darkvision}, \linkability{Low-Light Vision}, \linkability{Scent}, and \linkability{Tremorsense}.

\textbf{Battle Mastery (Ex):} At 3rd level, a Master Transmogrifist gains a +2 competence bonus on all attack rolls he makes while in one of his favored shapes. This bonus increases to +4 at 6th level and to +6 at 9th level.

\textbf{Effortless Change (Ex):} At 4th level, a Master Transmogrifist learns how to change his form through a simple act of will. He can choose to apply the benefits of the \linkfeat{Still Spell} and \linkfeat{Silent Spell} feats (even if he doesn’t have the feats) to any transmutation spell he casts to change into one of his favored shapes. This benefi t does not increase the spell’s level or casting time, or require any special preparation. Spells that can benefi t from this ability include \linkspell{Alter Self}, \linkspell{Polymorph}, \linkspell{Polymorph Any Object}, and \linkspell{Shapechange}.

\textbf{Shapechanger (Ex):} A Master Transmogrifist acquires the shapechanger subtype at 5th level. He also gains the ability to remain in an assumed form indefinitely when he casts \linkspell{Alter Self}. This works exactly like the alter self spell except that the duration is permanent. In other words, a Master Transmogrifist can remain in the form he assumes as long as he wishes, until either he chooses to dismiss it or the alter self effect is dispelled.

\textbf{Reflexive Change (Ex):} At 7th level and higher, a Master Transmogrifist has the ability to change into a favored shape via a transmutation spell in response to an opponent’s action once per day. If he has an appropriate spell prepared and chooses to use this ability, he can change form as an immediate action (see page 86) in response to the action of another creature.

For example, a Master Transmogrifist might turn into a dragon turtle to gain a high Armor Class against an impending attack, or change into a red dragon to gain immunity to the fire damage of an enemy’s fire storm spell. The spell is expended as if the transmogrifi st had cast it normally, and he remains in his new form until either the spell’s duration expires or he dismisses it. A transmogrifist gives up his next action to make a refl exive change. If a Master Transmogrifist is currently under the effect of a shapechange spell he cast on himself, he can use his reflexive change ability as often as he likes (although never more than once per round). Each time he uses it, he loses his next action.

\textbf{Manifest Qualities (Ex):} At 8th level and higher, a Master Transmogrifist has all the extraordinary special qualities of any favored shape he assumes. For example, he could change into a troll to make use of the troll’s regeneration ability, or take the form of a green hag to gain spell resistance 18.

\textbf{Infinite Variety (Su):} At 10th level, a Master Transmogrifist gains the ability to create completely imaginary forms when he casts \linkspell{Polymorph}, \linkspell{Polymorph Any Object}, and \linkspell{Shapechange} on himself. To create an imaginary form, he chooses one of his favored shapes as a base form. He can then choose a single aspect of a second monster whose form he could assume using the spell he is casting and add it to the first creature  His available options include the following.

\begin{itemize*}
\item Replace the base form’s natural armor bonus with that of the second form.
\item Add the second form’s movement modes.
\item Add one of the second form’s natural attack types (with the appropriate reach), if the base form doesn’t have that attack type already.
\item Add an extraordinary special attack of the second form.
\item Add an extraordinary special quality of the second form.
\item Replace one of the base form’s physical ability scores, if both the base form and the second form are the same size category.
\end{itemize*}

For example, if a young red dragon is the base form and a giant octopus is the second, a Master Transmogrifist could add the octopus’s eight tentacle rakes (damage 1d4 + Str bonus) to the dragon’s available natural attacks.
