%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Pale Master}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Necromancy is usually a poor choice for arcane spellcasters—those who really want to master the deathless arts almost always pursue divine means. However, there is an alternative for those who desire power over the Undead but refuse to give up their arcane craft completely. Enter the Pale Master, who draws on a font of special lore that provides a macabre power all its own. 
 
Virtually all Pale Masters are former wizards or sorcerers, due to the arcane talents required for entry into the class. Some have also dabbled in divine magic, perhaps multiclassing as clerics, before following this path.

\textbf{Prerequisites:} 
\begin{description*}
\item[\hspace*{1.5cm}Alignment:] Any Non-Good.
\item[\hspace*{1.5cm}Skills:] \linkskill{Knowledge} (Undead) 8 ranks.
\item[\hspace*{1.5cm}Spells:] Able to cast \linkspell{Command Undead} and \linkspell{Vampiric Touch} as Arcane spells.
\item[\hspace*{1.5cm}Special:] The candidate must have spent three or more days locked in a tomb with animate Undead. This contact may be peaceful or violent. A character who is slain by the Undead and later raised still meets the requirement, although the resulting level loss may delay compliance with other prerequisites.
\end{description*}

\textbf{Alignment:} Usually Evil.

\textbf{Hit Die:} d4

\textbf{Class Skills:} The Pale Master's class skills are \linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Hide} (Dex), \linkskill{Knowledge} (Int), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Profession} (Wis), and \linkskill{Spellcraft} (Int)

\textbf{Skills/Level:} 2 + Intelligence Bonus

\poorbab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{extraclasstable}{\textbf{Spellcasting}}
\levelone{\multicolumn{1}{p{5cm}}{\raggedright{} Undead Minion} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\leveltwo{\multicolumn{1}{p{5cm}}{\raggedright{} Animate Dead} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelthree{\multicolumn{1}{p{5cm}}{\raggedright{} Darkvision} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelfour{\multicolumn{1}{p{5cm}}{\raggedright{} Undead Armor Affinity} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelfive{\multicolumn{1}{p{5cm}}{\raggedright{} Control Undead, Deathless Vigor} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelsix{\multicolumn{1}{p{5cm}}{\raggedright{} Undead Graft, Paralyzing Touch} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelseven{\multicolumn{1}{p{5cm}}{\raggedright{} Tough as Bone, Weakening Touch} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\leveleight{\multicolumn{1}{p{5cm}}{\raggedright{} Undead Armor Affinity, Degenerative Touch} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelnine{\multicolumn{1}{p{5cm}}{\raggedright{} Destructive Touch} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\levelten{\multicolumn{1}{p{5cm}}{\raggedright{} Deathless Mastery, Deathless Master’s Touch} & \multicolumn{1}{p{4.5cm}}{\raggedright{} +1 level of existing arcane spellcasting class}}
\end{extraclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} The Pale Master gains Proficiency with Light and Medium Armor. They gain no Proficiency with any Weapons or Shields.

\textbf{Spellcasting:} A Pale Master gains new spells per day (and spells known, if applicable) as if he had also gained a level in an arcane spellcasting class to which he belonged before adding the prestige class level. He does not, however, gain any other benefit a character of that class would have gained (improved chance of turning or destroying Undead, metamagic or item creation feats, and so on). If he had more than one arcane spellcasting class before becoming a Pale Master, he must decide to which class to add new spells to when entering Pale Master Class.

\textbf{Undead Minion:} The Pale Master gains the services of an Undead creature, typically a wolf skeleton or a zombie troglodyte. With your DM's permission you can gain the services of a different skeleton or zombie creature with a total, post-template CR of 1 or lower.

The Pale Master's minion gains new abilities as he gains levels. A minion's abilities depend on the Pale Master's total level in this class. It obeys his commands without fail, and even takes suicidal actions. If destroyed, a new minion appears 24 hours later. The Pale Master can also choose to dismiss his minion to gain a new one. In this case, the Pale Master must wait 24 hours for the new minion to appear.

A Pale Master can choose to gain the services of a more powerful undead servitor at higher levels. Subtract the level modifier listed for a minion from the Pale Master's level to determine the abilities and bonuses it gains.

Any ability that give him a Undead Minion stacks with this.

\textbf{Animate Dead (Sp):} Starting at 2nd level, a Pale Master begins to exercise control over the Undead. Once per day, he can use \linkspell{Animate Dead}, as the spell, without need of a material component. Use the Pale Master’s Arcane Caster level for this effect. All other level restrictions of \linkspell{Animate Dead} still apply.

\textbf{Darkvision (Ex):} At 3rd level, the Dark begins to lose its mysteries to a Pale Master, who gains Darkvision 60 feet. If he already has Darkvision 60ft or gets Darkvision 60ft from somewhere else, its effective distance increases by 60 feet.

\textbf{Undead Armor Affinity (Ex):} A Pale Master has an instinctive feel for Undead Armor. At 4th level and higher, he treats the Undead Armor as if its Arcane Spell Failure Chance were one armor type less (Light Armor becomes Not-Armor and Medium Armor become Light Armor for Arcane Spell Failure Chance). At 8th level, this reduction two type less (Medium Armor become Not-Armor and Heavy Armor becomes Light Armor for Arcane Spell Failure Chance).

\textbf{Control Undead (Sp):} Once per day, a Pale Master of 5th level or higher can gain control over an Undead creature (with Hit Dice equal to or less than his Pale Master Caster level) by
making a successfu melee touch attack against it. The Undead creature receives no saving throw to resist this effect. The control lasts for 1 round per Pale Master Caster level. When the duration expires, the Undead creature returns to its former allegiance, if any. The newly controlled Undead can still be turned or rebuked as normal. This effect is otherwise identical to the \linkspell{Control Undead} spell. This ability is in addition to the number of Undead a Pale Master can control using his animate dead ability.

\textbf{Deathless Vigor (Ex):} Beginning at 5th level, a Pale Master’s body becomes more akin to the undying flesh of his Undead associates. The Pale Master gains everything from the list below.
\begin{itemize*}
\item Immunity to poison, paralysis, and disease.
\item Immune to damage to he's physical ability scores (Strength, Dexterity, and Constitution).
\item Heals using Negative energy (such as an Inflict spell), but is harmed from Positive energy (such as an Cure spell) like undead.
\item Gains +5 Fortitude save (unless the effect also works on objects or is harmless).
\item Dark Minded (subtype)
\item Unliving (subtype)
\end{itemize*}

\textbf{Undead Graft (Su):} At 6th level, a Pale Master gives in to terrible necrophiliac urges. He cuts off his arm and replaces it with an Undead prosthetic, which may be skeletal in form or preserved flesh stitched in place like that of a flesh golem. Regardless of its composition, the graft grants a +4 inherent bonus to the character’s Strength score.

Additionally, the Undead graft allows him to deliver horrible melee touch attacks. A Pale Master can use this ability once per day at 6th level, twice per day at 8th level, and three times per day at 10th level. The character must declare that he is using this ability before making the attack roll; a failed attack roll still expends that use of the ability. Each time he makes a melee touch attack using this ability, the Pale Master can select from any of the effects described below for which he meets the prerequisite class level. The save DC for the Pale Master’s melee touch attacks is 10 + his Pale Master class level + his Cha modifier.

Paralyzing Touch: Any living foe except for an elf that is hit by a Pale Master’s melee touch attack must succeed on a Fortitude save or be paralyzed for 1d4+1 rounds. Prerequisite: Class level 6th.

Weakening Touch: A living foe hit by a Pale Master’s melee touch attack takes 1d6 points of Strength damage (no save). A creature reduced to Strength 0 dies. Prerequisite: Class level 7th.

Degenerative Touch: A living foe hit by a Pale Master’s melee touch attack receives one negative level (no save), and must make a Fortitude save 24 hours later to avoid losing the level permanently. Prerequisite: Class level 8th.

Destructive Touch: A living foe hit by a Pale Master’s melee touch attack must succeed on a Fortitude save or take 1d6 points of Constitution drain. Prerequisite: Class level 9th.

Deathless Master’s Touch: A living foe of up to one size category larger than a Pale Master hit by the Pale Master’s melee touch attack must succeed on a Fortitude save or die. A slain creature automatically animates 1 round later as a Zombie and is under the Pale Master’s control as if he had animated it. Undead created using this power do not count against a Pale Master’s HD total for controlling Undead. Prerequisite: Class level 10th.

\textbf{Tough as Bone (Ex):} On reaching 7th level, a Pale Master takes on even more of the qualities of an Undead creature. He becomes immune to disease, nonlethal damage, and stunning.

\textbf{Deathless Mastery (Ex):} On reaching 10th level, a Pale Master gains the virtues of his deathless arts. His body becomes partly mummified (though he is not truly Undead), and gains all the effects from the Undead type, but doesn't gain the Undead type and is still living person. This does give him Darkvison 60ft.

\pagebreak

\begin{smallbasictable}{Pale Master's Undead Minion}{l l l l}
\textbf{Pale Master's Level} & \textbf{Bonus HD} & \textbf{Str/Dex Bonus} & \textbf{Special}\\
1-4 & +0 & +0 & Turn resistance +4\\
5-8 & +2 & +2 & Unholy might\\
9-12 & +4 & +4 & Persistent corruption\\
13-16 & +6 & +6 & Link of the grave\\
17-20 & +8 & +8 & Relentless undead\\
\end{smallbasictable}

\textbf{Undead Minion Basics:} Use the base statistics for a creature of the minion's kind, as given in the Monster Manual, but make the following changes.

Bonus Hit Dice: The undead minion gains the listed bonus hit dice. Advance its saving throws, base attack bonus, and so forth as per the Monster Manual It does not increase in size due to these bonus HD.

Str/Dex Bonus: The minion gains the listed bonus to both its Strength and Dexterity scores.

\textbf{Special Abilities:} As the Death Master gains levels, his undead minion gains a number of special abilities.

Turn Resistance +4: The undead minion gains this turn resistance in addition to any turn resistance it normally gains.

Unholy Might: Once per day as a standard action, the Death Master can channel unholy energy into his minion to allow it to fight with increased vigor. The Death Master must touch the minion to imbue it with this power. The minion gains a +4 bonus to Strength and a +2 bonus on all saves for a number of rounds equal to 5 + the Death Masters Wisdom modifier. If the minion is a zombie, it loses the single actions only drawback for the duration of this ability.

Persistent Corruption: The Death Master of this level has his destroyed minion returned to him shortly after its destruction. The Death Master must only wait 1 hour for a replacement undead minion if his is destroyed. He must still wait 24 hours for a replacement undead minion if he releases his current one.

Link of the Grave: Once per day as a free action, the Death Master can cast a shield other spell that links him to his minion. This spell has one critical difference from its normal form. Treat the Death Master as the spell's target and the minion as the caster. Thus, if the Death Master suffers damage he shares the total with his minion, but not vice versa.

Relentless Undead: The Death Master's minion gains fast healing 3.

\vspace*{15pt}

\begin{smallbasictable}{Alternative Undead Minions}{l l l l}
\textbf{4th Level (Level -3)} & \textbf{7th Level (Level -6)} & \textbf{10th Level (Level -9)} & \textbf{16th Level (Level -15)}\\
Bugbear Zombie & Ogre Zombie & Gray Render zombie & Spectre\\
Ghoul & Wyvern Zombie & Wight &\cellcolor{white}\\
Owlbear Skeleton & \cellcolor{white} \textbf{10th Level (Level -9)} & \cellcolor{white} \textbf{13th Level (Level -12)} &\cellcolor{white}\\
\textbf{7th Level (Level -6)} & \cellcolor{offyellow} Allip & \cellcolor{offyellow} Cloud Giant Skeleton &\cellcolor{white}\\
Chimera Skeleton & \cellcolor{white} Ettin Skeleton & \cellcolor{white} Mummy &\cellcolor{white}\\
Minotaur Zombie & \cellcolor{offyellow} Ghast & \cellcolor{offyellow} Wraith &\cellcolor{white}\\
\end{smallbasictable}

\pagebreak