\section{Armor}

\subsection{Armor Qualities}
To wear heavier armor effectively, a character can select the Armor Proficiency feats, but most classes are automatically proficient with the armors that work best for them. Characters who are not proficient with an armor or shield incur additional penalties when wearing them. Armor and shields can take damage from some types of attacks. Here is the format for armor entries (given as column headings on the table below).

\subsection{Category}
Armors and shields come in different categories. Nonarmor, light armor, medium armor, and heavy armor for armors, and shields and great shields for shields. Characters who are wearing armor that they do not have the appropriate proficiency with take additional penalties for wearing them (see Armor Class Penalties below). All characters are proficient with nonarmors.

\subsection{Cost}
The cost of the armor for Small or Medium humanoid creatures. See Armor for Unusual Creatures, below, for armor prices for other creatures.

\subsection{Armor Class (AC) Bonus}
Each armor grants an armor bonus to AC, while shields grant a shield bonus to AC. The armor bonus from a suit of armor doesn't stack with other effects or items that grant an armor bonus. Similarly, the shield bonus from a shield doesn't stack with other effects that grant a shield bonus.

\subsection{Maximum Dex Bonus (Max Dex)}
This number is the maximum Dexterity bonus to AC that this type of armor allows. Heavier armors limit mobility, reducing the wearer's ability to dodge blows. This restriction doesn't affect any other Dexterity-related abilities.

Even if a character's Dexterity bonus to AC drops to 0 because of armor, this situation does not count as losing a Dexterity bonus to AC.

Your character's encumbrance (the amount of gear he or she carries) may also restrict the maximum Dexterity bonus that can be applied to his or her Armor Class.

Shields do not affect a character's maximum Dexterity bonus.

\subsection{Armor Check Penalty (ACP)}
Any armor heavier than leather hurts a character's ability to use some skills. An armor check penalty number is the penalty that applies to Balance, Climb, Escape Artist, Hide, Jump, Move Silently, Sleight of Hand, or Tumble checks by a character wearing a certain kind of armor. Double the normal armor check penalty is applied to Swim checks. If a character casts arcane spells in armor which has an Armor Check Penalty, their spells with somatic components have a 5\% chance of failing for every point of armor check penalty. A character's encumbrance (the amount of gear carried, including armor) may also apply an armor check penalty.

If a character is wearing armor and using a shield, both armor check penalties apply.

If a character has a current armor check penalty, from his armor and shield combined, that is greater than their Base Attack Bonus, they move at reduced speed (2/3~Speed). If the Armor Check Penalty is 4 points greater than their Base Attack Bonus, they cannot take the Run action. If the Armor Check Penalty is ten points greater than their Base Attack Bonus, they can only stagger around, and only gain a standard action each round instead of a full-round action.

\subsection{Nonproficient with Armor Worn}
A character who wears armor and/or uses a shield with which he or she is not proficient takes the armor’s (and/or shields’s) armor check penalty on attack rolls and on all Strength-based and Dexterity-based ability and skill checks. The penalty for nonproficiency with armor stacks with the penalty for nonprofiency with shields

\subsection{Sleeping in Armor}
A character who sleeps in medium or heavy armor is automatically fatigued the next day. He or she takes a -2 penalty on Strength and Dexterity and can't charge or run. Sleeping in light armor does not cause fatigue.

\subsection{Weight}
This column gives the weight of the armor sized for a Medium wearer. Armor fitted for Small characters weighs half as much, and armor for Large characters weighs twice as much.

\end{multicols}

\begin{smallbasictable}{Armors}{p{1.8cm} c c c c c | p{1.8cm} c c c c c}
\textbf{Non-Armor} & \textbf{AC} & \multicolumn{1}{p{.75cm}}{\raggedright{}\textbf{Max Dex}} & \textbf{ACP} & \textbf{Cost} & \textbf{Weight} & \textbf{Medium Armor} & \textbf{AC} & \multicolumn{1}{p{.75cm}}{\raggedright{}\textbf{Max Dex}} & \textbf{ACP} & \textbf{Cost} & \textbf{Weight}\\ 
Camou-flaged Clothes & 0 &  & 0 & 1gp & 5 lb & Hide & +3 & +4 & -4 & 15gp & 25 lb\\
Functional Clothes & 0 &  & 0 & 1gp & 5 lb & Scale Mail & +4 & +3 & -5 & 50gp & 35 lb\\
Travelers Clothes & 0 &  & 0 & 1gp & 5 lb & Ringmail & +4 & +6 & -2 & 75gp & 30 lb\\
Fancy Clothes & 0 & +6 & -1 & 30gp & 5 lb & Chainmail & +5 & +3 & -3 & 150gp & 40 lb\\
Magic Clothes & +2 & +9 & 0 & 8,000gp & 5 lb & Lamellar & +5 & +4 & -4 & 190gp & 40 lb\\
\multicolumn{1}{p{1.8cm}}{\raggedright{}\textbf{Light Armor}} & \textbf{AC} & \multicolumn{1}{p{.75cm}}{\raggedright{}\textbf{Max Dex}} & \textbf{ACP} & \textbf{Cost} & \textbf{Weight} & Elaborate Gown & +1 & +3 & -5 & 300gp & 15 lb\\
\multicolumn{1}{p{1.8cm}}{\raggedright{}Padded Armor} & +1 & +8 & 0 & 5gp &10 lb & Lobster Mail & +5 & +2 & -5 & 350gp & 15 lb\\
\multicolumn{1}{p{1.8cm}}{\raggedright{}Cord Armor} & +2 &  & 0 & 20gp & 10 lb & Breastplate & +6 & +2 & -4 & 450gp & 40 lb\\
Winter Clothes & +2 & +4 & -4 & 30gp & 25 lb & Chitin Carapace & +6 & +4 & -3 & 500gp & 30 lb\\
\multicolumn{1}{p{1.8cm}}{\raggedright{}Leather Armor} & +2 & +7 & 0 & 45gp & 10 lb & \multicolumn{1}{p{1.8cm}}{\raggedright{}Gith Armor} & +5 & +4 & -2 & 900gp & 25 lb\\
Still Suit & +2 & +5 & -3 & 50gp & 25 lb & \multicolumn{1}{p{1.8cm}}{\raggedright{}Animal Spirit Armor} & +4 & +3 & -3 & 1,000gp & 30 lb\\
\multicolumn{1}{p{1.8cm}}{\raggedright{}Wicker Armor} & +3 & +7 & -1 & 55gp & 10 lb & Dragon-scale Shirt\textsuperscript{1} & +7 & +5 & -4 & 3,400gp & 30 lb\\
Studded Leather & +3 & +6 & -1 & 65gp & 16 lb & Mithril Suit\textsuperscript{1} & +7 & +5 & -2 & 5,000gp & 25 lb\\
Chain Shirt & +4 & +5 & -2 & 100gp & 25 lb & Adaman-tine Breastplate\textsuperscript{1} & +8 & +3 & -6 & 5,000gp & 60 lb\\
Brigadine & +4 & +6 & -2 & 110gp & 25 lb & \multicolumn{1}{p{1.8cm}}{\raggedright{}\textbf{Heavy Armor}} & \textbf{AC} & \multicolumn{1}{p{.75cm}}{\raggedright{}\textbf{Max Dex}} & \textbf{ACP} & \textbf{Cost} & \textbf{Weight}\\
\multicolumn{1}{p{1.8cm}}{\raggedright{}Gray Armor} & +4 &  & 0 & 1,000gp & 15 lb & \multicolumn{1}{p{1.8cm}}{\raggedright{}Hoplite Armor} & +6 & +1 & -9 & 250gp & 60 lb\\
Mithril Shirt & +5 & +6 & -1 & 4,000gp & 15 lb & Half Plate & +7 & +2 & -5 & 800gp & 45 lb\\
\multicolumn{12}{l}{\textsuperscript{1} This armor is already masterwork.}\\
\end{smallbasictable}

\begin{smallbasictable}{Armors}{p{1.8cm} c c c c c | p{1.8cm} c c c c c}
\multicolumn{1}{p{1.8cm}}{\raggedright{}\textbf{Heavy Armor}} & \textbf{AC} & \multicolumn{1}{p{.75cm}}{\raggedright{}\textbf{Max Dex}} & \textbf{ACP} & \textbf{Cost} & \textbf{Weight} & \textbf{Shields} & \textbf{AC} & \multicolumn{1}{p{.75cm}}{\raggedright{}\textbf{Max Dex}} & \textbf{ACP} & \textbf{Cost} & \textbf{Weight}\\ 
\multicolumn{1}{p{1.8cm}}{\raggedright{}Coral Armor} & +6 & +2 & -3 & 850gp & 40 lb & Steel Shield & +2 &  & -1 & 50gp & 10 lb\\
\multicolumn{1}{p{1.8cm}}{\raggedright{}Great Armor} & +7 & +2 & -7 & 1,000gp & 50 lb & Dragon-scale Shield\textsuperscript{1} & +3 &  & -1 & 950gp & 15 lb\\
\multicolumn{1}{p{1.8cm}}{\raggedright{}Full Armor} & +8 & +1 & -6 & 1,100gp & 50 lb & Mithril Shield & +2 &  & 0 & 1,020gp & 5 lb\\
\multicolumn{1}{p{.75cm}}{\raggedright{}Silk Steel Armor\textsuperscript{1}} & +7 & +3 & -4 & 3,400gp & 50 lb & Adaman-tine Shield\textsuperscript{1} & +3 &  & -1 & 2,000gp & 25 lb\\
Dragon-scale Suit\textsuperscript{1} & +9 & +4 & -5 & 5,500gp & 40 lb & \textbf{Great Shields} & \textbf{AC} & \multicolumn{1}{p{.75cm}}{\raggedright{}\textbf{Max Dex}} & \textbf{ACP} & \textbf{Cost} & \textbf{Weight}\\
Adaman-tine Caraoace\textsuperscript{1} & +11 & +2 & -9 & 9,000gp & 75 lb & Tower Shield & +4 &  & -10 & 100gp & 45 lb\\
\textbf{Shields} & \textbf{AC} & \multicolumn{1}{p{.75cm}}{\raggedright{}\textbf{Max Dex}} & \textbf{ACP} & \textbf{Cost} & \textbf{Weight} & Kite Shield & +4 &  & -5 & 120gp & 35 lb\\
Buckler & +1 &  & -1 & 15gp & 5 lb & Bone Wall & +3 &  & -10 & 150gp & 30 lb\\
Wooden Shield & +1 &  & 0 & 15gp & 5 lb & Kappa Shell & +3 &  & -12 & 500gp & 30 lb\\
\multicolumn{12}{l}{\textsuperscript{1} This armor is already masterwork.}\\
\end{smallbasictable}

\subsection{Individual Armor Entries}
In addition to the qualities given on the table, every armor and shield provides a special benefit unique to it, given below.

\subsection{Not Armors}
Anything you wear is a form of armor, but anything sufficiently light as to not count even as Light Armor can be worn by characters who lack armor proficiency without suffering penalties.\\

\begin{multicols}{2}

\skillarmor{Camouflaged Clothing:}
{Clothes specifically made to blend into the surroundings, whether by making your outline blotchy and incomprehensible, or simply matching the drapes.}
{Hide Ranks Benefit:}
{Opponents do not get a +4 bonus for spotting you for knowing what to look for.}
{You may hide while being observed without taking a special action.}
{You gain a +2 circumstance bonus on Hide checks.}
{You gain concealment.}

\skillarmor{Fancy Clothing:}{It's expensive and it looks it.}
{Bluff Ranks Benefit:}
{You receive a +2 circumstance bonus to Diplomacy and Bluff in civilized settings.}
{You may make a Bluff check as a free action to convince a character that you belong wherever you happen to be.}
{You may demand shelter from peasants at any time. No Bluff check required.}
{Once per turn, you may Feint as a free action.}

\skillarmor{Functional Clothing:}{Your outfit is covered in pockets and has many supporting straps designed to distribute weight.}
{Sleight of Hand Ranks Benefit:}
{You receive a +2 circumstance bonus to Escape Artist and Sleight of Hand checks.}
{You may Force March for one day without being Fatigued.}
{You may retrieve stored items about your person as a free action.}
{You can carry 50\% more stuff relative to your strength.}

\skillarmor{Travelers Clothing:}{This set of clothes consists of boots, a wool skirt or breeches, a sturdy belt, a shirt (perhaps with a vest or jacket), and an ample cloak with a hood.}
{Survival Ranks Benefit:}
{You receive a +2 circumstance bonus to Survival and Knowledge (local) checks.}
{You only need half the amount of food and water.}
{Your Overland Movement is reduced by x3/4.}
{You have Energy Resistance 5.}

\skillarmor{Magic Clothing:}{Your pants, your shirt, and your socks exude magic. Truth be told, it's mostly your pants.}
{Diplomacy Ranks Benefit:}
{You gain a +1 bonus on all Charisma-related checks.}
{You gain a +2 Deflection bonus to AC.}
{You gain a +3 bonus on all Charisma-related checks.}
{You gain a +5 Deflection bonus to AC.}

\subsection{Light Armors}

\attackarmor{Brigandine:}{A chain shirt on top of which has been layered some studded leather. It's like having chocolate and strawberry at the same time.
}{BAB Benefit:
}{You are encased in leather and steel and negate the first 5 points of nonlethal damage inflicted on you by any source.
}{You gain DR 5/Piercing
}{You can effectively disguise your armor as functional clothing. You gain a +5 bonus to Disguise checks to conceal your armor.
}{Your Armor check Penalty is halved.
}

\attackarmor{Chain Shirt:}{Interwoven links of the finest steel cover your torso.
}{BAB Benefit:
}{You are encased in steel and negate the first 5 points of nonlethal damage inflicted on you by any source.
}{You gain DR 5/Piercing
}{You receive a +2 bonus on any checks to resist grapple maneuvers.
}{Slashing damage from any source is reduced by half.
}

\skillarmor{Cord Armor:}{A series of knots wrapped about your person protect you from incoming attacks.
}{Tumble Ranks Benefit:
}{You are encased in cords and negate the first 5 points of bludgeoning damage you take.
}{As an immediate action, you can replace the AC for one attack made against you with the result of a tumble check.  You may use this ability after an attack has hit you, but not before damage has been rolled.
}{You gain a swim speed equal to your base land speed.
}{You may move up to your move speed with a swift action.
}

\skillarmor{Darkleaf Armor:}{This armour, grown rather than made, consists of hundreds of leaves that are as hard as iron.
}{Knowledge (Nature) Ranks Benefit:
}{Your armour grows small roots into you, granting you fast healing 1. 
}{You gain DR 5/piercing.
}{You gain hide in plain sight, but only in natural surroundings. 
}{You and your armor are one with nature, letting you move through any natural vegetation (such as a tree trunk
or brambles) as if they were level ground, as long as you end your turn in an unoccupied square. If you end your
turn inside a plant, you are ejected from the nearest open space.
}

\attackarmor{Gray Armor:}{Made from slaadskin, grey armour shifts to anticipate attacks with the power of Limbo.
}{BAB Benefit:
}{You are encased in shifting skin and negate the first 5 points of damage from any critical hit or sneak attack.
}{You gain DR 5/lawful.
}{Your armour is so shifty that you negate an amount of damage from any critical hit or sneak attack equal to
your BAB.
}{You are surrounded by a 10ft radius area of Raw Limbo. You automatically succeed on unopposed control checks
over this area, and gain a +4 bonus to opposed control checks. The controlled area reverts to normal once it
leaves the affected radius.
}

\skillarmor{Leather Armor:}{Made from cured cowhide, it's cheap, but does its job.
}{Tumble Ranks Benefit:
}{You are encased in leather and negate the first 2 points of bludgeoning damage you take. 
}{You gain fire resistance 5. 
}{As an immediate action, you can replace your AC for one attack with the result of a Tumble check.You may use
this ability after an attack has hit you, but before damage has been determined. 
}{You may move up to your speed as a swift action.
}

\attackarmor{Mithril Shirt:}{The links that make up this chain shirt are woven much tighter and made of mithril.
}{BAB Benefit:
}{You are encased in Mithril and negate the first 5 points of extra damage inflicted on you by a critical hit or sneak attack.
}{Your armor moves so easily that you can use the Tumble skill during a charge. 
}{You gain DR 5/bludgeoning and piercing. 
}{You convert an amount of lethal physical damage that you take equal to your BAB into nonlethal damage.
}

\skillarmor{Padded Armor:}{You wear thick cloth padding as protection.
}{Tumble Ranks Benefit:
}{You may reroll a failed tumble check when you attempt to move your full speed or through an occupied space.
}{You can gain the benefits of 8 hours of sleep with 7 hours of sleep.
}{As an immediate action, you can replace your AC for one attack with the result of a Tumble check.
}{You may move up to your speed as a swift action. 
}

\skillarmor{Still Suit:}{A watertight suit envelops your whole body, recycling all of your excretions and protecting you from the heat.
}{Survival Ranks Benefit:
}{You do not have to make checks to avoid Heat Exhaustion and Heat Stroke.
}{You have Fire Resistance 5.
}{You do not have to drink.
}{You are immune to Fire.
}

\skillarmor{Studded Leather Armor:}{Leather armor that has been adorned with metal studs to help protect your vitals.
}{Tumble Ranks Benefit:
}{Your important bits are protected by metal chunks, allowing you to negate the first 3 points of extra damage inflicted on you by a critical hit or sneak attack.
}{You gain DR 5/piercing.
}{When you deal damage in a grapple, you deal additional damage equal to this armour's AC bonus.
}{You may move up to your speed as a swift action. 
}

\skillarmor{Wicker Armor:}{This armor is made of woven willow branches, and makes you look a bit like furniture with wings.
}{Jump Ranks Benefit:
}{You are encased in wood, and gain DR 2/-. 
}{All your jumps are considered to have a running start. 
}{You no longer take falling damage. 
}{Your wooden wings give you a fly speed equal to your base land speed, at perfect manoeuvreability.
}

\skillarmor{Winter Clothing:}{Thick clothing that keeps you warm.
}{Survival Ranks Benefit:
}{You do not have to make checks to avoid hypothermia or frostbite while in cold areas.
}{You have Cold Resistance 5.
}{You have Cold Resistance 10.
}{You are immune to Cold.
}

\subsection{Medium Armors}

\attackarmor{Adamantine Breastplate:}{
}{BAB Benefit:
}{You gain Damage Reduction equal to your Base Attack Bonus, which is negated by Adamantine Weapons.
}{You gain a +2 bonus on Bullrush checks.
}{You do not provoke attacks of opportunity when charging.
}{You gain 5 points of Energy Resistance to Electricity, Acid, and Sonic.
}

\skillarmor{Animal Spirit Armor:}{Fashioned of the skin of an angry beast, this armor still carries its spirit and will lend you its strength.
}{Survival Ranks Benefit:
}{You inflict +2d6 damage while charging.
}{You gain scent.
}{You gain a natural weapon. This is used as a secondary natural weapon, even if you are otherwise unarmed.
}{You may Wildshape into an appropriate mighty beast.
}

\attackarmor{Breastplate:}{A solid steel armor underlayed with chainmail, it protects all of your vital bits.
}{BAB Benefit:
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/critical hits. 
}{You reduce the critical multiplier of any weapons used against you by 1 point, and reduce the bonus damage
dice from sneak attacks and death attacks against you by 2 dice. 
}{You gain DR 10/critical hits. 
}

\attackarmor{Chainmail:}{This armor is made of interlocking metal rings. It includes a layer of quilted fabric worn underneath to prevent chafing and to cushion the impact of blows. Several layers of mail are hung over vital areas.}
{BAB Benefit:}
{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.}
{Your armor moves so easily that you can use the Tumble skill during a charge.}
{You gain DR 5/Bludgeoning and Piercing.}
{You convert an amount of lethal physical damage that you take equal to your BAB into nonlethal damage.}

\skillarmor{Chitin Carapace:}{Made out an Ankheg or something, it's amazingly light and makes you look like a crazy mantis man when you wear it.
}{Climb Ranks Benefit:
}{You are ignored by Vermin until you attack them and you cannot be detected by the scent ability of creatures with the [Bug] subtype.
}{You gain a Climb Speed equal to your land speed.
}{You are immune to non-magical poison.
}{You gain a Flight Speed equal to your land speed (perfect).
}

\attackarmor{Dragonscale shirt:}{
}{BAB Benefit:
}{Each shirt provides Energy Resistance to a specific Energy type as appropriate to the dragon whose scales formed the shirt. The ER is equal to the Armor Bonus the shirt provides.
}{The Armor Check Penalty of this armor does not apply to Jump checks.
}{You gain a +4 intimidate bonus against Dragons. And a similar bonus to your saving throws against Fear from Dragons.
}{You gain Immunity to the appropriate energy type.
}

\skillarmor{Elaborate Gowns:}{It's a big frilly dress, or a bulky robe, or something else that's expensive and hard to move in.
}{Diplomacy Ranks Benefit:
}{You gain a +2 bonus to Intimidate and Perform checks.
}{You can hide weapons of a size up to your own inside your outfit with a normal Sleight of hand check.
}{You gain a +2 bonus to Escape Artist and Sleight of Hand checks.
}{You can cast \linkspell{sanctuary}, at will, as a sorcerer of your level.
}

\skillarmor{Gith Armor:}{The Gith have mastered the techniques of manipulating Astral Driftmetal and the chaotic stuff of Limbo to make a reasonably lightweight, yet oddly protective garment.
}{Concentration Ranks Benefit:
}{You gain a +2 bonus on Concentration checks.
}{You do not suffer any Arcane Spell Failure in this armor if you are proficient with it.
}{You are protected from the harmful effects of Limbo and the Astral Plane.
}{You may \linkspell{planeshift} to the Astral Plane or Limbo as a standard action.
}

\skillarmor{Hide Armor:}{You wear some other creature as a hat.
}{Survival Ranks Benefit:
}{You reek in those animal pants. But you reek like another creature, making you unlocatable by Scent.
}{The DC to Track you is increased by 4.
}{You gain DR 5/Piercing
}{You do not suffer a penalty to your Disguise to emulate other creatures.
}

\attackarmor{Lamellar Armor:}{Small metal or leather plates that are linked together to protect you.
}{BAB Benefit:
}{You are encased in laquered wood and steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Slashing
}{You do not take falling damage.
}{Once per round, you can convert an amount of lethal physical damage that you take equal to your BAB into nonlethal damage.
}

\skillarmor{Lobster Mail:}{A living carapace of a deep aquatic design. The engineering style is reminiscent of that of Kwalish, but much sleeker and individualized.
}{Swim Ranks Benefit:
}{You can breathe under water.
}{The Armor Check Penalty of this Armor is reduced to zero under water.
}{Each empty hand may be used as a Natural Weapon (Pincher). At Medium size, it does 1d6 damage.
}{You may walk on water, beginning or ending the effect as a free action (or immediate action). You can also \linkspell{control water} as a standard action. Your ability to use \linkspell{control water} refreshes when the last \linkspell{control water} effect ends for whatever reason.
}

\skillarmor{Mithril Suit:}{A full body covering of light metal. Very shiny, and nearly skin tight, the mithril suit is surprisingly protective.
}{Tumble Ranks Benefit:
}{Mithril is very light, and its Armor Check Penalty is not applied against your skill checks.
}{You allow no miss chance when averting your eyes from an opponent.
}{Your Commander Rating is increases by 1.
}{When you have concealment, you have total concealment instead.
}

\attackarmor{Ringmail:}{Steel rings are woven flat onto a leather armor backing.
}{BAB Benefit:
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Piercing
}{You gain a +2 bonus on Disarm checks.
}{You gain a +4 AC bonus against bludgeoning ranged weapons.
}

\skillarmor{Scale Mail:}{
}{Intimidate Ranks Benefit:
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Piercing
}{You reduce the damage from Falling and Constriction damage by 10 points.
}{You can make an Intimidate check as a Swift action.
}

\subsection{Heavy Armors}

\attackarmor{Adamantine Carapace:}{Made of one of the hardest and most durable known metals, this armor completely encases you.
}{BAB Benefit:
}{You gain Damage Reduction equal to your Base Attack Bonus, which is negated by Adamantine Weapons.
}{You gain a +2 bonus on Bullrush checks.
}{You do not provoke attacks of opportunity when charging.
}{You gain 5 points of Energy Resistance to Electricity, Acid, and Sonic.
}

\attackarmor{Coral Armor:}{Made of living Coral, this armor is as dangerous to your opponents as it is protective. All Coral Armor counts as having been made with Armor Spikes (a weapon three sizes smaller than the Armor).
}{BAB Benefit:
}{The Armor Check Penalty of Coral Armor does not get applied against your Swimming checks. You gain a Swim Speed equal to your land speed.
}{Enemies you damage with the Coral spikes are poisoned (DC 10 + half your Level + Con Bonus), initial and secondary damage of 1d3 Dex.
}{You gain a +5 bonus to Hide checks under water.
}{You gain DR 5/Bludgeoning
}

\attackarmor{Full Plate:}{Plates of steel, flexible chain armor, and leather straps encase your entire body.
}{BAB Benefit:
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Critical Hits
}{You negate the first three points of energy damage from any source.
}{Your DR improves to DR 10/Critical Hits
}

\attackarmor{Great Armor:}{
}{BAB Benefit:
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Slashing
}{You gain a +3 bonus on Intimidate checks.
}{You are immune to fear.
}

\attackarmor{Half Plate:}{A mixture of rigid plates and flexible chain, Half Plate combines protection with flexibility. It is very noisy, however.
}{BAB Benefit:
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Critical Hits
}{You gain a +2 bonus on Grapple checks.
}{You may make an Escape Artist check as a Swift Action.
}

\attackarmor{Hoplite Armor:}{Oldschool armor made of bronze and layered on in thick sheets all over the vitals.
}{BAB Benefit:
}{You are encased in bronze and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/critical hits. 
}{Your armour check penalty is halved. 
}{You gain DR 10/critical hits. 
}

\skillarmor{Silk Steel Armor:}{Made of an ancient bugbear technique, overlapping plates of steel are held apart by layers of silk and the entire carapace slides virtually without sound. While bulky, this black armor is remarkably stealthy.
}{Move Silently Ranks Benefit:
}{You gain a +2 Synergy bonus to Hide checks.
}{You negate 10 points of penalty to Move Silently for moving quickly (so running or fighting suffers only a -10 penalty, moving at normal speed is at no penalty).
}{You negate the first 10 points of Falling damage any time you fall (this does not negate damage caused by something you fall on, such as poison spikes or lava).
}{Once per round, you may attempt to hide while being observed.
}

\subsection{Shields}

\attackarmor{Adamantine Shield:}{A target shield constructed of pure Adamantine, it is nearly indestructible and can be placed between your important bits and deadly weapons.
}{BAB Benefit:
}{You can use your shield as a point of leverage, gaining a +2 bonus on Bullrush attempts.
}{Your shield may act as a wedge, providing a +2 bonus on Disarm attempts.
}{You can add your Shield bonus to the DC to grapple you.
}{You can throw your shield, performing any special combat maneuver with a range increment twice your natural reach.
}

\skillarmor{Buckler:}{A small shield strapped to the wrist or forearm used for parrying. It provides no bonuses while you are denied your Dexterity bonus to AC.
}{Balance Ranks Benefit:
}{You may use a weapon with the hand using the Buckler, but doing so causes you to suffer a -1 penalty to attack rolls using this hand (including two handed weapons).
}{You gain a +2 bonus to Sleight of Hand or Bluff checks to draw a weapon or feint in combat.
}{You no longer suffer a penalty to attack rolls when using a weapon in your buckler hand.
}{Your shield bonus works against touch attacks.
}

\attackarmor{Dragonscale Shield:}{
}{BAB Benefit:
}{Each shield provides Energy Resistance to a specific Energy type as appropriate to the dragon whose scales formed the shield. The ER is equal to the Shield Bonus the shield provides.
}{The Shield bonus of the shield adds to your Reflex saves against Supernatural Abilities.
}{You gain a +4 intimidate bonus against Dragons. And a similar bonus to your saving throws against Fear from Dragons.
}{You gain Evasion.
}

\attackarmor{Mithril Shield:}{It's as strong as titanium and as light as titanium. Who are we fooling? This is a great shield.
}{Sleight of Hand Ranks Benefit:
}{You can use your shield as a point of leverage, gaining a +2 bonus on Bullrush attempts.
}{Your shield may act as a wedge, providing a +2 bonus on Disarm attempts.
}{You can add your Shield bonus to the DC to grapple you.
}{You can throw your shield, performing any special combat maneuver with a range increment twice your natural reach.
}

\attackarmor{Steel Shield:}{It can be round or square or shaped like something in particular. It's not important, the key is that it's between you and sharp objects and it's made out of steel.
}{BAB Benefit:
}{You can use your shield as a point of leverage, gaining a +2 bonus on Bullrush attempts.
}{Your shield may act as a wedge, providing a +2 bonus on Disarm attempts.
}{You can add your Shield bonus to the DC to grapple you.
}{You can throw your shield, performing any special combat maneuver with a range increment twice your natural reach.
}

\attackarmor{Wooden Shield:}{Made of wood and held together with bands of steel or strips of leather, a wooden shield makes up in shock absorbance what it loses in resilience.
}{BAB Benefit:
}{You can use your shield as a point of leverage, gaining a +2 bonus on Bullrush attempts.
}{Your shield may act as a wedge, providing a +2 bonus on Disarm attempts.
}{You can add your Shield bonus to the DC to grapple you.
}{You can throw your shield, performing any special combat maneuver with a range increment twice your natural reach.
}

\subsection{Great Shields}

\skillarmor{Bone Wall:}{A seemingly random assortment of bones collected into a large shield.
}{Knowledge (Religion) Ranks Benefit:
}{You gain a bonus to your Saving throws against death effects equal to the Shield Bonus of this shield.
}{You may cast Necromancy spells without somatic components.
}{You gain Positive Energy Resistance equal to the shield bonus of this shield.
}{This shield provides bonuses to your AC against Incorporeal Touch Attacks.
}

\attackarmor{Kappa Shell:}{Fitting on the back of a character like the Kappa's Shell it is named after, the Kappa Shell provides decent protection for units moving across a dangerous battlefield.
}{BAB Benefit:
}{You may use both your hands while using this shield, but your attacks suffer a -2 penalty.
}{You may catch one ranged attack per turn on your shield automatically (the attack misses, whether it was an arrow or a magical ray).
}{You cannot be Flanked, except by a Rogue with 4 more levels than you have BAB.
}{You do not suffer a penalty to attack rolls when using both hands.
}

\skillarmor{Kite Shield:}{Shaped metal shields fit easily over a rider and his steed, allowing good protection for mounted troops.
}{Ride Ranks Benefit:
}{Your Mount gains the same shield bonus to AC that you gain from this shield.
}{Your Mount gains Evasion.
}{You may catch one ranged attack per turn on your shield automatically (the attack misses, whether it was an arrow or a magical ray).
}{Your Mount gains Improved Evasion.
}

\attackarmor{Tower Shield:}{Giant pieces of wood or metal, tower shields offer tremendous protection, but cannot be effectively used while mounted.
}{BAB Benefit:
}{You may claim half Cover at any time, but your own attacks suffer a -2 penalty.
}{You may catch one ranged attack per turn on your shield automatically (the attack misses, whether it was an arrow or a magical ray).
}{You may negate one bite attack per turn from a creature that is at least 2 sizes larger than yourself.
}{If you claim cover from your shield, you suffer no penalties to your attack rolls. So you're pretty much going to have cover all the time.
}

\subsection{Necromantic Armors}
\textbf{Blood steel}
Blood steel is steel that has been mixed with the blood of certain powerful creatures, making it redder than normal steel and with unusual properties.

Any armor made of blood steel has an armor bonus two higher. These effects only manifest if the blood steel is allowed to hungrily latch onto its user's flesh, at which point it reduces the bearer's Constitution by two points. Treat blood steel as normal steel for creatures with no Constitution or creatures protected from this effect.

Cost: 1,000 gp for armor or shield.

\subsection{Masterwork Armor}

You can purchase or craft masterwork versions of armor or 
shields. Such a well-made item functions like the normal version, except that its 
armor check penalty is lessened by 1. 

A masterwork suit of armor or shield costs an extra 150 gp over and above the normal 
cost for that type of armor or shield.

The masterwork quality of a suit of armor or shield never provides a bonus on attack 
or damage rolls, even if the armor or shield is used as a weapon.

All magic armors and shields are automatically considered to be of masterwork quality.

You can't add the masterwork quality to armor or a shield after it is created; 
it must be crafted as a masterwork item.

\subsection{Armor For Unusual Creatures}
\begin{multicolsbasictable}{l c c c c}

\textbf{Size} & \multicolumn{2}{c}{\textbf{Humanoid}} & \multicolumn{2}{c}{\textbf{Non-Humanoid}}\\ 
 & \textbf{Cost} & \textbf{Weight} & \textbf{Cost} & \textbf{Weight} \\
\multicolumn{1}{p{2cm}}{\raggedright{}Tiny or smaller\textsuperscript{1}} & x1/2 & x1/10 & x1  & x1/10\\
Small & x1 & x1/2 & x1 & x1/2\\
Medium & x1 & x1 & x2 & x1\\
Large & x2 & x2 & x4 & x2\\
Huge & x4 & x5 & x8 & x5\\
Gargantuan& x8 & x8 & x16 & x8\\
Colossal & x16 & x12 & x32 & x12\\
\multicolumn{5}{l}{\cellcolor{white}\textsuperscript{1}Divide armor bonus by 2.}\\
\end{multicolsbasictable}

Armor and shields for unusually big creatures, unusually little creatures, and nonhumanoid creatures have different costs and weights from those given on the armors table. Refer to the appropriate line on Table: Nonstandard Armors and apply the multipliers to cost and weight for the armor type in question.

\subsection{Getting Into And Out Of Armor}

The time required to don armor depends on its type, see the Table: Donning and Removing Armor.

\textbf{Don:} This column tells how long it takes a character to put the armor 
on. (One minute is 10 rounds.) Readying (strapping on) a shield is only a move 
action.

\textbf{Don Hastily:} This column tells how long it takes to put the armor on in 
a hurry. The armor check penalty and armor bonus for hastily donned armor are each 
1 point worse than normal. 

\textbf{Remove:} This column tells how long it takes to get the armor off. Loosing 
a shield (removing it from the arm and dropping it) is only a move action.

\end{multicols}

\begin{smallbasictable}{Donning and Removing Armor}{l l l l}
\textbf{Armor Type} & \textbf{Don} & \textbf{Don Hastily} & \textbf{Remove}\\
Shield or Great Shield & 1 move action & n/a & 1 move action\\
Nonarmor & 5 rounds & 1 full-round action & 1 full-round action\\
Light Armor & 1 minute & 5 rounds & 1 minute\textsuperscript{1}\\
Medium Armor & 4 minutes\textsuperscript{1} & 1 minute & 1 minute\textsuperscript{1}\\
Heavy Armor & 4 minutes\textsuperscript{2} & 4 minutes\textsuperscript{1} & 1d4+1 minutes\textsuperscript{1}\\
\multicolumn{4}{p{\textwidth}}{\cellcolor{white}\textsuperscript{1} If the character has some help, cut this time in half. A single character doing nothing else can help one or two adjacent characters. Two characters can't help each other don armor at the same time.}\\
\multicolumn{4}{p{\textwidth}}{\cellcolor{white}\textsuperscript{2} The wearer must have help to don this armor. Without help, it can be donned only hastily.}\\
\end{smallbasictable}

\pagebreak

\begin{multicols}{2}


