%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Starting Gear}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

you can instead purchase weapons, armor, and miscellaneous equipment item by item. You begin with a random number of gold pieces that is determined by your character’s class, and you decide how to spend it.

Note that buying beginning equipment this way is an abstraction. Your character doesn’t walk into a store with handfuls of gold and buy every item one by one. Rather, these items may have come the character’s way as gifts from family, equipment from patrons, gear granted during military service, swag gained through duplicity, and so on.

Assume your character owns at least one outfit of normal clothes. Pick any one of the following clothing outfits for free: artisan’s outfit, entertainer’s outfit, explorer’s outfit, monk’s outfit, peasant’s outfit, scholar’s outfit, or traveler’s outfit.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Wealth and Money}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Coins}
%%%%%%%%%%%%%%%%%%%%%%%%%

The most common coin is the gold piece (gp\index{gp}). A gold piece is worth 10 silver pieces (sp\index{sp}). Each silver piece is worth 10 copper pieces (cp\index{cp}). In addition to copper, silver, and gold coins, there are also platinum pieces (pp\index{pp}), which are each worth 10 gp.

The standard coin weighs about a third of an ounce (fifty to the pound).

\begin{multicolsbasictable}{l c c c c}

\textbf{Type} & \textbf{CP} & \textbf{SP} & \textbf{GP} & \textbf{PP}\\
\multicolumn{1}{p{2cm}}{\raggedright{}Copper piece (cp)} & 1 & 1/10 & 1/100 & 1/1,000\\
\multicolumn{1}{p{2cm}}{\raggedright{}Silver piece (sp)} & 10 & 1 & 1/10 & 1/100\\
\multicolumn{1}{p{2cm}}{\raggedright{}Gold piece (gp)} & 100 & 10 & 1 & 1/10\\
\multicolumn{1}{p{2cm}}{\raggedright{}Platinum piece (pp)} & 1,000 & 100 & 10 & 1\\
\end{multicolsbasictable}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Wealth Other Than Coins}
%%%%%%%%%%%%%%%%%%%%%%%%%

Merchants commonly exchange trade goods without using currency. As a means of comparison, some trade goods are detailed below.

\begin{multicolsbasictable}{l l}

\textbf{Cost} & \textbf{Item} \\
1cp & One pound of wheat.\\
2cp & One pound of flour, or one chicken.\\
1sp & One ponund of iron.\\
5sp & One pound of tobacco or copper.\\
1gp & One pound of cinnamon, one goat.\\
2gp & One pound of ginger of pepper, or one sheep.\\
3gp & One pig.\\
4gp & One square yard of linen.\\
5gp & One pound of salt or silver.\\
10gp & One square yard of silk, or one cow.\\
15gp & One pound of saffron or cloves, or one ox.\\
50gp & One pound of gold.\\
500gp & One pound of platinum.\\
\end{multicolsbasictable}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Selling Loot}
%%%%%%%%%%%%%%%%%%%%%%%%%

In general, a character can sell something for half its listed price.

Trade goods are the exception to the half-price rule. A trade good, in this sense, is a valuable good that can be easily exchanged almost as if it were cash itself.