%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Duergar}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Grim and determined, the duergar (or gray dwarves) lead lives of neverending toil in the great foundry-cities they have built in the Underdark. The gray dwarves are nearly as widespread and numerous as the drow, and the typical duergar realm is every bit as strong, cruel, and wealthy as a great city of the dark elves. But while most drow cities exist to exalt the high nobility of the dark elves, duergar cities exist only for the manufacture of wealth through unending labor.

Duergar are sullen, insular, and industrious, but they tend to be better neighbors than drow and are less likely to raid surface lands or seek out victims to torment. They are the preeminent artisans and merchants of the Underdark, and duergar caravans cross every corner of Faerûn miles beneath the surface. The gray dwarves are all too willing to enslave any likely creatures that fall into their hands, but they don’t waste slaves in the sort of cruel spectacles that the drow enjoy. Instead, the duergar simply work their captives to death.

\begin{multicols}{2}

\begin{itemize*}
\item Medium size.
\item Dwarf base land speed is 20 feet. Gray dwarves can move at this speed even when wearing medium or heavy armor or when carrying a medium or heavy load.
\item Humanoid Type (Dwarf subtype)
\item \linkability{Darkvision} 120ft
\item +2 Constitution, –4 Charisma.
\item Immunities (Ex): Gray dwarves are immune to paralysis, phantasms, and poison.
\item  +2 racial bonus on saves against spells and spell-like abilities.
\item +4 racial bonus on Move Silently checks.
\item +1 racial bonus on Listen and Spot checks
\item +2 bonus on Appraise and Craft checks that are related to stone or metal.
\item +1 racial bonus on attack rolls against orcs (including half-orcs) and goblinoids.
\item Stability: A duergar gains a +4 bonus on ability checks made to resist being bull rushed or tripped when standing on the ground.
\item Stonecunning: This ability grants a duergar a +2 racial bonus on Search checks made to notice unusual stonework. A gray dwarf who merely comes within 10 feet of unusual stonework is entitled to a Search check as if she were actively searching, and she can use the Search skill to find stonework traps as a rogue can. A duergar can also intuit depth, sensing her approximate depth underground.
\item Spell-Like Abilities: 1/day— \linkspell{Enlarge Person}, \linkspell{Invisibility}. Caster level equals twice the duergar’s hit dices (minimum 3rd level). These abilities affect only the duergar and whatever she carries.
\item +4 dodge bonus to Armor Class against giants.
\item Light Sensitivity (Ex): Duergar are dazzled in bright light (such as sunlight or a daylight spell).
\item Alignment: Usually lawful evil
\item Favored Classes: \linkclass{Blackguard} and \linkclass{Fighter}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
40 & +3d6 & +5d6 & +7d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'2'' & 4'0'' & \multicolumn{2}{c}{+2d4}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 180 lb. & \cellcolor{white}150 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d8) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\pagebreak

\begin{smallbasictable}{Urdunnir Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
Underdark (Darklands) & Elven, Dwarven & \multicolumn{1}{p{5cm}}{\raggedright{}Aquan, Chondathan, Draconic, Giant, Goblin} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Iron Mind}, \linkfeat{Magic in the Blood}, \linkfeat{Mercantile Background}}\\
Underdark (Northdark) & Elven, Dwarven & \multicolumn{1}{p{5cm}}{\raggedright{}Draconic, Giant, Goblin, Orc, Terran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Bullheaded}, \linkfeat{Daylight Adaptation}, \linkfeat{Resist Poison}}\\
\end{smallbasictable}

\pagebreak