%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Shield Dwarf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Found largely in the northern reaches of western and central Faerûn, Shield Dwarves are the dominant northern branch of the Stout Folk. Renowned for their smithwork and craftsmanship, Shield Dwarves have endured a centuries-long decline in the face of never-ending wars with orcs, goblins, giants, and trolls. Shield dwarves are descended from the founders of Shanatar, a legendary dwarven empire that once ruled the caverns beneath modern-day Amn, Tethyr, and Calimshan. After Shanatar fell, the Shield Dwarves migrated north, founding kingdoms such as Ammarindar, Delzoun, Gharraghaur, Haunghdannar, Oghrann, and Sarbreen. Although those kingdoms have also largely fallen, the Stout Folk of the North endure. The Thunder Blessing has served as a welcome reprieve for the beleaguered Shield Dwarves, giving hope that the descendants of ancient Shanatar may one day reclaim the glory of their forebears. Taller by half a foot than their Gold Dwarf cousins, Shield dwarves average 4 1/2 feet tall and weigh as much as an adult human. The skin of a Shield Dwarf is fair or lightly tanned, and her eyes are usually green or silvered blue. Both genders wear their hair long, and males (and a very few females) have long, carefully groomed beards and mustaches. Hair color ranges from light brown to red, with all shades fading to silver or white as time progresses. Shield dwarves keep to their word, whatever the cost, and are incredibly stubborn, unwilling to concede an inch unless there is absolutely no alternative. Such intransigence has enabled dwindling Shield Dwarf populations to hold on to ancient strongholds with just a fraction of their original defenders. However, it has also led to clan feuds and long-standing misunderstandings with other races that have sapped the strength of the Stout Folk. Shield dwarves love worked beauty, seeing the world as raw material to be forged and shaped into something more than the original

\begin{multicols}{2}

\begin{itemize*}
\item Medium size.
\item Dwarf base land speed is 20 feet. However, Shield Dwarves doesn't have their movement speed reduced from armour.
\item Humanoid Type (Dwarf subtype)
\item \linkability{Darkvision} 60ft
\item +2 Constitution, -2 Charisma.
\item Stonecunning: This ability grants the dwarf a +2 racial bonus on \linkskill{Search} checks to notice unusual stonework, such as sliding walls, stonework traps, new construction (even when built to match the old), unsafe stone surfaces, shaky stone ceilings, and the like. Something that isn't stone but that is disguised as stone also counts as unusual stonework. A Shield Dwarf who merely comes within 10 feet of unusual stonework can make a \linkskill{Search} check as if he were actively searching, and can use the \linkskill{Search} skill to find stonework traps; they can also intuit depth, sensing his approximate depth underground as naturally as a human can sense which way is up.
\item Weapon Familiarity: Shield Dwarves may treat dwarven waraxes and dwarven urgroshes as martial weapons, rather than exotic weapons.
\item Stability: Shield Dwarf gains a +4 bonus on ability checks made to resist being bull rushed or tripped when standing on the ground (but not when climbing, flying, riding, or otherwise not standing firmly on the ground).
\item +2 racial bonus on saving throws against poison.
\item +2 racial bonus on saving throws against spells and spell-like effects.
\item +1 racial bonus on attack rolls against orcs and goblinoids.
\item +4 dodge bonus to Armor Class against monsters of the giant type.
\item +2 racial bonus on \linkskill{Appraise} checks that are related to stone or metal items.
\item +2 racial bonus on \linkskill{Craft} checks that are related to stone or metal.
\item Alignment: Often lawful good
\item Favored Classes: \linkclass{Barbarian} and \linkclass{Fighter}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
40 & +3d6 & +5d6 & +7d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'2'' & 4'0'' & \multicolumn{2}{c}{+2d4}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 145 lb. & \cellcolor{white}110 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d6) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\pagebreak

\begin{smallbasictable}{Shield Dwarf Regions}{l l p{4cm} p{3cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
 The Galena Mountains & Damaran, Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Chondathan, Giant, Goblin, Orc} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Dauntless}, \linkfeat{Foe Hunter} (Goblin), \linkfeat{Tireless}}\\
 The Great Glacier & Dwarven, Uluik & \multicolumn{1}{p{4cm}}{\raggedright{}Aquan, Auran, Damaran, Draconic, Giant} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Axethrower}, \linkfeat{Oral History}, \linkfeat{Survivor}}\\
 The Spine of the World & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Chondathan, Draconic, Giant, Goblin, Illuskan, Orc} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Bullheaded}, \linkfeat{Foe Hunter} (Orc), \linkfeat{Oral History}}\\
 The Sword Coast & Dwarven, Illuskan & \multicolumn{1}{p{4cm}}{\raggedright{}Chondathan, Elven, Giant, Gnome, Orc} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Forgeheart}, \linkfeat{Metallurgy}, \linkfeat{Tireless}}\\
 Turmish & Dwarven, Turmic & \multicolumn{1}{p{4cm}}{\raggedright{}Chondathan, Elven, Giant, Gnome, Halfling} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Dauntless}, \linkfeat{Silver Palm}, \linkfeat{Stoneshaper}}\\
 Underdark (Earthroot) & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Elven, Giant, Goblin, Orc, Terran} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Bullheaded}, \linkfeat{Dauntless}}\\
 Underdark (Old Shanatar) & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Aquan, Draconic, Elven, Gnome, Terran} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Azerblood}, \linkfeat{Batrider}, \linkfeat{Tireless}}\\
 Waterdeep & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Alzhedo, Chondathan, Elven, Halfling, Illuskan, Orc} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Cosmopolitan}, \linkfeat{Silver Palm}, \linkfeat{Thug}}\\
\end{smallbasictable}

\pagebreak