%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Urdunnir}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Urdunnirs, sometimes known as orecutter dwarves, are a longforgotten offshoot of shield dwarves who have become one with the earth and stone. Thanks to the blessings of Dumathoin, Urdunnirs can walk through earth and stone as if it were air and shape metal and stone with their hands. Many orecutter dwarves are clerics of Dumathoin, expert smiths, or expert gemcutters. The Children of Dumathoin, as they call themselves, believe that the Silent Keeper transformed their ancestors in order to create a race of dwarves who could appreciate the true beauty of the subterranean landscape without needing to destroy it in the process. They have dwelt ever since in splendid isolation in Oldonnar, the legendary Lost Kingdom of Shanatar, deep beneath the Alimir Mountains.

\begin{multicols}{2}

\begin{itemize*}
\item Medium size.
\item Dwarf base land speed is 20 feet. However, Urdunnirs doesn't have their movement speed reduced from armour.
\item Humanoid Type (Dwarf subtype)
\item \linkability{Darkvision} 60ft
\item +2 Constitution, -2 Charisma.
\item Stonecunning: This ability grants the dwarf a +2 racial bonus on \linkskill{Search} checks to notice unusual stonework, such as sliding walls, stonework traps, new construction (even when built to match the old), unsafe stone surfaces, shaky stone ceilings, and the like. Something that isn't stone but that is disguised as stone also counts as unusual stonework. A Urdunnir who merely comes within 10 feet of unusual stonework can make a \linkskill{Search} check as if he were actively searching, and can use the \linkskill{Search} skill to find stonework traps; they can also intuit depth, sensing his approximate depth underground as naturally as a human can sense which way is up.
\item Weapon Familiarity: Urdunnirs may treat dwarven waraxes and dwarven urgroshes as martial weapons, rather than exotic weapons.
\item Stability: Urdunnir gains a +4 bonus on ability checks made to resist being bull rushed or tripped when standing on the ground (but not when climbing, flying, riding, or otherwise not standing firmly on the ground).
\item +4 racial bonus on saving throws against poison.
\item +2 racial bonus on saving throws against spells and spell-like effects.
\item +1 racial bonus on attack rolls against orcs and goblinoids.
\item +4 dodge bonus to Armor Class against monsters of the giant type.
\item +2 racial bonus on \linkskill{Appraise} checks that are related to stone or metal items.
\item +2 racial bonus on \linkskill{Craft} checks that are related to stone or metal.
\item Light Blindness (Ex): Abrupt exposure to bright light (such as sunlight or a daylight spell) blinds aUrdunnir for 1 round. In addition, he takes a –1 circumstance penalty on all attack rolls, saves, and checks while operating in bright light.
\item Alignment: Usually Neutral
\item Favored Classes: \linkclass{Cleric} and \linkclass{Fighter}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
40 & +3d6 & +5d6 & +7d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'2'' & 4'0'' & \multicolumn{2}{c}{+2d4}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 180 lb. & \cellcolor{white}150 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d8) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\pagebreak
Urdunnir Dwarf
\begin{smallbasictable}{Urdunnir Regions}{l l p{4cm} p{3cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
The Galena Mountains & Damaran, Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Chondathan, Giant, Goblin, Orc} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Dauntless}, \linkfeat{Foe Hunter} (Goblin), \linkfeat{Tireless}}\\
The Great Glacier & Dwarven, Uluik & \multicolumn{1}{p{4cm}}{\raggedright{}Aquan, Auran, Damaran, Draconic, Giant} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Axethrower}, \linkfeat{Oral History}, \linkfeat{Survivor}}\\
The Spine of the World & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Chondathan, Draconic, Giant, Goblin, Illuskan, Orc} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Bullheaded}, \linkfeat{Foe Hunter} (Orc), \linkfeat{Oral History}}\\
The Sword Coast & Dwarven, Illuskan & \multicolumn{1}{p{4cm}}{\raggedright{}Chondathan, Elven, Giant, Gnome, Orc} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Forgeheart}, \linkfeat{Metallurgy}, \linkfeat{Tireless}}\\
Turmish & Dwarven, Turmic & \multicolumn{1}{p{4cm}}{\raggedright{}Chondathan, Elven, Giant, Gnome, Halfling} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Dauntless}, \linkfeat{Silver Palm}, \linkfeat{Stoneshaper}}\\
Underdark (Earthroot) & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Elven, Giant, Goblin, Orc, Terran} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Bullheaded}, \linkfeat{Dauntless}}\\
Underdark (Old Shanatar) & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Aquan, Draconic, Elven, Gnome, Terran} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Azerblood}, \linkfeat{Batrider}, \linkfeat{Tireless}}\\
Waterdeep & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Alzhedo, Chondathan, Elven, Halfling, Illuskan, Orc} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Cosmopolitan}, \linkfeat{Silver Palm}, \linkfeat{Thug}}\\
Oldonnar & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Draconic, Elven, Giant, Terran} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Magic in the Blood}, \linkfeat{Stoneshape}, \linkfeat{Strong Soul}}\\
Tethyr & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Alzhedo, Chondathan, Elven, Goblin, Orc} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Furious Charge}, \linkfeat{Luck of Heroes}}\\
The Lake of Steam & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Alzhedo, Chondathan, Goblin, Shaaran, Tashalan} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Knifefighter}, \linkfeat{Snake Blood}, \linkfeat{Stormheart}}\\
The North & Dwarven & \multicolumn{1}{p{4cm}}{\raggedright{}Chondathan, Elven, Giant, Goblin, Illuskan Orc,} & \multicolumn{1}{p{3cm}}{\raggedright{}\linkfeat{Axethrower}, \linkfeat{Foe Hunter} (Orc), \linkfeat{Jotunbrud}}\\
\end{smallbasictable}

\pagebreak