%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Aarakocra}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Aarakocras are a race of intelligent birdlike people who live in mountainous areas around Toril. Aarakocras love to soar high in the sky for hours on end, riding the thermal currents and updrafts with their wings spread wide. From a distance, it’s easy to mistake them for eagles or some other large bird of prey.

Aarakocras stand about 5 feet tall and have a wingspan of 20 feet. On average, they only weigh about 90 pounds. Midway along each wing they have a three-fingered hand, which is only useful when the wings are folded in. Their wing muscles attach to a bony chestplate, and their powerful legs end in sharp talons that can be drawn back, allowing aarakocras to use their feet as hands. Their heads combine the features of an eagle and a parrot. Their beaks are gray-black, and their eyes are black as well. The males are brightly colored, usually red, orange, or yellow, while the females are either brown or gray.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 20ft movement; 90ft fly speed (Average Maneuverability)
\item Monstrous Humanoid (Air)
\item -2 Strength, +4 Dexterity
\item +1 Natural Armor bonus.
\item Natural Attacks: A flying Aarakocra can attack with 2 talons, dealing 1d4 points of damage each, or he can use a weapon in his talons. An Aarakocra on the ground can wield weapons in their wing-claws at his base attack bonus and attack with his bite as a secondary attack (–5 penalty on the attack roll, and half Strength bonus on the damage roll), dealing 1d3 points of damage.
\item Proficient with javelin
\item +2 racial bonus on \linkskill{Craft} (any one), \linkskill{Knowledge} (nature), \linkskill{Listen}, and \linkskill{Spot} checks.
\item Alignment: Often neutral good
\item Favored Classes: \linkclass{Fighter}, and \linkclass{Ranger}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
15 & +1d4 & +1d6 & +2d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 120 lb. & \cellcolor{white} 85 lb. & \multicolumn{2}{c}{\cellcolor{white} X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Aarakocra Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
The Stormhorns & Auran & \multicolumn{1}{p{5cm}}{\raggedright{}Chondathan, Draconic, Elven, Orc, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fearless}, \linkfeat{Furious Charge}, \linkfeat{Hover}}\\
\end{smallbasictable}

\pagebreak