%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Extaminaar}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The extaminaars are the snake-blooded members of the human noble House Extaminos, which has ruled the city of Hlondeth for more than eight hundred years. During the last century, the extaminaars have gone beyond Hlondeth to set up operations in other cities across Faerûn. They operate from the sewers and the shadows, hatching schemes to increase the power of their house and finding victims on which to perform their vile grafting and breeding experiments.

Extaminaars make excellent rogues, because they are known for their guile and wicked ability to strike from the shadows. Others often try to enlist extaminaars into their organizations because of their skills as crime bosses, interrogators, and information brokers. Still, most extaminaars have proven exceedingly loyal to their noble house.

\begin{multicols}{2}

\begin{itemize*}
\item Medium size
\item 30ft movement.
\item Humanoid Type (Human and Yuan-ti subtype)
\item –2 Strength, +2 Dexterity: Extaminaar are agile but not as strong as other humanoids their size.
\item Low-Light Vision: An extaminaar can see twice as far as a human in starlight, moonlight, torchlight, and similar conditions of poor illumination. He retains the ability to distinguish color and detail under these conditions.
\item +2 racial bonus on Fortitude saves versus poison: Exterminaars do not easily succumb to venom of any kind.
\item +4 racial bonus on Swim checks: Extaminaars are comfortable in the water, and their light frames make it easier for them to stay afloat.
\item +2 racial bonus on Escape Artist checks: Extaminaars can wriggle their way out of sticky situations.
\item Spell-Like Abilities: At will—speak with animals (snakes only); 3/day—charm animal (snakes only). Extaminaar often fill their lairs with poisonous snakes to dissuade interlopers.
\item Alignment: Usually lawful evil
\item Favored Classes: \linkclass{Ranger} and \linkclass{Rogue}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
15 & +1d4 & +1d6 & +2d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
5'0'' & 4'7'' & \multicolumn{2}{c}{+2d4}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 120 lb. & \cellcolor{white} 85 lb. & \multicolumn{2}{c}{\cellcolor{white} X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Extaminaar Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Hlondeth & Chondathan, Yuan-ti & \multicolumn{1}{p{5cm}}{\raggedright{}Chessentan, Damaran, Draconic, Elven, Shaaran, Turmic} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Plague Resistant}, \linkfeat{Silver Palm}, \linkfeat{Thug}}\\
\end{smallbasictable}

\pagebreak