%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Kuo-Toa}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Kuo-toa (meaning "original masters" in their native tongue) were a debased, piscine race of warm-blooded and amphibious creatures that dwelt in the Underdark. Sinister secrets lurked below the surface of their alien minds, for the kuo-toa were fanatics plagued by mental instability that saw things others couldn't and worshiped gods that didn't exist — at least until they believed hard enough.

\begin{multicols}{2}

\begin{itemize*}
\item Medium size
\item 20ft land movement, 50ft swim movement.
\item Monstrous Humanoid (Aquatic subtype)
\item Darkvision 60 ft
\item Keen Sight 60ft (Ex):A kuo-toa has excellent vision, thanks to his two independently focusing eyes. His eyesight is so keen that he can spot a moving object or creature even if it is invisible or ethereal. Only by remaining perfectly still can such objects or creatures avoid a kuo-toa's notice.
\item +2 Wisdom, -2 Charisma.
\item +2 Natural Armor bonus.
\item Amphibious (Ex): Kuo-toas can breathe both air and water without difficulty and are capable of surviving indefinitely in either environment.
\item Adhesive (Ex):A kuo-toa uses his own body oil and other materials to give his shield a finish almost like flypaper, capable of holding fast any creatures or items that touch it. Any creature that makes an unsuccessful melee attack against a kuo-toa must succeed on a Reflex save (DC 11 + kuo-toa's Con modifier), or the weapon sticks to the shield and is yanked out of its wielder's grip. A creature using a natural weapon is automatically grappled if it gets stuck. A kuo-toa requires one hour and special materials costing 20 gp to coat a shield with adhesive, but the secretion remains sticky for up to three days, or until it actually catches something or someone, whichever comes first. Successfully trapping a creature or item uses up the adhesive, so the shield can trap no further creatures or items until its coating is replenished. Pulling a stuck weapon or limb from a shield requires a DC 20 Strength check.
\item Slippery (Ex): A kuo-toa secretes an oily film that makes him difficult to grapple or snare. Webs (magic or otherwise) don't affect kuo-toas, and they usually can wriggle free from most other forms of confinement.
\item Light Blindness (Ex): Abrupt exposure to bright light (such as sunlight or a daylight spell) blinds a Kuo-Toa for 1 round. In addition, he takes a –1 circumstance penalty on all attack rolls, saves, and checks while operating in bright light.
\item Alignment: Often Neutral Evil
\item Favored Classes: \linkclass{Cleric} and \linkclass{Monk}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
20 & +1d6 & +1d8 & +2d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'9'' & 4'11'' & \multicolumn{2}{c}{+2d4}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 85 lb. & \cellcolor{white} 90 lb. & \multicolumn{2}{c}{\cellcolor{white} X 1d4.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Kuo-Toa Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Underdark & Kuo-Toan & \multicolumn{1}{p{5cm}}{\raggedright{}Aquan, Draconic, Dwarven, Elven, Gnome, Serusann} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Discipline}, \linkfeat{Foe Hunter} (Human or Mindflayer), \linkfeat{Theocrat}}\\
\end{smallbasictable}
\pagebreak