%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Tibbit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Tibbits (also known as catweres) are small, humanoid creatures that have the ability to turn into a common house cat. They arose from felines kept as familiars in ages past. The powerful magic that allows a familiar to gain intelligence and magic abilities slowly filtered from one generation of cats to the next. Whether tibbits evolved from a natural process, divine intervention, or a sudden surge in the magic running through their ancestry, none can say. Tibbits have never existed in large numbers, and their tendency to spread across the world leaves them with a fractured, incomplete racial history.

Much like their feline ancestors tibbits exhibit independence, curiosity, and quickness of mind and body. They rarely form communities larger than two or three families, and even these small colonies rarely hold together for more than a few years. Shortly after reaching adulthood, a tibbit develops an intense desire to wander the world and satisfy her racial curiosity. Tibbits can be found wherever humans and other civilized humanoid races have established cities, towns, and colonies. Among humans and other humanoids tibbits usually remain in their cat form. The stray cat that prowls a neighborhood, the mangy cat adopted as a temple's unofficial pet, and the lazy feline always close at hand at the local tavern might be tibbits. Driven by curiosity, tibbits love to remain in their animal form while observing humans.

In humanoid form, tibbits are small, stealthy, dark-skinned people with pointed ears and catlike eyes. Their hair tends to grow thick and long and males tend to grow sideburns. Their skin tones range from a tawny brown to black, but occasionally a tibbit has pure white skin. Their hair color matches the wide range of colors found in house cats, from pure white to striped silver to deep black.

In their cat form, tibbits look like fat but energetic house cats. They appear identical to—and indistinguishable from—any common, domesticated breed.

\begin{multicols}{2}

\begin{itemize*}
\item Small size
\item 20ft movement.
\item Monstrous Humanoid Type (Shapeshifter subtype)
\item Darkvision 60ft
\item +2 Dexterity, -2 Strength: Tibbits are small and relatively weak, but they have a cat's quick reflexes and fluid agility.
\item Small: As a Small creature, a tibbit gains a +1 size bonus to Armor Class, a +1 size bonus on attack rolls, and a +4 size bonus on Hide checks, but she uses smaller weapons than humans use, and her lifting and carrying limits are three-quarters of those of a Medium creature.
\item Feline Transformation: See below
\item +2 racial bonus on all Spot checks. Tibbits have keen eyes.
\item +2 racial bonus on all Jump and Escape Artist checks. Like their feline cousins, tibbits are quick, nimble, and lithe.
\item Feline Languages: The Feline language is spoken by all tibbits and cats with an Intelligence of 3 or higher, allowing a tibbit to use the Diplomacy skill against such felines. The Feline language is part of the felines' racial heritage. Other races cannot master it, nor can they use spells such as tongues to communicate with cats.
\item Alignment: Usually chaotic neutral
\item Favored Classes: \linkclass{Ranger} and \linkclass{Rogue}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
14 & +1d4 & +1d6 & +2d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
2'6'' & 2'6'' & \multicolumn{2}{c}{+2d4}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 30 lb. & \cellcolor{white} 30 lb. & \multicolumn{2}{c}{\cellcolor{white} X 1 lb.}\\
\end{multicolsbasictable}

\end{multicols}

\pagebreak

\textbf{Feline Transformation:} At will, as a standard action, a tibbit can transform into a house cat. This effect is similar to the spell polymorph but with a number of key changes.

In cat form, the tibbit becomes size Tiny. Her size bonus to Armor Class and on attack rolls increases to +2, and her size bonus on Hide checks becomes +8. She gains a +10 bonus to her land speed. A tibbit uffers a -8 penalty to Strength (minimum 3) but gains a +2 bonus to Dexterity.

A tibbit gains natural claw and bite attacks in her feline form. A tibbit's claws deal 1d2 points of damage and her bite deals ld3 points of damage. With a full attack, she can attack twice with her claws at her full attack bonus and once with her bite with a -5 penalty. A tibbit does not gain additional attacks due to a high base attack bonus when in cat form.

A tibbit can transform from a cat back to her humanoid form as a full-round action. She must wait 1 hour to turn back into a cat after reverting to her humanoid form.

A tibbit's equipment doen't transforms and fall were they are, magical equipment shifts to adopt a form suitable to a cat, such as a collar or anklet and continue to provide their benefits.
A tibbit's cat form is unable to speak or use her paws to manipulate fine objects. She cannot cast spells with a verbal or somatic component, use scrolls, or otherwise activate magic items.

While in cat form, a tibbit gains the scent ability.

A tibbit slain in cat form reverts to her humanoid form after 1 round.

Any spell that reveals the true nature of a creature under the effects of polymorph shows the truth behind a tibbit's cat guise. Spells that reveal magical auras but do not penetrate a polymorph spell reveal nothing special about a tibbit in cat form.

Aside from the changes noted here, a tibbit's abilities and game statistics otherwise remain the same. Note that anyone spotting a tibbit in cat form has a difficult time recognizing the feline as a tibbit.

\begin{smallbasictable}{Tibbit Regions}{p{2cm} l p{5cm} p{5cm}}
\multicolumn{4}{c}{\textbf{As Any \linksec{Human} Regions}}\\
\end{smallbasictable}

\pagebreak