%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Deep Imaskari Human}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Secret and few, the deep Imaskari are heirs to the lost empire of Imaskar. One of the earliest human empires, Imaskar rose in what is now the Dust Desert and Plains of Purple Dust. Wizard-kings of heady power, the Imaskari were destroyed by the slaves they had abducted from other worlds (who eventually became the folk of Mulhorand and Unther) and the machinations of unusual creatures of their own creation (the phaerimms). The Imaskari faded away into history as their empire crumbled, leaving behind nothing but mysterious ruins. A secret few, however, charged with epic wizardry, managed to preserve themselves and their kin. Fleeing deep into the bowels of the earth, they sealed themselves away from both the knowledge and the recriminations of the surface world.

The deepest fissures of the earth have long hidden an ancient secret: The descendents of the Imaskari still live. Thousands of years of isolation combined with purposeful magical modifications have transformed these deep Imaskari into a human subrace adapted to life underground. The deep Imaskari have long managed to conceal the existence of their hidden kingdom even from other Underdark races by enforcing complete separation.

Now, however, deep Imaskari isolation is coming to an end. The magical seal that so long protected the kingdom of Deep Imaskar has been breached, and a few deep Imaskari have begun to wander the deep ways of the world that their ancestors fled long ago.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Humanoid Type (Human subtype)
\item +2 Intelligence, –2 Dexterity. Deep Imaskari are bright and quick to learn arcane lore, but they lack the balance and agility of most other humanoid races.
\item Low-Light Vision: A deep Imaskari can see twice as far as a human in starlight, moonlight, torchlight, or similar conditions of poor illumination. She retains the ability to distinguish color and detail under these conditions.
\item Spell Clutch (Su): Because the deep Imaskari have studied magic for ages on end, a certain facility with magic has seeped into their blood. Once per day, a deep Imaskari can recall any 1st level spell that she has already prepared and then cast. The spell is then prepared again, just as if it hadn’t been cast.
\item +4 bonus on Hide checks when underground: A deep Imaskari’s marblelike skin helps her hide in underground terrain.
\item Alignment: Usually neutral
\item Favored Classes: See Deep Imaskari Regions Below
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
20 & +4d6 & +6d6 & +3d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'4'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 126 lb. & \cellcolor{white} 86 lb. & \multicolumn{2}{c}{\cellcolor{white}X (1d6) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Deep Imaskari Regions}{c*{5}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{4cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{4cm}}{\raggedright{}\textbf{[Regional] Feat}} & \textbf{Favored Classes} \\
\multicolumn{1}{p{2cm}}{\raggedright{}Underdark (Deep Imaskar)} & Roushoum & \multicolumn{1}{p{4cm}}{\raggedright{}Abyssal, Aquan, Celestial, Draconic, Elven, Terran} & \multicolumn{1}{p{4cm}}{\raggedright{}\linkfeat{Arcane Schooling}, \linkfeat{Magical Training}, \linkfeat{Otherworldly}} & \linkclass{Warlock} and \linkclass{Wizard} \\
\end{smallbasictable}

\pagebreak