%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Chondathan Human}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Descended from the natives of the Vilhon Reach, these hardy folk have spread to settle most of the western and central Inner Sea region and much of the Western Heartlands. Chondathans form the primary racial stock of Altumbel, Cormyr, the southern Dalelands, the Dragon Coast, the Great Dale, Hlondeth and both shores of the Vilhon Reach, the Pirate Isles of the Inner Sea, Sembia, and Sespech. They are slender, tawny-skinned folk with brown hair that ranges from almost blond to almost black. Most are tall and have green or brown eyes, but these traits are hardly universal. The Chondathan domination of central Faerûn came about largely by virtue of extensive trade and settlement rather than by force of arms. Many Chondathans are merchants of one sort or another, and they are not afraid to take risks, travel, or settle new lands.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Humanoid Type (Human subtype)
\item 1 extra feat at 1st level.
\item 4 extra skill points at 1st level and 1 extra skill point at each additional level.
\item Alignment: Any
\item Favored Classes: See Chondathan Regions Below
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
15 & +1d4 & +1d6 & +2d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
5'0'' & 4'4'' & \multicolumn{2}{c}{+3d6}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 120 lb. & \cellcolor{white}85 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Chondathan Regions}{c*{5}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{[Regional] Feat}} & \textbf{Favored Classes} \\
 Aglarond & Aglarondan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Chessentan, Damaran, Draconic, Elven, Mulhorandi, Orc, Sylvan, Untheric} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Discipline}, \linkfeat{Luck of Heroes}, \linkfeat{Treetopper}} & \linkclass{Cleric} and \linkclass{Wizard} \\
 Altumbel & Aglarondan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Aquanm, Chondathan, Chessentan, Rashemi, Serusan, Untheric} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Bullheaded}, \linkfeat{Militia}, \linkfeat{Stormheart}} & \linkclass{Rogue} and \linkclass{Wizard} \\
 Cormyr & Chondathan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Damaran, Elven, Gnome, Goblin, Halfling, Orc, Turmic} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Caravanner}, \linkfeat{Discipline}, \linkfeat{Foe Hunter} (Goblinoid)} & \linkclass{Knight} and \linkclass{Wizard} \\
 The Dalelands & Chondathan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Damaran, Elven, Giant, Gnome, Orc, Sylvan} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Caravanner}, \linkfeat{Luck of Heroes}} & \linkclass{Barbarian} and \linkclass{Druid} \\
\end{smallbasictable}

\pagebreak

\begin{smallbasictable}{Chondathan Regions}{c*{5}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{[Regional] Feat}} & \textbf{Favored Classes} \\
 Damara & Damaran & \multicolumn{1}{p{3.5cm}}{\raggedright{}Chondathan, Dwarven, Giant, Goblin, Orc, Uluik} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Bullheaded}, \linkfeat{Grim Visage}, \linkfeat{Jotunbrud}} & \linkclass{Monk} and \linkclass{Paladin} \\
 The Dragon Coast & Chondathan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Aglarondan, Chessentan, Damaran, Goblin, Halflling, Orc, Turmic} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Silver Palm}, \linkfeat{Stormheart}, \linkfeat{Thug}} & \linkclass{Assassin} and \linkclass{Druid} \\
 The Great Dale & Damaran & \multicolumn{1}{p{3.5cm}}{\raggedright{}Giant, Goblin, Mulhorandi, Rashemi, Sylvan} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Bullheaded}, \linkfeat{Dauntless}, \linkfeat{Forester}} & \linkclass{Barbarian} and \linkclass{Druid} \\
 Impiltur & Damaran & \multicolumn{1}{p{3.5cm}}{\raggedright{}Aglarondan, Chessentan, Chondathan, Dwarven, Giant, Goblin, Mulhorandi, Turmic} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Dauntless}, \linkfeat{Fearless}, \linkfeat{Foe Hunter} (Demon)} & \linkclass{Paladin} and \linkclass{Wizard} \\
 The Moonsea & Damaran & \multicolumn{1}{p{3.5cm}}{\raggedright{}Chessentan, Chondathan, Draconic, Giant, Goblin, Orc} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Foe Hunter} (Orc), \linkfeat{Street Smart}, \linkfeat{Thug}} & \linkclass{Fighter} and \linkclass{Rogue} \\
 The Nelanther Isles & Chondathan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Alzhedo, Goblin, Illuskan, Lantanese, Orc, Shaaran} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Stormheart}, \linkfeat{Thug}} & \linkclass{Rogue} and \linkclass{Storm Lord} \\
 Sembia & Chondathan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Chessentan, Damaran, Gnome, Halfling, Mulhorandi, Shaaran, Turmic} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Caravanner}, \linkfeat{Silver Palm}, \linkfeat{Twin Sword Style}} & \linkclass{Fighter} and \linkclass{Paladin} \\
 Silverymoon & Chondathan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Dwarven, Elven, Giant, Illuskan, Orc, Sylvan} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Education}, \linkfeat{Smooth Talk}} & \linkclass{Sorcerer} and \linkclass{Wizard} \\
 Turmish & Turmic & \multicolumn{1}{p{3.5cm}}{\raggedright{}Chessentan, Chondathan, Draconic, Dwarven, Ignan, Shaaran} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Luck of Heroes}, \linkfeat{Mercantile Background}, \linkfeat{Militia}} & \linkclass{Fighter} and \linkclass{Wizard} \\
 The Vast & Damaran & \multicolumn{1}{p{3.5cm}}{\raggedright{}Aglarondan, Chondathan, Dwarven, Giant, Goblin, Orc, Rashemi} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Luck of Heroes}, \linkfeat{Mercantile Background}, \linkfeat{Thug}} & \linkclass{Fighter} and \linkclass{Wizard} \\
\end{smallbasictable}

\pagebreak