%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Mulan Human}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Since the fall of ancient Imaskar, the Mulan have dominated the eastern shores of the Sea of Fallen Stars. Led by two pantheons of deities, the ancient Mulan empires of Mulhorand and Unther conquered at various times Ashanath, Chessenta, the Eastern Shaar, Murghôm, Rashemen, Semphar, Thay, Thesk, and the Wizards’ Reach cities that lie south of the Yuirwood. In their wake, these empires have left ruling elites composed almost exclusively of Mulan. After millennia of rulership, the Mulan have become arrogant, highly resistant to change, and wholly convinced of their cultural superiority.

The Mulan are firmly wedded to the use of magic, with the only major point of disagreement being whether to pursue the arcane or divine tradition. For many generations the god-kings, powerful avatars of the Mulhorandi and Untheric deities long resident on Toril, ruled both empires as incarnate gods. The somnolent rule of the god-kings permitted the development of a powerful priest class in Mulan cultures that has long struggled with practitioners of arcane spellcasting for power. Their heavyhanded clerical rule prompted repeated rebellions by wizards and sorcerers, leading to the dominance of Thay by Red Wizards of Mulan descent.

Mulan are generally tall, slim, and sallow-skinned with eyes of hazel or brown. They lack much body hair, and many, including all nobles, shave any hair that they do have. Hair color on an unshaved Mulan ranges from black to dark brown. The lower classes of Thay, Mulhorand, and Unther often have significant Rashemi or Turami blood, leading to darker complexions. The folk of Chessenta have long mixed with the nearby Chondathans, and pure Mulan features are rare there.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Humanoid Type (Human subtype)
\item 1 extra feat at 1st level.
\item 4 extra skill points at 1st level and 1 extra skill point at each additional level.
\item Alignment: Any
\item Favored Classes: See Mulan Regions Below
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
15 & +1d4 & +1d6 & +2d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'11'' & 4'6'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 120 lb. & \cellcolor{white} 85 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Mulan Regions}{c*{5}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{[Regional] Feat}} & \textbf{Favored Classes} \\
 Altumbel & Aglarondan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Aquan, Chondathan, Chessentan, Rashemi, Serusan, Untheric} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Bullheaded}, \linkfeat{Militia}, \linkfeat{Stormheart}} & \linkclass{Rogue} and \linkclass{Wizard} \\
 Chessenta & Chessentan & \multicolumn{1}{p{3.5cm}}{\raggedright{}Aglarondan, Chondathan, Draconic, Mulhorandi, Turmic, Untheric} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Artist}, \linkfeat{Magical Training}, \linkfeat{Street Smart}} & \linkclass{Bard} and \linkclass{Fighter}/\linkclass{Marshall} \\
 Mulhorand & Mulhorandi & \multicolumn{1}{p{3.5cm}}{\raggedright{}Aglarondan, Chessentan, Draconic, Durpari, Goblin, Tuigan, Untheric} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Magical Training}, \linkfeat{Mind over Body}, \linkfeat{Theocrat}} & \linkclass{Paladin} and \linkclass{Wizard} \\ 
Thay & Mulhorandi & \multicolumn{1}{p{3.5cm}}{\raggedright{}Chessentan, Damaran, Gnoll, Infernal, Rashemi, Tuigan, Untheric} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Discipline}, \linkfeat{Mind over Body}, \linkfeat{Tattoo Focus}} & \linkclass{Cleric} and \linkclass{Wizard} \\
Unther & Untheric & \multicolumn{1}{p{3.5cm}}{\raggedright{}Chessentan, Draconic, Mulhorandi, Orc, Shaaran} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Magical Training}, \linkfeat{Street Smart}, \linkfeat{Theocrat}} & \linkclass{Cleric} and \linkclass{Wizard} \\
\end{smallbasictable}

\pagebreak