%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Bedine Human}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Bedine were a proud, warlike race that inhabited the southern Anauroch regions, but were concentrated in the region known as the Sword. Most folk of the Realms had no idea that the Bedine even existed, and those who did rarely could understand the difficult conditions of survival that drove them to live the way that they did.

They had brown-hued skin, brown eyes, and black or brown hair and were of average height and weight for a humanoid creature of Faerun. Those rare instances of blue eyes or blond hair were a product of outlander blood.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Humanoid Type (Human subtype)
\item 1 extra feat at 1st level.
\item 4 extra skill points at 1st level and 1 extra skill point at each additional level.
\item Alignment: Usually chaotic
\item Favored Classes: See Bedine Regions Below
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
15 & +1d4 & +1d6 & +2d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'9'' & 4'4'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 115 lb. & \cellcolor{white} 80 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Bedine Regions}{c*{5}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{[Regional] Feat}} & \textbf{Favored Classes} \\
 Anauroch & Midani & \multicolumn{1}{p{3.5cm}}{\raggedright{}Chondathan, Damaran, Draconic, Gnoll, Netherese, Orc} & \multicolumn{1}{p{2.4cm}}{\raggedright{}\linkfeat{Fearless}, \linkfeat{Knifefighter}, \linkfeat{Survivor}} & \linkclass{Fighter} and \linkclass{Ranger} \\
\end{smallbasictable}

\pagebreak