%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Half Mountain Orc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Half Orcs are fairly common throughout Faerûn. They have no true homeland to call their own and as a result most spend their lives wandering the world in search of a purpose. Half Orcs are invariably the product of a Human and an Orc, but stories are told of Half Orcs carrying the blood of Dwarves, Goblins, Hobgoblins, and even Halflings, Gnomes, and Rlves. Orcs are a fecund race, and such stories likely have some genesis in truth.

Half Mountain Orcs are usually about as tall as a Human and a little heavier. Their skin tends to be pale green with purple undertones, and their faces feature sloping brows, jutting jaws with prominent teeth, and flat, squashed noses. This and their coarse body hair make their lineage plain for all to see.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Humanoid Type (Orc and Human subtype)
\item Darkvision 60ft
\item +2 Strength
\item +2 to \linkskill{Intimidate}, \linkskill{Gather Information}, and \linkskill{Survival}.
\item Alignment: Any
\item Favored Classes: \linkclass{Assassin} and \linkclass{Barbarian}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
14 & +1d4 & +1d6 & +2d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d12}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 150 lb. & \cellcolor{white} 110 lb. & \multicolumn{2}{c}{\cellcolor{white} X (2d6) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Half Mountain Orc Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Amn & Orc, Chondathan & \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Draconic, Giant, Gnoll, Halfling} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Dauntless}, \linkfeat{Surefooted}, \linkfeat{Thug}}\\
Chessenta & Orc, Chessentan & \multicolumn{1}{p{5cm}}{\raggedright{}Chondathan, Draconic, Giant, Turmic} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Daylight Adaptation}, \linkfeat{Dauntless}, \linkfeat{Furious Charge}}\\
\multicolumn{1}{p{2cm}}{\raggedright{}The Moonsea} & Orc, Damaran & \multicolumn{1}{p{5cm}}{\raggedright{}Chondathan, Draconic, Dwarven, Giant} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Axethrower}, \linkfeat{Resist Poison}, \linkfeat{Surefooted}}\\
The North & Orc, Illuskan & \multicolumn{1}{p{5cm}}{\raggedright{}Draconic, Dwarven, Goblin, Giant} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Daylight Adaptation}, \linkfeat{Resist Poison}, \linkfeat{Swift and Silent}}\\
Thesk & Orc, Damaran & \multicolumn{1}{p{5cm}}{\raggedright{}Giant, Gnoll, Gnome, Mulhorandi, Rashemi} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Daylight Adaptation}, \linkfeat{Knifefighter}, \linkfeat{Thug}}\\
Vaasa & Orc, Damaran & \multicolumn{1}{p{5cm}}{\raggedright{}Dwarven, Giant, Goblin, Uluik} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Dauntless}, \linkfeat{Surefooted}}\\
\end{smallbasictable}

\pagebreak