%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Orog}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Although everyone in Faerûn knows about the orc hordes of the North (the mountain orcs) and the nomadic orcs of the East (the gray orcs), only a relative few know of a third subrace that hails from the deeps below ground. The Underdark is the chosen haunt of these terrible creatures, the orogs. After thousands of years of survival in the harsh and dan- gerous Underdark, the orogs have changed to match their home, becoming more ferocious and better able to cope with the dangers found there.

Physically, an orog looks similar to a large mountain orc, except that the ears are somewhat larger, and their eyes are huge and pale. They average six and a half feet tall.

Over the centuries, orogs have mastered the art of forging armor and weapons from the strange ores found in the Underdark. They favor halfplate and full plate armor, which are typically adorned with armor spikes. Orog weapons are festooned with a multitude of hooks, spines, and redundant cutting edges. An orog rarely goes anywhere without being fully armed and armored.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Humanoid Type (Orc subtype)
\item Darkvision 120ft
\item +6 Strength, –2 Dexterity, –2 Wisdom, +2 Charisma: Orogs are incredibly strong, and they make natural leaders despite their ferocious appearance.
\item +2 racial bonus on \linkskill{Craft} (Armorsmithing) and \linkskill{Craft} (Weaponsmithing) checks. Orogs train from an early age at their tribal forges.
\item +2 natural armor.
\item Light Blindness (Ex): Abrupt exposure to bright light (such as sunlight or a daylight spell) blinds an orog for 1 round. In addition, orogs suffer a –1 circumstance penalty on all attack rolls, saves, and checks while operating in bright light.
\item Resistances: Orogs have fire resistance 5 and cold resistance 5. They are inured to extremes of temperature.
\item Proficient with greatsword and throwing axe. All orogs train with some sort of martial weapon from a very young age.
\item Alignment: Usually lawful evil
\item Favored Classes: \linkclass{Bard} and \linkclass{Fighter}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
14 & +1d4 & +1d6 & +2d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
5'10'' & 5'2'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 160 lb. & \cellcolor{white} 125 lb. & \multicolumn{2}{c}{\cellcolor{white} X (2d6) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Half Mountain Orc Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
The Moonsea & Orc, Damaran & \multicolumn{1}{p{5cm}}{\raggedright{}Chondathan, Draconic, Dwarven, Giant} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Axethrower}, \linkfeat{Resist Poison}, \linkfeat{Surefooted}}\\
The North & Orc, Illuskan & \multicolumn{1}{p{5cm}}{\raggedright{}Draconic, Dwarven, Goblin, Giant} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Daylight Adaptation}, \linkfeat{Resist Poison}, \linkfeat{Swift and Silent}}\\
Underdark & Orc & \multicolumn{1}{p{5cm}}{\raggedright{}Abyssal, Elven, Giant, Goblin, Illuskan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Axethrower}, \linkfeat{Blooded}, \linkfeat{Thug}}\\
\end{smallbasictable}

\pagebreak