%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Aquatic Elf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Rarely encountered by the landbound races, the aquatic elves are a civilized and good-hearted people who inhabit the seas surrounding Faerûn. Most aquatic elves hail from underwater cities in the Sea of Fallen Stars or in the Great Sea south of Faerûn, but small settlements of this race can be found in the seas along Faerûn’s western coasts as well.

The aquatic elves are tall, standing 6 feet or more in height. They have long limbs with strong swimming muscles, and their fingers and toes are long with thick webbing. Their most striking features are sets of gills along the collarbone and ribcage. Aquatic elves are nowhere near as thin as their landbound cousins, and their hair is usually stringy and thick, cut short for warriors but otherwise worn long. Great Sea aquatic elves have radiant skin of deep green with irregular thin brown stripes and patches. Aquatic elves from the Sea of Fallen Stars have skin in many shades of blue with white patches and stripes. Eye colors for both types of aquatic elf come in every shade seen among gold, moon, or wild elves. Their clothing is made of various undersea plants in shades of green, black, and brown, although aquatic elves usually go about lightly clad, if dressed at all, while underwater.

\begin{multicols}{2}

\begin{itemize*}
\item Medium sized.
\item 30ft movement, 40ft swin movement
\item Humanoid Type (Elf subtype)
\item \linkability{Low-Light Vision} (Ex)
\item Gills (Ex): Aquatic elves breathe salt water with ease. They can also breathe fresh water, but most find the experience to be very uncomfortable and are treated as fatigued while doing so and for 10 minutes afterward. Aquatic elves can survive out of the water for 1 hour per point of Constitution.
\item +2 Dexterity, -2 Intelligence.
\item Weapon Proficiency: The Aquatic Elves start proficient with trident, longspear, and net.
\item +8 racial bonus on all \linkskill{Swim} checks and can always choose to take 10 with \linkskill{Swim} checks, even if rushed or threatened. Aquatic elves can use the run action while swimming, as long as they swim in a straight line.
\item Alignment: Usually chaotic good
\item Favored Classes: \linkclass{Fighter} and \linkclass{Ranger}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
110 & +4d6 & +6d6 & +10d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 90 lb. & \cellcolor{white}70 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Aquatic Elf Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
 The Inner Sea & Elven, Serusan & \multicolumn{1}{p{5cm}}{\raggedright{}Aquan, Chondathan, Draconic, Giant, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Landwalker}, \linkfeat{Survivor}}\\
The Outer Sea & Elven, Serusan & \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Chondathan, Draconic, Illuskan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Survivor}, \linkfeat{Swift and Silent}}\\
\end{smallbasictable}

\pagebreak