%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Avariel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The avariels, or winged elves, are without a doubt the most reclusive and least numerous of the elven subraces on Faerûn. Many scholars have long dismissed them as creatures of myth. In truth, small numbers of avariels still dwell in Faerûn, concealed in hidden enclaves and remote regions.

The most striking feature of the avariels is their soft, feathered wings. These wings have spans of anywhere from twelve to sixteen feet and are usually white, but may also be gray, brown, black, or speckled. Avariels take great pride in their wings and spend long hours grooming them. Their skin is pale, often porcelain white, with tinges of blue or faint silver. They have silverwhite or black hair, with other shades being rare but not unheard of. The avariels’ eyes are rather large and more expressive than those of other elves, and they tend to be brilliant shades of blue or green. A few avariel have scintillating violet eyes as pure as amethysts. Avariels stand 5'9" tall on average, with thin, graceful limbs and angular facial features. They are the most beautiful and striking of the elven races, although too often this beauty is marred by haughtiness and condescension toward their landbound kin, whom they often pity.

Avariels are even more delicate than other elves, and their movements are quick, calculated, and graceful. They prefer to wear loose fitting, diaphanous clothing that catches the wind in flight and ripples and weaves in the air. Armor is almost never worn, because it tends to weigh the avariels down and hinder their graceful motion. Avariels cannot fly while wearing heavy armor.
\begin{multicols}{2}

\begin{itemize*}
\item Medium sized.
\item 30ft movement, 50ft fly movement
\item Humanoid Type (Elf subtype)
\item Keen Sight (Ex): Avariels gain a +4 racial bonus on all \linkskill{Spot} checks.
\item Flight (Ex): Avariels have a flying speed of 50 feet with average maneuverability, as long as they do not carry more than a Medium load, are not wearing Heavy armor, and are not fatigued or exhausted. Avariel wings have a span of 12 feet on average; they cannot fly in an area that does not allow them to fully extend their wings.

An avariel may make a dive attack. A dive attack works just like a charge, but the avariel must descend a minimum of 30 feet and attack with a piercing weapon; if she hits, she deals double damage. An avariel can use the run action while flying, provided she flies in a straight line.
\item +4 Dexterity, –2 Constitution, +2 Intelligence, +2 Wisdom. Avariels have hollow bones and, as a result, are more fragile than humans. At the same time, they are gifted with a keen intuition and intellect, and an almost otherworldly grace
\item Weapon Proficiency: The Avariel start proficient with rapier, longsword, lasso and bolas.
\item +4 racial bonus on \linkskill{Jump} checks. They are strong for their weight.
\item Alignment: Usually chaotic good
\item Favored Classes: \linkclass{Cleric} and \linkclass{Ranger}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
110 & +4d6 & +6d6 & +10d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
5'0" & 4'8" & \multicolumn{2}{c}{+2d8}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 70 lb. & \cellcolor{white}65 lb. & \multicolumn{2}{c}{\cellcolor{white}X (1d6) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Avariel Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
Snow Eagle Aerie & Auran, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Damaran, Draconic, Giant, Rashemi, Sylvan, Tuigan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Artist}, \linkfeat{Mind over Body}, \linkfeat{Rapid Flight}}\\
\end{smallbasictable}

\pagebreak