%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Drow}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Of the various elven subraces, none are more notorious than the Drow. Descended from the original dark-skinned Elven subrace called the Ssri-tel-quessir, the Drow were cursed into their present appearance by the good Elven deities for following the goddess Lolth down the path to evil and corruption. Also called Dark Elves, the Drow have black skin that resembles polished obsidian and stark white or pale yellow hair. They commonly have blood-red eyes, although pale eyes (so pale as to be often mistaken for white) in shades of pale lilac, silver, pink, and blue are not unknown. They also tend to be smaller and thinner than most Faerûnian Elves. Most Drow on the surface are evil and worship Vhaeraun, but some outcasts and renegades have a more neutral attitude, and there are even groups of good Drow who worship Eilistraee or other deities not of the traditional Drow pantheon. Though divided by endless feuds and schisms, the Drow are united in one terrible desire: they seethe with a hatred for the surface Elves. By their way of reckoning, they proved themselves the superior race in the Fourth Crown War, and the fact that the Seldarine (and Corellon in particular) punished them for their success is a poison that churns in their hearts and minds eternally. They burn with hatred for the Seldarine and their coddled children, and want nothing more than to return to the surface and bring to the elves there suffering a thousand times greater than that which the drow have been forced to endure over the past ten thousand years.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Humanoid Type (Elf subtype)
\item \linkability{Darkvision} 60ft
\item +2 Dexterity, –2 Constitution, +2 Intelligence. The drow have ruthlessly selected for agility, intelligence, and force of personality over generations.
\item Daylight Sensitivity: While in brightly lit surroundings (such as a \linkspell{daylight} spell), a Drow suffers a -2 penalty to attack rolls and precision-based skill checks.
\item +2 bonus to saving throws against spells and spell-like abilities.
\item +2 bonus to \linkskill{Spot}, and \linkskill{Listen} checks. A Drow who merely passes within 5 feet of a secret or concealed door is entitled to a Search check to notice it as if she were actively looking for it. A Drow’s senses are so keen that she practically has a sixth sense about hidden portals.
\item Drow never sleep and are immune to \linkcondition{sleep} effects. Drow must still perform their 4 hour daily trance to stay coherent and rested.
\item Proficient with either rapier, shortsword, hand crossbow and light crossbow
\item Alignment: Usually evil
\item Favored Classes: \linkclass{Cleric} and \linkclass{Wizard}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
110 & +4d6 & +6d6 & +10d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'5'' & 4'5'' & \multicolumn{2}{c}{+2d6}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 85 lb. & \cellcolor{white} 80 lb. & \multicolumn{2}{c}{\cellcolor{white} X (1d6) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Drow Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
Cormanthor Drow & Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Abyssal, Chondathan, Draconic, Drow Sign, Orc, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Blooded}, \linkfeat{Daylight Adaptation}, \linkfeat{Swift and Silent}}\\
Menzoberranyr & Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Abyssal, Draconic, Drow Sign, Goblin, Illuskan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Arachnid Rider}, \linkfeat{Magic in the Blood}, \linkfeat{Twin Sword Style}}\\
\end{smallbasictable}

\pagebreak