%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Moon Elf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The most common of the elven subraces on Faerûn are the Moon Elves. They have fair skin, sometimes tinged with blue, and hair of silver-white, black, or blue; humanlike colors are somewhat rare. Their eyes are blue or green, with gold flecks. Moon Elves prefer to dress in rustic clothes of simple cuts and fashions that are nevertheless of fine and exquisite make. They adorn their dress with embroidered patterns, beads, and similar trappings, preferring earthen colors for everyday wear, hues that make it easy to conceal themselves in foliage. In places of safety or in times of revelry, Moon Elves enjoy dressing in bold colors— the more brightly colored, the better. Hair is worn in braids or ponytails, twined with wires or beads. Moon Elves sometimes wear body paint or tattoos in mystic patterns, although not to extent the wild elves do.

\begin{multicols}{2}

\begin{itemize*}
\item Medium sized.
\item 30ft movement
\item Humanoid Type (Elf subtype)
\item \linkability{Low-Light Vision}
\item +2 Dexterity, -2 Constitution.
\item Immunity to magic sleep effects, and a +2 racial saving throw bonus against enchantment spells or effects.
\item Weapon Proficiency: Moon Elves receive the Martial Weapon Proficiency feats for the longsword, rapier, longbow (including composite longbow), and shortbow (including composite shortbow) as bonus feats.
\item +2 racial bonus on \linkskill{Listen}, \linkskill{Search}, and \linkskill{Spot} checks. A Moon Elf who merely passes within 5 feet of a secret or concealed door is entitled to a \linkskill{Search} check to notice it as if she were actively looking for it.
\item Alignment: Usually chaotic good
\item Favored Classes: \linkclass{Assassin} and \linkclass{Wizard}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
110 & +4d6 & +6d6 & +10d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 90 lb. & \cellcolor{white}70 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Moon Elf Regions}{l l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Elven Court & Chondathan, Elven & Damaran, Giant, Gnome, Orc, Sylvan & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fearless}, \linkfeat{Strong Soul}, \linkfeat{Woodwise}}\\
Evereska & Chondathan, Elven & Auran, Draconic, Goblin, Giant, Illuskan, Orc & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Discipline}, \linkfeat{Gift of Tongues}, \linkfeat{Magical Training}}\\
Evermeet & Elven & Aquan, Auran, Celestial, Chondathan, Illuskan, Sylvan & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Magical Training}, \linkfeat{Otherworldly}, \linkfeat{Spellwise}}\\
Silverymoon & Elven, Illuskan & Chondathan, Dwarven, Giant, Orc, Sylvan & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Education}, \linkfeat{Mind over Body}, \linkfeat{Strong Soul}}\\
Waterdeep & Chondathan, Elven &  Alzhedo, Dwarven, Halfling, Illuskan, Orc & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Cosmopolitan}, \linkfeat{Smooth Talk}, \linkfeat{Twin Sword Style}}\\
\end{smallbasictable}

\pagebreak