%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Half Moon Elf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The most prominent of the races of mixed heritage, Half Elves can be found throughout Faerûn, but have few lands to call their own. They feel at home both in the sprawling human empires and the secretive Elven retreats, standing between elf and human culture but truly belonging to neither. They are a handsome and even-tempered race who handle the challenges of their mixed heritage with grace and reserve.

One of the major subraces of Half Elves in Faerûn are the Common Half Elves. The Common Half Elves are those whose elven parents hail from the Moon Elf, Sun Elf, Wild Elf, and Wood Elf peoples

Common Half Eelves blend Human and Elven features, influenced by the subrace of their Elven parent and the ethnicity of their Human parent. Moon Half Elves have pale skin tinged bluish around the ears and chin, framing their lower faces.

\begin{multicols}{2}

\begin{itemize*}
\item Medium sized.
\item 30ft movement.
\item Humanoid Type (Elf and Human subtype)
\item \linkability{Low-Light Vision}
\item Immunity to \linkspell{sleep} spells and similar magical effects, and a +2 racial bonus on saving throws against enchantment spells or effects.
\item +1 racial bonus on \linkskill{Listen}, \linkskill{Search}, and \linkskill{Spot} checks.
\item +2 racial bonus on \linkskill{Diplomacy} and \linkskill{Gather Information} checks.
\item Alignment: Any
\item Favored Classes: \linkclass{Fighter} and \linkclass{Wizard}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
20 & +1d6 & +2d6 & +3d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 110 lb. & \cellcolor{white} 80 lb. & \multicolumn{2}{c}{\cellcolor{white} X {2d4} lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Half Moon Elf Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
Aglarond & Aglarondan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Chessentan, Damaran, Draconic, Mulhorandi, Orc, Sylvan, Untheric} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Forester}, \linkfeat{Luck of Heroes}, \linkfeat{Treetopper}}\\
\multicolumn{1}{p{2cm}}{\raggedright{}The Dalelands} & Chondathan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Dwarven, Giant, Goblin, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Artist}, \linkfeat{Fleet of Foot}, \linkfeat{Strong Soul}}\\
Silverymoon & Elven, Illuskan & \multicolumn{1}{p{5cm}}{\raggedright{}Chondathan, Dwarven, Giant, Orc, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Education}, \linkfeat{Mind over Body}, \linkfeat{Strong Soul}}\\
\multicolumn{1}{p{2cm}}{\raggedright{}The High Forest} & Elven, Illuskan & \multicolumn{1}{p{5cm}}{\raggedright{}Chondathan, Giant, Goblin, Orc, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fleet of Foot}, \linkfeat{Forester}, \linkfeat{Treetopper}}\\
Waterdeep & Chondathan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Dwarven, Halfling, Illuskan, Orc} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Cosmopolitan}, \linkfeat{Smooth Talk}, \linkfeat{Twin Sword Style}}\\
\end{smallbasictable}

\pagebreak