%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Star Elf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The green depths of the Yuirwood hide an ancient secret long forgotten by folk beyond Aglarond’s borders, and not widely known even within—the star elves, an elven subrace that retreated from Faerûn to an extraplanar refuge known as Sildëyuir. Sometimes referred to in ancient texts as mithral elves, the star elves concealed the existence of their hidden kingdom for almost two thousand years, leaving behind nothing but mysterious ruins and old, strong magic in the stone circles of the Yuirwood.

While the star elves have kept themselves apart from the rest of Faerûn for many centuries, their isolation is coming to an end. Besieged by an insidious peril from beyond the circles of the world, they face the possibility of being driven from Sildëyuir back to their ancient abode in the Yuirwood.

\begin{multicols}{2}

\begin{itemize*}
\item Medium sized.
\item 30ft movement
\item Humanoid Type (Elf subtype)
\item \linkability{Low-Light Vision}
\item +2 Charisma, –2 Constitution: Star elves are graceful but frail.
\item Immunity to magic sleep effects, and a +2 racial saving throw bonus against enchantment spells or effects.
\item Otherworldly Touch (Su): Between sunset and sunrise a star elf confers the ghost touch ability on any melee weapon she wields and any armor she wears, but only so long as she keeps the weapon in hand or wears the armor. Star elves have a magical affinity for starlight that gives them an unusual edge in fighting extradimensional foes.
\item Extraplanar (Su): Star elves are not outsiders, but they are not native to Faerûn. Spells and effects that target extraplanar creatures affect star elves. Banishment, dismissal, and similar effects that banish outsiders return a star elf to Sildëyuir.
\item +2 racial bonus on \linkskill{Listen}, \linkskill{Search}, and \linkskill{Spot} checks. A Star Elf who merely passes within 5 feet of a secret or concealed door is entitled to a \linkskill{Search} check to notice it as if she were actively looking for it.
\item Alignment: Usually good
\item Favored Classes: \linkclass{Bard} and \linkclass{Paladin}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
110 & +4d6 & +6d6 & +10d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 95 lb. & \cellcolor{white}75 lb. & \multicolumn{2}{c}{\cellcolor{white}X (1d6) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Star Elf Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
 Sildëyuir & Aglarondan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Abyssal, Auran, Infernal, Mulhorandi, Rashemi, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Forester}, \linkfeat{Otherworldly}, \linkfeat{Woodwise}}\\
 The Yuirwood & Aglarondan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Chessentan, Damaran, Draconic, Mulhorandi, Sylvan, Untheric} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Discipline}, \linkfeat{Luck of Heroes}, \linkfeat{Treetopper}}\\
\end{smallbasictable}

\pagebreak