%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Sun Elf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The majority of Faerûn’s sun elves live on Evermeet, having abandoned what remained of their ancient realms during the centuries following the falls of Illefarn and Cormanthyr. They are only now returning to the mainland to reestablish their presence there. The sun elves are famed for their command of both arcane and divine magic, which exceeds that of any other living race. Works of elven high magic thousands of years old still survive in the hidden refuges of the sun elves.

Sun elves are responsible for the majority of the great elven cities of legend, although other elven subraces aided the construction of many of these cities. Myth Drannor is perhaps their most famous creation, although probably not their most magnificent. Sun elf realms are the stuff legends are made of, an integral part of the history of Faerûn for thousands of years. The sun elves certainly know this, for they distance themselves from nonelf races and often won’t let such “lesser beings” into their lands.

Sun elves have bronze skin, hair of golden blond, copper, or black, and eyes of green or gold. They favor contemplation, lore, and study over the quick games and light-hearted songs of other elves, but seem to embody the unearthly beauty, grace, and presence of the elven folk.

Sun elves dress in clothing that is at the same time magnificent and understated, favoring cool colors such as blue and green. They decorate their clothes with intricate gold- or mithral-thread embroidery in exacting patterns whose subtle designs are easy to miss at first. Jewelry is simple but painstakingly crafted.

Of all the elven subraces, sun elves are the most arrogant and haughty—even more so than the avariels, whose haughtiness is rooted in pity for the landbound races. Sun elves believe that they are the true elven race, the builders and the leaders of the elven realms, and that the other elven subraces fail to live up to the solemnity and dignity of their ancient stock.

\begin{multicols}{2}

\begin{itemize*}
\item Medium sized.
\item 30ft movement
\item Humanoid Type (Elf subtype)
\item \linkability{Low-Light Vision}
\item +2 Intelligence, –2 Constitution. Sun elves value study and contemplation over the feats of agility learned by most other elves.
\item Immunity to magic sleep effects, and a +2 racial saving throw bonus against enchantment spells or effects.
\item Weapon Proficiency: Moon Elves receive the Martial Weapon Proficiency feats for the longsword, rapier, longbow (including composite longbow), and shortbow (including composite shortbow) as bonus feats.
\item +2 racial bonus on \linkskill{Listen}, \linkskill{Search}, and \linkskill{Spot} checks. A Sun Elf who merely passes within 5 feet of a secret or concealed door is entitled to a \linkskill{Search} check to notice it as if she were actively looking for it.
\item Alignment: Usually Good
\item Favored Classes: \linkclass{Fighter} and \linkclass{Wizard}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
110 & +4d6 & +6d6 & +10d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 90 lb. & \cellcolor{white}70 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Sun Elf Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
Evereska & Chondathan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Auran, Draconic, Goblin, Giant, Illuskan, Orc} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Discipline}, \linkfeat{Gift of Tongues}, \linkfeat{Magical Training}}\\
Evermeet & Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Aquan, Auran, Celestial, Chondathan, Illuskan, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Magical Training}, \linkfeat{Otherworldly}, \linkfeat{Spellwise}}\\
Silverymoon & Elven, Illuskan & \multicolumn{1}{p{5cm}}{\raggedright{}Chondathan, Dwarven, Giant, Orc, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Education}, \linkfeat{Mind over Body}, \linkfeat{Strong Soul}}\\
Waterdeep & Chondathan, Elven &  \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Dwarven, Halfling, Illuskan, Orc} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Cosmopolitan}, \linkfeat{Smooth Talk}, \linkfeat{Twin Sword Style}}\\
\end{smallbasictable}

\pagebreak