%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Wild Elf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The wild elves of Faerûn are insular and savage, and as a result are rarely seen outside their forest homes. In ages past the wild elves (or green elves, as they were more commonly known) raised great kingdoms in the forests and fielded armies to defend their homes, but with the march of time they have aban doned the trappings of civilization, becoming a furtive, reclusive race. The wild elves were always close to nature, even more so than other elves, but they have forgotten many of the high arts and lore of their people, choosing stealth and survival over building and book learning.

Wild elves are stocky and strongly built for elves. Their skin tends to be dark brown, and their hair ranges from black to light brown, lightening to silvery white with age. They are quiet around anyone except their own kind, and quickly become hostile in these uncomfortable situations. Clothing is kept to a minimum among the wild elves, although they make up for this with body decoration of all sorts—tattoos, war paint, feathers, and beaded jewelry that shows a surprising streak of complex and beautiful artistry.

\begin{multicols}{2}

\begin{itemize*}
\item Medium sized.
\item 30ft movement
\item Humanoid Type (Elf subtype)
\item \linkability{Low-Light Vision}
\item +2 Dexterity, –2 Intelligence. Wild elves are hardier than other elves, but favor physical action and feats of athleticism instead of learning to solve problems.
\item Immunity to magic sleep effects, and a +2 racial saving throw bonus against enchantment spells or effects.
\item Weapon Proficiency: Moon Elves receive the Martial Weapon Proficiency feats for the longsword, rapier, longbow (including composite longbow), and shortbow (including composite shortbow) as bonus feats.
\item +2 racial bonus on \linkskill{Listen}, \linkskill{Search}, and \linkskill{Spot} checks. A Wild Elf who merely passes within 5 feet of a secret or concealed door is entitled to a \linkskill{Search} check to notice it as if she were actively looking for it.
\item Alignment: Usually chaotic good
\item Favored Classes: \linkclass{Sorcerer} and \linkclass{Barbarian}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
110 & +4d6 & +6d6 & +10d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 100 lb. & \cellcolor{white}80 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Wild Elf Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
 The Chondalwood & Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Chessentan, Chondathan, Gnoll, Halfling, Shaaran, Sylvan, Untheric} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Forester}, \linkfeat{Survivor}, \linkfeat{Treetopper}}\\
Elven Court & Chondathan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Damaran, Giant, Gnome, Orc, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fearless}, \linkfeat{Strong Soul}, \linkfeat{Woodwise}}\\
 The Wealdath & Chondathan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Draconic, Giant, Goblin, Shaaran, Orc} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fleet of Foot}, \linkfeat{Swift and Silent}, \linkfeat{Woodwise}}\\
\end{smallbasictable}

\pagebreak