%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Wood Elf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The wood elves are among the most numerous of Faerûn’s elven people, a young and confident folk who hold the old elven forest homelands in strength. Heirs to the second generation of elven nations, the wood elves see their realms as the natural successors to lands such as Eaerlann and Cormanthyr. Where the old empires expanded with strength and pride, the realms of the wood elves hope to grow with compassion and humility. The wood elves do not view their homelands as a land apart from Faerûn; they understand better than their kindred that for better or worse, their fates are bound up with the fates of the humans, dwarves, and halflings around them.

Also known as copper elves or sylvan elves, these people have coppery skin tinged with green, and brown, green, or hazel eyes. Hair is usually brown or black, occasionally blond or coppery- red. Wood elves prefer to dress in simple clothing, similar to the moon elves but not quite so colorful. They favor a simple cut to tunic or dress, set off by common embroidery in natural designs.

They are particularly fond of leather armor, and they often wear lovingly tooled and well-crafted suits even when they do not feel endangered. Their clothing, leather armor or not, is usually in dark shades of green and earth tones to better blend with their natural surroundings. They are a humble race and only rarely do they enhance their appearance with jewelry or similar accessories.

\begin{multicols}{2}

\begin{itemize*}
\item Medium sized.
\item 30ft movement
\item Humanoid Type (Elf subtype)
\item \linkability{Low-Light Vision}
\item +2 Strength, +2 Dexterity, –2 Constitution, –2 Intelligence, –2 Charisma. Wood elves are strong but slight, and tend to be less cerebral and intuitive than other elves.
\item Immunity to magic sleep effects, and a +2 racial saving throw bonus against enchantment spells or effects.
\item Weapon Proficiency: Moon Elves receive the Martial Weapon Proficiency feats for the longsword, rapier, longbow (including composite longbow), and shortbow (including composite shortbow) as bonus feats.
\item +2 racial bonus on \linkskill{Listen}, \linkskill{Search}, and \linkskill{Spot} checks. A Wood Elf who merely passes within 5 feet of a secret or concealed door is entitled to a \linkskill{Search} check to notice it as if she were actively looking for it.
\item Alignment: Usually neutral
\item Favored Classes: \linkclass{Ranger} and \linkclass{Druid}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
110 & +4d6 & +6d6 & +10d6\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d10}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 100 lb. & \cellcolor{white}80 lb. & \multicolumn{2}{c}{\cellcolor{white}X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Wood Elf Regions}{c*{4}{c}}
\textbf{Region} & \multicolumn{1}{p{2cm}}{\raggedright{}\textbf{Automatic Laguages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{Bonus Languages}} & \multicolumn{1}{p{5cm}}{\raggedright{}\textbf{[Regional] Feat}}\\
Elven Court & Chondathan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Damaran, Giant, Gnome, Orc, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fearless}, \linkfeat{Strong Soul}, \linkfeat{Woodwise}}\\
Evermeet & Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Aquan, Auran, Celestial, Chondathan, Illuskan, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Magical Training}, \linkfeat{Otherworldly}, \linkfeat{Spellwise}}\\
The Forest of Lethyr & Damaran, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Giant, Gnoll, Gnome, Orc, Rashemi} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fleet of Foot}, \linkfeat{Forester}, \linkfeat{Luck of Heroes}}\\
The High Forest & Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Gnoll, Goblin, Halfling, Illuskan, Sylvan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fleet of Foot}, \linkfeat{Forester}, \linkfeat{Treetopper}}\\
The Wealdath & Chondathan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Draconic, Giant, Goblin, Shaaran, Orc} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fleet of Foot}, \linkfeat{Swift and Silent}, \linkfeat{Woodwise}}\\
The Yuirwood & Aglarondan, Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Chessentan, Damaran, Draconic, Mulhorandi, Sylvan, Untheric} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Discipline}, \linkfeat{Luck of Heroes}, \linkfeat{Treetopper}}\\
\end{smallbasictable}

\pagebreak