%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Knight}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Knights are more than a social position, in fact many knights don't have any social standing at all. These knight errants uphold the values of honour, and make a name for themselves adventuring (Hedge Knight).

\textbf{Alignment:} Many Knights are Lawful. But not all of them. You have to maintain your code of conduct, but plenty of Chaotic creatures can do that too.

\textbf{Starting Gold:} 6d6x10 gp (210 gold)

\textbf{Starting Age:} Moderate

\textbf{Hit Die:} d12

\textbf{Class Skills:} The Knight's class skills are \linkskill{Climb} (Str), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Handle Animal} (Cha), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Knowledge} (Int), \linkskill{Listen} (Wis),  \linkskill{Perform} (Cha), \linkskill{Ride} (Dex), \linkskill{Sense Motive} (Wis), \linkskill{Spot} (Wis), and \linkskill{Swim} (Str).

\textbf{Skills/Level:} 4 + Intelligence Bonus

\goodbab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{classtable}
\levelone{Code of Conduct, \linkfeat{Mounted Combat}}
\leveltwo{Knightly Challenge, Speak to Animals}
\levelthree{Damage Reduction, Quick Recovery}
\levelfour{Bonus [Combat] Feat}
\levelfive{linkfeat{Command}, Knightly Courage}
\levelsix{Call to Battle, Defend Others}
\levelseven{Knightly Spirit, Sacrifice}
\leveleight{Bonus [Combat] Feat}
\levelnine{Bastion of Defense, Energy Resistance}
\levelten{Knightly Order}
\leveleleven{Knightly Courage}
\leveltwelve{Bonus [Combat] Feat}
\levelthirteen{Draw Fire}
\levelfourteen{Mettle}
\levelfifteen{Spell Shield}
\levelsixteen{Bonus [Combat] Feat}
\levelseventeen{Knightly Courage}
\leveleighteen{Impetuous Endurance}
\levelnineteen{Loyal Beyond Death}
\leveltwenty{Knightly Paragon}
\end{classtable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} Knights are proficient with all Simple weapons and Martial Weapons. Knights are proficient with Light, Medium, and Heavy Armor, Shields, and Great Shields.

\textbf{Code of Conduct:} A Knight must fight with honor even when her opponents do not. Indeed, a Knight subscribes to honor to a degree far more than that which is strictly considered necessary by other honorable characters. Actions which even hint at the appearance of impropriety are anathema to the Knight:

\begin{itemize*}
\item A Knight must not accept undue assistance from allies even in combat. A Knight must refuse bonuses from Aid Another actions.
\item A Knight must refrain from the use poisons of any kind, even normally acceptable poisons such as blade toxins.
\item A Knight may not voluntarily change shape, whether she is impersonating a specific creature or not.
\item A Knight may not sell Magic Items.
\end{itemize*}

A Knight who fails to abide by her code of conduct loses the ability to use any of her Knightly abilities which require actions until she atones.

\textbf{Mounted Combat:} A Knight gains \linkfeat{Mounted Combat} as a Bonus [Combat] Feat at 1st level. If she already has \linkfeat{Mounted Combat}, she may gain any [Combat] Feat she meets the prerequisites for instead.

\textbf{Knightly Challenge (Ex):} At 2nd level as a Swift Action, a Knight can challenge an opponent. This foe must be within Medium Range(100 ft.+10 ft./level.) and be able to hear the Knight's challenge. If the target creature inflicts any damage on the Knight before the Knight's next turn, the attempt fails. Otherwise, any attacks the Knight uses against the opponent \textit{during} her next turn inflict an extra d6 of damage for each Knight level. This effect ends at the end of her next turn, or when she has struck her opponent a number of times equal to the number of attacks normally allotted her by her Base Attack Bonus.

You can use this ability a number of times per day equal to 1/2 her Knight levels + her Charisma bonus (minimum once per day).

\textit{Example:} Vayn is a 6th level Knight presently benefiting from a \linkspell{Haste} spell, granting her an extra attack during a Full Attack action. On her turn she designates an Ettin as her primary opponent, and the Ettin declines to attack her during the ensuing turn. When her next turn comes up, she uses a Full Attack and attacks 3 times. The first two hits inflict an extra 6d6 of damage, and then she designates the Ettin as her opponent again. It won't soon ignore her!

\textbf{Speak to Animals (Ex):} A Knight can make herself understood by beasts. Her steed always seems to be able to catch the thrust of anything she says. A 2nd level Knight gains a bonus to any of her \linkskill{Ride} and \linkskill{Handle Animal} checks equal to half her Knight Level. In addition, there is no limit to how many tricks she can teach a creature, and her \linkskill{Handle Animal} checks are not penalized for attempting to get a creature to perform a trick it does not know.

 \textbf{Damage Reduction (Ex):} A Knight trains to suffer the unbearable with chivalry and grace. At 3rd level, she gains Damage Reduction of X/-, where X is half her Knight level, rounded down.

\textbf{Quick Recovery (Ex):} If a 3rd level Knight is \textit{stunned} or \textit{dazed} during her turn, that condition automatically ends at the end of that turn, even if the duration would normally be longer.

\textbf{Command:} A Knight gains \linkfeat{Command} as a Bonus Feat at level 5.

\textbf{Knightly Courage (Ex):} At 5th level, a Knight becomes immune to shaken effects, a 9th level Knight will now become immune to frightened effects and at 15th level a Knight becomes fully immune to all fear effects.

\textit{Note:} A failed fear saving throw will still consider the Knight to be ''shaken or frightened'' for the effect of becoming frightened and panicked.

\textbf{Call to Battle (Ex):} Starting at 6th level, a Knight become an inspiring figure on the battlefield. When all seems lost, she becomes a beacon of hope who continues to fight on despite the odds. No cause is yet lost when a knight still battles on its name.

As a swift action, a Knight can expend one use of her knight's Challenge ability to grant an ally another save against a fear effect. The target gains a bonus on this save equal to her Charisma bonus (if any). If the target succeeds on this save, he gains the benefit for a successful save against the attack or spell. This ability reflects her talent to inspire her allies in the face of a daunting foe.

\textit{Example:} Cornelius fails his save against Hyperia-lich's fear spell. On his next action, Herr Rex uses his call to battle ability to grant Cornelius another save. If he succeeds, he immediately shrugs off the effect of the fear spell.

\textbf{Defend Others (Ex):} A 6th level Knight may use her own body to defend others. Any ally adjacent to the Knight gains Evasion, though she does not.

\textbf{Knightly Spirit (Ex):} As a Move Equivalent Action, a 7th level Knight may restore an amount of attribute damage or drain equal to half of her Knight's level.

\textbf{Sacrifice (Ex):} As an immediate action, a 7th level Knight may make herself the target of an attack or targeted effect that targets any creature within her reach.

\textbf{Bastion of Defense (Ex):} A 9th level Knight can defend others with great facility. All adjacent allies except the Knight gain a +2 Dodge bonus to their Armor Class and Reflex Saves.

\textbf{Energy Resistance (Ex):} A Knight may protect herself from energy types that she expects. As a Swift Action, a 9th level Knight may grant herself Energy Resistance against any energy type she chooses equal to her Knight Level +  her Shield Bonus. This energy resistance lasts until she spends a Swift Action to choose another Energy type or her Shield bonus is reduced.

\textbf{Knightly Order:} At 10th level you become a full Knight and take up a Knightly Order. 

You gain an ability related to the Order, below are some Orders you may join, you may also make a Order of your own (Work with GM on what this new Order does and what ability it has, you may also use an Order below as base for your new Order).

\begin{itemize*}
\item \textbf{Angelic Knight (LG):} The Angelic Knights are a transformational order that attempts to live by the precepts of the upper planes. An Angelic Knight gains wings that allow her to Fly 60ft with perfect maneuverability. Also an Angelic Knight benefits from \linkspell{Protection From Evil} at all times.
\item \textbf{Bane Knight (LE):}  The Bane Knights stand for running around burning the countryside with extreme burning. Bane Knights are immune to fire and do not have to breathe. In addition, a Bane Knight may set any unattended object on fire with a Swift Action at up to Medium Range(100 ft.+10 ft./level.).
\item \textbf{Chaos Knight (C-Any):}  Chaos Knights follow Chaos, and the Primordial Gods. The Primordial forces grants great power in order to spread chaos everywhere. Their natural armor bonus increases by +5 and they are immune to \textit{Sleep} effects.
\item \textbf{Dragon Knight (LG):}  Dedicated to the Platinum Dragon, the Dragon Knights serve love and justice in equal measure as dishes to those who need them. A Dragon Knight gains a +5 bonus to \linkskill{Sense Motive} and any armor she wears has an enhancement bonus of 2 higher than normal (it also gains a platinum sheen in the process, and as a side effect a Dragon Knight is never dirty for more than a few seconds).
\item \textbf{Elemental Knight (C-Any):}  The Elemental Knights may be dedicated to a particular element, or somehow dedicated to all of them. An Elemental Knight can \linkspell{Plane Shift} at will to any Inner plane or the Prime Material plane a number of times be day equal to her Charisma bonus. Also, she is immune to \textit{stunning} and ignores the harmful planar effects of the Inner Planes.
\item \textbf{Fey Knight (Any):}  Using the powers of the Sprites, the Fey Knight has many fairy strengths. Firstly, she gains DR 10/Iron added to her DR from Knight levels. Also, any of her attacks may do non-lethal damage at any time if this is desired. Also she never ages and does not need to drink or eat.
\item \textbf{Great Knight (Any-E):}  Clad in opulent armor, the Great Knight cares only for her own power. The Great Knight gains a +4 bonus on Disarm or Sunder tests, and gains a +4 Profane bonus to her Strength.
\item \textbf{Hell Knight (LE):}  Forged in the sulphurous clouds of Hell, the Hell Knight is bathed in an evil radiance. In addition to being granted a ceremonial weapon made of green steel, a Hell Knight gains the coveted See In Darkness ability of the Devils.
\item \textbf{Imperial Knight (L-Any):}  All Great Reams needs champions able to unswervingly support its interests, and the Imperial Knight is one of the best. She may impose a \linkspell{Zone of Truth} at will as a Supernatural ability, and all of her attacks are Lawfully aligned. Also, she continuously benefits from \linkspell{Magic Circle Against Chaos}.
\end{itemize*}

%\pagebreak


\textbf{Draw Fire (Ex):} A 13th level Knight can exploit the weaknesses of unintelligent opponents. With a Swift Action, she may pique the interest of any mindless opponent within Medium Range(100 ft.+10 ft./level.). That creature must make a Willpower Save (DC 10 + 1/2 Hit Dice + Constitution Modifier) or spend all of its actions moving towards or attacking the Knight. This effect ends after a number of rounds equal to the Knight's class level.

\textbf{Mettle (Ex):} An 14th level Knight who succeeds at a Fortitude Partial or Willpower Partial save is not affected at all (basically like Evasion, but for Fortitude and Willpower saves).

\textbf{Spell Shield (Ex):} An 15th level Knight gains Spell Resistance of 5 + her Knight levels + shield AC bonus.

\textbf{Impetuous Endurance (Ex):} Starting at 18th level, a Knights fighting spirit enables her to push her body beyond the normal limits of endurance. She no longer automatically fail a saving throw on a roll of 1. She might still fail the save if she result fails to equal or beat the DC.

\textbf{Loyal Beyond Death (Ex):} At 19th level, if a Knight is reduced to 0 or fewer hit points by an effect that otherwise leaves her body intact, she can expend one use of her knight's challenge ability to remain conscious and continue to act for 1 more round before dying. She can use this ability even if she hit point total is -10 or lower. If her body is somehow destroyed before her next action (such as by disintegrate), then she cannot act. She can continue to expend uses of her knight's challenge ability to survive from round to round until she run out of uses. If she receive healing that leaves her with more than -10 hit points, she survive (or fall unconscious, as appropriate to her new hit point total) when she stop using this ability. Otherwise, death overtakes her or when she run out of uses of her knight's challenge ability.

\textbf{Knightly Paragon:} At 20 level a Knight becomes a Paragon of her Order turning into a Native Outsider, type chages to Outsider, adding Native and (her alignment) subtypes.

\textit{Example:} Grimm Bladebright being a Chaotic Neutral Shield Dwarf will become a Outsider type (Chaotic, Dwarf and Native subtype).