%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Yathrinshee}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Because she is a goddess of undeath, Kiaransalee favors servants who combine their clerical mastery of the undead with arcane research into negative energy and necromancy. Yathrinshees, the elite ranks of Kiaransalee’s priests, are powerful masters of necromantic magic, both arcane and divine.

In order to become a yathrinshee, a priestess must have access to both divine and arcane magic. Virtually all yathrinshees were clerics and wizards before adopting the prestige class, though a very few were sorcerers rather than wizards. Most are specialist necromancers rather than generalist wizards. The strict spellcasting requirements tend to keep members of other classes out of the yathrinshee class.

Yathrinshees are the leaders of Kiaransalee’s secretive church wherever it is found. They lead Kiaransalee’s followers in worship and also in pursuing the church’s goals—plotting revenge against
the enemies of their goddess, killing her foes, and animating them as undead

\textbf{Prerequisites:} 
\begin{description*}
\item[\hspace*{1.4cm}Race:] Drow.
\item[\hspace*{1.4cm}Gender:] Female.
\item[\hspace*{1.4cm}Skills:] \linkskill{Knowledge} (Arcana) 7 ranks, \linkskill{Knowledge} (Religion) 7 ranks, \linkskill{Knowledge} (Undeath) 7 ranks, \linkskill{Perform} (Sing) 3 ranks.
\item[\hspace*{1.4cm}Spells:] Able to cast \linkspell{Animate Dead} as a divine spell and \linkspell{Spectral Hand} as an arcane spell
\item[\hspace*{1.4cm}Patron Deity:] Kiaransalee.
\end{description*}

\textbf{Alignment:} Usually Chaotic Evil.

\textbf{Hit Die:} d6

\textbf{Class Skills:} The Yathrinshee's class skills are \linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Knowledge} (Int), \linkskill{Profession} (Wis), \linkskill{Search} (Int), and \linkskill{Spellcraft} (Int).

\textbf{Skills/Level:} 2 + Intelligence Bonus

\poorbab{}
\poorfor{}
\poorref{}
\goodwil{}

\begin{extraclasstable}{\textbf{Spellcasting}}
\levelone{Rebuke Undead, Necromancer &\multicolumn{1}{p{4.5cm}}{\raggedright +1 level of arcane and Divine Spellcasting Class}}
\leveltwo{Threnody &\multicolumn{1}{p{4.5cm}}{\raggedright +1 level of arcane and Divine Spellcasting Class}}
\levelthree{Curse of the Revenancer &\multicolumn{1}{p{4.5cm}}{\raggedright +1 level of arcane and Divine Spellcasting Class}}
\levelfour{Zone of Desecration &\multicolumn{1}{p{4.5cm}}{\raggedright +1 level of arcane and Divine Spellcasting Class}}
\levelfive{Death Ward, Keening & \multicolumn{1}{p{4.5cm}}{\raggedright+1 level of arcane and Divine Spellcasting Class}}
\end{extraclasstable}

\classfeatures

\textbf{Weapon and Armor Proficiency:} The Yathrinshee gains no weapons or armor proficiency.

\textbf{Spellcasting:} The Yathrinshee gains new spells per day (and spells known, if applicable) as if she had also gained a level in an arcane and a divine spellcasting class that she belonged to before, She does not, however, gain any other benefit a character of that class would have gained (bonus metamagic or item creation feats, and so on), except for an increased effective caster level. If a character had more than one arcane spellcasting class or more than one divine spellcasting class before she became a yathrinshee, she must decide to which class she adds each level of yathrinshee for the purpose of determining spells per day and spells known.

\textbf{Rebuke Undead (Su):} The Yathrinshee levels stack with her Cleric levels for the purpose of Rebuking or Commanding Undead. Don't give the Yathrinshee a Rebuke Undead ability.

\textbf{Necromancer (Ex):} The Yathrinshee has unsurpassed power over death. When she casts spells from the School of Necromancy, all her spellcaster levels stack for the purpose of determining her effective caster level. She does not gain higher-level spells any faster than normal or gain any additional spells per day, but the spells she casts are much more effective.

\textbf{Threnody (Su):} Once per day, a Yathrinshee of 2nd level or higher can sing a song of lament that can unnerve opponents who are engaged in combat with an undead creature. In effect, any undead within 30 feet of the yathrinshee gains a gaze attack identical to the unnerving gaze of a chain devil. Any creature that meets the Yathrinshee’s eyes must make a Will save (DC 10 + Necromancy Caster level/2 + Cha Modifier) or take a –2 penalty on attack rolls for 1d3 rounds because it sees the faces of departed loved ones or bitter enemies. If an undead creature actually is the animated corpse of a friend or companion of the Yathrinshee’s opponent, the save DC increases by 2 and the penalty is doubled (to –4).

\textbf{Curse of the Revenancer (Su):} Any creature slain by a Yathrinshee of 3rd level or higher rises immediately as a Zombie under her control.

\textbf{Zone of Desecration (Su):} At 4th level, the Yathrinshee is continuously surrounded by a 20-foot-radius aura of negative energy. The effect is otherwise identical to that of the \linkspell{Desecrate} spell.

\textbf{Death Ward (Su):} A Yathrinshee of 5th level or higher is immune to death effects and negative energy as though protected by a death ward spell. A Undead Yathrinshee also gains Turn Resistance +4. This benefit stacks with any existing Turn Resistance.

\textbf{Keening (Su):} At 5th level, the Yathrinshee can Keen once per day. This ability works like the \linkspell{Wail of the Banshee} spell, except that it affects any number of creatures within a 30-foot-radius spread centered on the Yathrinshee. (DC 10 + Necromancy Caster level/2 + Cha Modifier)



