%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Aasimar}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Aasimar bear the legacy of a celestial being or even a deity in their ancestry, and have incredible potential to do good in the world. At the same time, their heritage marks them as different and often leads to persecution, ridicule, or exile from superstitious or backward communities. It is not unknown for an Aasimar to give in to bitterness in the face of adversity and turn to evil.

Aasimar are the descendants of Humans and some good outsider, such as a true celestial, a celestial creature, Couatl, Lillend, or even a servant or avatar of a good deity. (Some of these creatures must use magic to assume a form that is compatible with a Human mate, of course.) While Elves, Dwarves, Gnomes, and Halflings with good outsider ancestry are reputed to exist, those crossbreeds are not true Aasimar.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Outsider Type (Native and Human subtype)
\item \linkability{Darkvision} 60ft
\item +2 Charisma, +2 Wisdom
\item Aasimar with a Charisma of at least 10 may cast \linkspell{light} as a spell-like ability at will. They may only have one such light active at a time.
\item +2 racial bonus to \linkskill{Spot}, and \linkskill{Listen} checks.
\item Alignment: Usually good
\item Favored Classes: \linkclass{Paladin} and \linkclass{Sorcerer}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
15 & +1d6 & +1d8 & +2d8\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d8}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 120 lb. & \cellcolor{white} 85 lb. & \multicolumn{2}{c}{\cellcolor{white} X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Aasimar Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Mulhorand & Mulhorandi & \multicolumn{1}{p{5cm}}{\raggedright{}Aglarondan, Celestial, Rashemi, Shaaran, Untheric} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Discipline}, \linkfeat{Magic in the Blood}, \linkfeat{Theocrat}}\\
Chessenta & Chessentan & \multicolumn{1}{p{5cm}}{\raggedright{}Aglarondan, Chondathan, Draconic, Mulhorandi, Turmic, Untheric} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Magical Training}, \linkfeat{Knifefighter}, \linkfeat{Street Smart}}\\
Unther & Untheric & \multicolumn{1}{p{5cm}}{\raggedright{}Abyssal, Chessentan, Dwarven, Orc, Shaaran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Magic in the Blood}, \linkfeat{Theocrat}, \linkfeat{Thug}}\\
\end{smallbasictable}

\pagebreak