%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Genasi, Fire}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Fire genasi are usually thought of as hot-blooded and quick to anger, and they have earned that reputation. Mercurial, proud, and often fearless, they are not content to sit and watch the world pass them by. Fire genasi have obvious physical traits that mark them as different from humans, and they are often the target of mistrust and persecution. Some fire genasi are able to use their quick wits to turn the tables on their tormentors, while others find that their barbed words only make their foes more angry. Many fire genasi are destroyed as infants by their own parents, who fear that they are demonspawn

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Outsider Type (Native, Fire and Human subtype)
\item \linkability{Darkvision} 60ft
\item +2 Intelligence, -2 Charisma
\item Control Flame (Sp): Fire Genasi can cause a nonmagical fire within 10 feet of them to diminish to the level of coals or flare to the brightness of daylight and double the normal radius of its illumination. This ability does not change the normal heat output or fuel consumption of the fire source, lasts 5 minutes, and may be done once per day. They use this ability as 5th-level sorcerers.
\item Clerical Focus: A Fire Genasi Cleric must choose a deity who grants access to the \linkdomain{Fire} domain and select Fire as one of his two domains.
\item Alignment: Usually Neutral
\item Favored Classes: \linkclass{Fighter} and \linkclass{Wizard}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
15 & +1d6 & +1d8 & +2d8\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d12}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 120 lb. & \cellcolor{white} 85 lb. & \multicolumn{2}{c}{\cellcolor{white} X (2d6) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Tiefling Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Calimshan & Alzhedo & \multicolumn{1}{p{5cm}}{\raggedright{}Auran, Chondathan, Goblin, Ignan, Shaaran, Tashalan} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Bloodline of Fire}, \linkfeat{Mind over Body}, \linkfeat{Magic in the Blood}}\\
Thay & Mulhorandi & \multicolumn{1}{p{5cm}}{\raggedright{}Aglarondan, Damaran, Gnoll, Infernal, Rashemi} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Dreadful Wrath}, \linkfeat{Mind over Body}, \linkfeat{Tattoo Focus}}\\
Unther & Untheric & \multicolumn{1}{p{5cm}}{\raggedright{}Abyssal, Chessentan, Dwarven, Orc, Shaaran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Magic in the Blood}, \linkfeat{Theocrat}, \linkfeat{Thug}}\\
\end{smallbasictable}

\pagebreak