%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Gloaming}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Gloamings are planetouched beings descended from natives of Gnomes and the Plane of Shadow. These unusual creatures are quite uncommon in the Underdark and extremely rare in the surface world. Most observers can easily recognize that a gloaming is planetouched in some fashion, but few know exactly how. Members of other races often mistake a gloaming for some sort of tiefling.

Gloamings are compulsive travelers, so they usually remain strangers among other races. Their curiosity often manifests as wanderlust, and indeed most gloamings display a great drive to explore. Different gloamings pursue different interests and goals, so finding more than four or five of them together for a long time is atypical.

A gloaming is a pale-skinned humanoid with catlike eyes and dark, furry wings. Her skin is naturally luminescent, and she can control its glow, choosing a degree of illumination from none to as bright as a torch. A typical gloaming has one or more tattoos that create interesting shading effects when her skin glows. Her eyes have slightly oval pupils and reflect light like a cat’s. This property makes them seem almost metallic in dim light, though in ordinary light they appear gray, green-gray, blue-gray, or violet-gray. A gloaming’s wings may be black or any deep shade of brown, blue or gray.

\begin{multicols}{2}

\begin{itemize*}
\item Small size. A gloaming has a +1 size bonus to Armor Class, a +1 size bonus on attack rolls, and a +4 size bonus on Hide checks.
\item 20ft movement, Fly spped 40 ft (average)
\item Outsider Type (Native and Gnome subtype)
\item \linkability{Darkvision} 60ft
\item –2 Strength, +2 Dexterity, –2 Wisdom, +2 Charisma. Gloamings are lithe but not very strong. Their exotic appearance is appealing to many, but their curiosity sometimes makes them choose courses of action that are less than wise.
\item Light Blindness (Ex): Abrupt exposure to bright light (such as sunlight or a daylight spell) blinds a gloaming for 1 round. In addition, she takes a –1 circumstance penalty on all attack rolls, saves, and checks while operating in bright light.
\item Shadow Spells: Gloamings have a racial predilection for shadow-based spells. They cast illusion (shadow) spells at +1 caster level.
\item +2 racial bonus on saves against illusion (shadow) spells or effects
\item +4 racial bonus on saves against psionic abilities
\item +4 racial bonus on Move Silently checks.
\item Luminescence: As a standard action, a gloaming can make her skin provide illumination equal to that produced by any light source up to and including a torch, or she can mute the glow altogether. A gloaming’s luminescence lasts until she chooses to change it.

When a gloaming dies, her luminescence fades to nothing over the course of 10 minutes.
\item Portal Sensitive: Gloamings can detect an active or inactive portal as if it were a normal secret door (Search DC 20). If you merely pass within 5 feet of a portal, you are entitled to a Search check to notice it as if you were actively looking for it.

You also gain a +2 bonus on your caster level check when trying to discern portal properties with the analyze portal spell.
\item Alignment: Usually chaotic
\item Favored Classes: \linkclass{Shadow Warrior} and \linkclass{Sorcerer}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
13 & +1d4 & +1d4 & +2d4\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
2'6'' & 2'6'' & \multicolumn{2}{c}{+1d4}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 25 lb. & \cellcolor{white} 25 lb. & \multicolumn{2}{c}{\cellcolor{white} X (1) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Tiefling Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Sphur Upra & Elven & \multicolumn{1}{p{5cm}}{\raggedright{}Aquan, Draconic, Dwarven, Sylvan, Terran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Fearless}, \linkfeat{Luck of Heroes}, \linkfeat{Smooth Talk}}\\
\end{smallbasictable}

\pagebreak