%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\raceentry{Tiefling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Carrying the taint of evil in their very souls, Tieflings are persecuted and feared in most parts of Faerûn. Those with gross physical alterations are often killed at birth, and even those with less noticeable physical traits are sometimes killed by their own horrified parents. Occasionally a Tiefling is born to someone indifferent to its appearance, determined to redeem it, willing to exploit it, or evil enough not to care about its nature, and these Tieflings are most likely to survive to adulthood. Most Tieflings are evil, but a few have managed to overcome their bloodline’s influence to make their own choices about good and evil. Tieflings are the distant descendants of a Human and some evil outsider, such as a Demon (usually a Marilith or Succubus), Devil (usually an Erinyes, Gelugon, or Pit Fiend), Night Gag, Rakshasa, or even a servant of an evil deity (some of these creatures must use magic to assume a form that is compatible with a Human mate, of course). Fiendtouched and similarly tainted mixes of Rlves (notably the Fey’ri), Orcs (such as the Tanarukk), and other races are known, but those are distinct lines and are not true Tieflings.

\begin{multicols}{2}

\begin{itemize*}
\item Medium Size
\item 30ft movement.
\item Outsider Type (Native and Human subtype)
\item \linkability{Darkvision} 60ft
\item +2 Dexterity, +2 Intelligence, -2 Charisma
\item Tieflings with a Charisma of at least 10 may cast \linkspell{Darkness} as a spell-like ability with a caster level equal to their character level once per day.
\item +2 bonus to \linkskill{Bluff}, \linkskill{Hide}, and \linkskill{Move Silently} checks.
\item Alignment: Usually evil
\item Favored Classes: \linkclass{Rogue} and \linkclass{Shadow Warrior}
\end{itemize*}

\begin{multicolsbasictable}{c*{4}{c}}

\textbf{Adulthood} & \textbf{Simple} & \textbf{Moderate} & \textbf{Complex}\\
15 & +1d6 & +1d8 & +2d8\\
\multicolumn{2}{c}{\textbf{Base Height}} & \multicolumn{2}{c}{\textbf{Base Height}}\\
\textbf{Male} &\textbf{Female} & \multicolumn{2}{c}{\textbf{Modifier}}\\
4'10'' & 4'5'' & \multicolumn{2}{c}{+2d8}\\
\multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}} & \multicolumn{2}{c}{\cellcolor{white}\textbf{Base Weight}}\\
\cellcolor{offyellow}\textbf{Male} & \cellcolor{offyellow}\textbf{Female} & \multicolumn{2}{c}{\cellcolor{offyellow}\textbf{Modifier}}\\
\cellcolor{white} 120 lb. & \cellcolor{white} 85 lb. & \multicolumn{2}{c}{\cellcolor{white} X (2d4) lb.}\\
\end{multicolsbasictable}

\end{multicols}

\begin{smallbasictable}{Tiefling Regions}{p{2cm} l p{5cm} p{5cm}}
\textbf{Region} & \textbf{Automatic Laguages} & \textbf{Bonus Languages} & \textbf{[Regional] Feat}\\
Impiltur & Damaran & \multicolumn{1}{p{5cm}}{\raggedright{}Abyssal, Aglarondan, Chessentan, Chondathan, Dwarven, Goblin, Turmic} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Dauntless}, \linkfeat{Dreadful Wrath}, \linkfeat{Thug}}\\
Mulhorand & Mulhorandi & \multicolumn{1}{p{5cm}}{\raggedright{}Aglarondan, Celestial, Rashemi, Shaaran, Untheric} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Discipline}, \linkfeat{Magic in the Blood}, \linkfeat{Theocrat}}\\
Silver Marches & Illuskan & \multicolumn{1}{p{5cm}}{\raggedright{}Abyssal, Chondathan, Dwarven, Elven, Giant, Goblin, Orc} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Dreadful Wrath}, \linkfeat{Education}, \linkfeat{Thug}}\\
Thay & Mulhorandi & \multicolumn{1}{p{5cm}}{\raggedright{}Aglarondan, Damaran, Gnoll, Infernal, Rashemi} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Dreadful Wrath}, \linkfeat{Mind over Body}, \linkfeat{Tattoo Focus}}\\
The Western Heartlands & Chondathan & \multicolumn{1}{p{5cm}}{\raggedright{}Alzhedo, Elven, Giant, Goblin, Infernal, Orc} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Dreadful Wrath}, \linkfeat{Street Smart}, \linkfeat{Thug}}\\
Unther & Untheric & \multicolumn{1}{p{5cm}}{\raggedright{}Abyssal, Chessentan, Dwarven, Orc, Shaaran} & \multicolumn{1}{p{5cm}}{\raggedright{}\linkfeat{Magic in the Blood}, \linkfeat{Theocrat}, \linkfeat{Thug}}\\
\end{smallbasictable}

\pagebreak